### 2020-05-27 paper/ms.tex
init

\documentclass[journal]{IEEEtran}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{listings}
\usepackage{makecell}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usepackage[hyphens]{url}
\usepackage{hyperref}

\lstdefinestyle{lststyle}{
	aboveskip=20pt,
	belowskip=20pt,
	frame=single,
	basicstyle=\tt\scriptsize,
	commentstyle=\color{gray}}

\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}

\begin{document}
\DTLloaddb{keys_values}{keys_values.csv}

\title{Reconciler: A Workflow for Certifying Computational Research Reproducibility}

\author{Paschalis~Bizopoulos and Dimitris~Bizopoulos
\thanks{P. Bizopoulos and D. Bizopoulos are Independent Researchers, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com, dimitrisbizopoulos@gmail.com}}

\maketitle

\begin{abstract}
	Previous work in reproducibility focused on providing frameworks to make research reproducible, however fewer work was done on reproducibility certification.
	We propose the Reconciler, that certifies the reproducibility of computational research papers written in \LaTeX.
	Two Docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
	Then the results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
	Lastly a third VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
	The two builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
	We release an open source implementation of the Reconciler, that certifies the reproducibility of this paper.
\end{abstract}

\section{Introduction}
A research paper is considered reproducible when reviewers are able to reproduce its results, given the data and experimental procedure.
More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms them creating the figures, tables and variables of the paper.
Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but this is not enough to certify its reproducibility.
A common workflow among researchers for certifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.

We propose the Reconciler workflow, that certifies the reproducibility of computational research papers written in \LaTeX.
The Reconciler workflow consists of two separate Virtual Machines (VMs) that build and run the Docker container which produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce two pdf files.
Lastly, a third VM compares the pdf files and certifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.

We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/9999.99999}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

For the rest of the paper we will refer to:
\begin{itemize}
	\item `paper' as a computational research paper,
	\item `results' as the figures, tables and variables that are shown in the paper,
	\item `\LaTeX\ code' as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the research paper,
	\item `results code' as the files containing the scientific-oriented programming language code that produces the results (\textit{*.py} files) and
	\item `code' as both the `\LaTeX\ code' and `results code'.
\end{itemize}

\section{The Reconciler Workflow}

\begin{figure*}[!t]
	\begin{minipage}{0.2\linewidth}
		\centering
		\subfloat[]{\begin{tikzpicture}[%
				grow via three points={one child at (0.5,-0.7) and
				two children at (0.5,-0.7) and (0.5,-1.4)},
				edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
				\node[draw]{root}
				child{node[draw, anchor=west]{workflow.yml}}
				child{node[draw, anchor=west]{Makefile}}
				child{node[draw, anchor=west, fill=blue!20]{Dockerfile}}
				child{node[draw, anchor=west, fill=blue!20]{main.py}}
				child{node[draw, anchor=west, fill=red!20]{paper}
				child{node[draw, anchor=west, fill=red!20]{ms.tex}}
				child{node[draw, anchor=west, fill=red!20]{ms.bib}}
				};
		\end{tikzpicture}
		\label{subfig:filehierarchy}}
	\end{minipage}
	\begin{minipage}{0.4\linewidth}
		\centering
		\subfloat[]{\begin{tikzpicture}[node distance=1.9cm, minimum height=1cm]
			\node[draw, rounded corners] (localrepo) {Local Repo};
			\node[draw, rounded corners, above of=localrepo] (remoterepo) {Remote Repo};
			\node[draw, rounded corners, above left of=remoterepo, fill=blue!20] (builddocker1) {Build Docker};
			\node[draw, rounded corners, above of=builddocker1, fill=red!20] (compilelatex1) {Compile \LaTeX};
			\node[draw, rounded corners, above right of=compilelatex1, fill=white] (comparison) {Comparison};
			\node[draw, rounded corners, above right of=remoterepo, fill=blue!20] (builddocker2) {Build Docker};
			\node[draw, rounded corners, above of=builddocker2, fill=red!20] (compilelatex2) {Compile \LaTeX};
			\path[draw, ->] (localrepo) -- node[left]{push} (remoterepo);
			\path[draw, ->] (remoterepo) -| node[left]{checkout} (builddocker1);
			\path[draw, ->] (builddocker1) -- node[left]{\LaTeX+results}(compilelatex1);
			\path[draw, ->] (compilelatex1) |- node[left]{pdf} (comparison);
			\path[draw, ->] (remoterepo) -| node[right]{checkout} (builddocker2);
			\path[draw, ->] (builddocker2) -- node[right]{\LaTeX+results} (compilelatex2);
			\path[draw, ->] (compilelatex2) |- node[right]{pdf} (comparison);
			\begin{scope}[on background layer]
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_1$}]{};
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker2) (compilelatex2) (builddocker2.west), label={[black!50]70:$VM_2$}]{};
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_3$}]{};
			\end{scope}
		\end{tikzpicture}
		\label{subfig:workflow}}
	\end{minipage}
	\begin{minipage}{0.4\linewidth}
		\centering
		\subfloat[]{\begin{tikzpicture}[node distance=1.9cm, minimum height=1cm]
			\node[draw, rounded corners] (localrepo) {Local Repo};
			\node[draw, rounded corners, above of=localrepo] (remoterepo) {Remote Repo};
			\node[draw, rounded corners, above of=remoterepo, fill=blue!20] (builddocker1) {Build Docker};
			\node[draw, rounded corners, above of=builddocker1, fill=red!20] (compilelatex1) {Compile \LaTeX};
			\node[draw, rounded corners, above right of=compilelatex1, fill=white] (comparison) {Comparison};
			\node[draw, rounded corners, below right of=comparison, fill=red!20] (compilelatex2) {Compile \LaTeX};
			\node[draw, rounded corners, below = 2.8cm of compilelatex2] (arxivrepo) {arXiv Repo};
			\path[draw, ->] (localrepo) -- node[left]{push} (remoterepo);
			\path[draw, ->] (remoterepo) -- node[left]{checkout} (builddocker1);
			\path[draw, ->] (builddocker1) -- node[left]{\LaTeX+results}(compilelatex1);
			\path[draw, ->] (compilelatex1) |- node[left]{pdf} (comparison);
			\path[draw, ->] (arxivrepo) -- node[right]{\LaTeX+results} (compilelatex2);
			\path[draw, ->] (compilelatex2) |- node[right]{pdf} (comparison);
			\begin{scope}[on background layer]
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_1$}]{};
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(compilelatex2), label={[black!50]50:$VM_2$}]{};
				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_3$}]{};
			\end{scope}
		\end{tikzpicture}
		\label{subfig:workflowarxiv}}
	\end{minipage}
	\caption{In (a) the template Reconciler file hierarchy is depicted as a file tree directory.
	Results and \LaTeX\ code reside in the same repository but this is optional.
	In (b) the proposed Reconciler workflow with the two independent branches is depicted, and in (c) a variation of the Reconciler applied on certifying arXiv papers, where the right branch fetches the results and the \LaTeX\ code from the arXiv servers.
	Blue denotes results code file or procedure, red denotes \LaTeX\ code file or procedure and gray background denotes that the encapsulated procedures is happening in a VM.
	Arrows in (b) and (c) denote the data flow direction, complemented by descriptive labels.}
	\label{fig:filehierarchyworkflow}
\end{figure*}

The Reconciler workflow can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container.
\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
The corresponding Dockerfile can be provided by the researcher or generated by tools such as containerit~\cite{nust2019containerit}.

A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:filehierarchy}) is used in this paper however this is optional, as the Reconciler only needs to know the directories of the main files of the \LaTeX\ and results code through its configuration file \textit{workflow.yml}.
The Reconciler workflow fits in the researcher workflow in the following way (as also shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}):
\begin{enumerate}
	\item the researcher writes or edits code,
	\item the researcher commits and pushes the changes to the remote repository, which triggers the Reconciler workflow:
		\begin{enumerate}
			\item two VMs (builders) independently build and run the Dockerfile of the results code,
			\item the results along with the \LaTeX\ code are used to compile the pdf files,
			\item the pdf files are sent to a third VM (certifier),
			\item the certifier VM certifies the research paper as reproducible if and only if the pdf files are the same using bit comparison.
		\end{enumerate}
\end{enumerate}

Docker usage in the Reconciler provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
The reason that two independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the certifier VM report the paper as non-reproducible.

Additional constraints could be imposed in the VMs such as disallowing images in the code and monitoring the network connections of the code to ensure that results are generated from the code and not fetching them from an external source.
Alternatively the code could just be open source to enable reviewers inspect the result generation procedure.

Variations of the Reconciler main workflow include:
\begin{itemize}
	\item preprint server (such as arXiv) results reproducibility certification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflowarxiv}.
		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the results code.
	\item one branch local certification where the last VM returns the hash of the resulted pdf enabling reviewers certifying the pdf output of their local branch.
		Using the previous workflow the Reconciler could also be used for regression testing and debugging, to ensure that changes to the code do not alter the results.
\end{itemize}

\subsection{Technical implementation}
A template of the Reconciler is available using Github Actions and is applied on the arXiv version of this paper.
The builder VMs use different versions of Ubuntu (16.04 and 18.04) and pull a docker image for building \LaTeX\ from DockerHub.

Regarding research that is computational costly or when reproducibility certification is required from the first stages of the research, the Reconciler template provides a debug flag that certifies the reproducibility of a smaller scale of the computational experiment.
E.g.\ the debug flag in the concept of neural networks could set the number of epochs and number of training samples to a low value.
Some possible executions that the Reconciler provides are summarized in the following syntax:
\begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
# SYNTAX
make [docker] [ARGS="[--full] [--gpu]"] [GPU="--gpus all"]

# where [...] denotes an optional argument.

# For example you can choose one of the following:
make
# Requires local installation of
# requirements.txt and texlive-full.
# Takes ~1 minute and populates the figures and table.
make ARGS="--full --gpu"
# Requires local installation of
# requirements.txt and texlive-full.
# Takes ~1 minute on an NVIDIA Titan X.
make docker
# Requires local installation of docker.
# Takes ~1 minute.
make docker ARGS="--full --gpu" GPU="--gpus all"
# Requires local installation of nvidia-container-toolkit.
# Takes ~1 minute on an NVIDIA Titan X.
make clean
# Restores the repo in its initial state by removing
# all figures, tables and downloaded datasets.
\end{lstlisting}

\section{Discussion}
Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
The Reconciler provides a simple solution in certifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
Future work needs to be done regarding improving the use of the Reconciler on reproducibility on the following:
\begin{enumerate}
	\item making scientific programming libraries reproducible,
	\item regarding infrastructure: the use of VMs that support CUDA to enable the application of the Reconciler on deep neural network research.
\end{enumerate}

\section{Conclusion}
Automating research reproducibility certification is becoming more important due to the increasing research output that has been observed the last few years.
Few works were done on this area, mostly proposing trust on an external third party.
The Reconciler certifies research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.

\section{APPENDIX - Improving Computational Research Reproducibility}
This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the results code Programming language.
A common culprit of reproducibility using \LaTeX\ is the time-date metadata of pdf output which can be disabled using the following into the \textit{.tex} code after the preamble:
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands for preamble.}, captionpos=b]
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\end{lstlisting}

A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named num\_samples.}, captionpos=b]
\DTLloaddb{keys_values}{keys_values.csv}
\DTLfetch{keys_values}{key}{num_samples}{value}
\end{lstlisting}

For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the results code:
\begin{itemize}
	\item number of samples of Fig.~\ref{fig:image} is $\DTLfetch{keys_values}{key}{num_samples}{value}$ and
	\item the number of columns of Table~\ref{table:table} is $\DTLfetch{keys_values}{key}{num_columns}{value}$.
\end{itemize}

Regarding the results code for Python random seeds need to be set to a specific value such as:
\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
random.seed(0) # for build-in random module
np.random.seed(0) # for numpy
torch.manual_seed(0) # for pytorch
torch.backends.cudnn.deterministic = True # for pytorch
torch.backends.cudnn.benchmark = False # for pytorch
tf.random.set_seed(0) # for Tensorflow
\end{lstlisting}

Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
For example Fig.~\ref{fig:image} depicts the signal:
\begin{equation}
	f(t) = \DTLfetch{keys_values}{key}{mu}{value} + \DTLfetch{keys_values}{key}{sigma}{value} * Z(t) + t
\end{equation}

,where $Z(t)\sim\mathcal{N}$.

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/image.pdf}
	\caption{Image example created from results code.}
	\label{fig:image}
\end{figure}

Another useful results function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}.

\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}, captionpos=b]
num_columns = 11
table = np.random.random((7, num_columns))
df = pd.DataFrame(table)
df.to_latex('table.tex', float_format="%.2f")
\end{lstlisting}

\begin{table}[h]
	\centering
	\caption{Table example created from results code.}
	\label{table:table}
	\setlength\tabcolsep{4.2pt}
	\input{tables/table.tex}
\end{table}

\bibliographystyle{IEEEtran}
\bibliography{ms}

\end{document}

### 2020-05-27 main.py

@@ -1,0 +1,53 @@
+#!/usr/bin/env python
+import argparse
+import numpy as np
+import pandas as pd
+
+from matplotlib import pyplot as plt
+from pathlib import Path
+
+plt.rcParams.update({'font.size': 12})
+
+if __name__ == '__main__':
+    np.random.seed(0)
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--full', default=False, action='store_true')
+    parser.add_argument('--gpu', default=False, action='store_true')
+    args = parser.parse_args()
+    if args.full:
+        num_samples = 200
+    else:
+        num_samples = 200
+    if args.gpu:
+        device = 'cuda'
+    else:
+        device = 'cpu'
+    path_paper = './paper'
+    path_images = f'{path_paper}/images'
+    path_tables = f'{path_paper}/tables'
+    Path(path_images).mkdir(parents=True, exist_ok=True)
+    Path(path_tables).mkdir(parents=True, exist_ok=True)
+
+    # Creating pdf images
+    mu = 0.42
+    sigma = 0.69
+    data = mu + sigma*np.random.randn(num_samples) + np.linspace(0, 5, num_samples)
+    plt.figure(constrained_layout=True, figsize=(6, 2))
+    plt.plot(data)
+    plt.grid(True)
+    plt.xlabel('X label')
+    plt.ylabel('Y label')
+    plt.ylim([-2, 7])
+    plt.autoscale(enable=True, axis='x', tight=True)
+    plt.savefig(f'{path_images}/image.pdf')
+    plt.close()
+
+    # Creating tables
+    num_columns = 11
+    table = np.random.random((3, num_columns))
+    df = pd.DataFrame(table)
+    df.to_latex(f'{path_tables}/table.tex', float_format="%.2f")
+
+    # Creating variables
+    df = pd.DataFrame({'key': ['num_samples', 'num_columns', 'mu', 'sigma'], 'value': [num_samples, num_columns, mu, sigma]})
+    df.to_csv(f'{path_paper}/keys_values.csv', index=False, float_format='%.1f')

### 2020-05-28 main.py
fix arXiv v2

@@ -17,7 +17,7 @@ if __name__ == '__main__':
     if args.full:
         num_samples = 200
     else:
-        num_samples = 200
+        num_samples = 20
     if args.gpu:
         device = 'cuda'
     else:

### 2020-05-29 paper/ms.tex
fix arxiv id

@@
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/9999.99999}}.
+We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

### 2020-06-04 main.py
simplify repo

@@ -1,15 +1,18 @@
 #!/usr/bin/env python
 import argparse
 import numpy as np
+import os
 import pandas as pd
 
 from matplotlib import pyplot as plt
-from pathlib import Path
 
 plt.rcParams.update({'font.size': 12})
 
 if __name__ == '__main__':
     np.random.seed(0)
+    path_results = 'results'
+    if not os.path.exists(path_results):
+        os.mkdir(path_results)
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
     parser.add_argument('--gpu', default=False, action='store_true')
@@ -22,11 +25,6 @@ if __name__ == '__main__':
         device = 'cuda'
     else:
         device = 'cpu'
-    path_paper = './paper'
-    path_images = f'{path_paper}/images'
-    path_tables = f'{path_paper}/tables'
-    Path(path_images).mkdir(parents=True, exist_ok=True)
-    Path(path_tables).mkdir(parents=True, exist_ok=True)
 
     # Creating pdf images
     mu = 0.42
@@ -39,15 +37,15 @@ if __name__ == '__main__':
     plt.ylabel('Y label')
     plt.ylim([-2, 7])
     plt.autoscale(enable=True, axis='x', tight=True)
-    plt.savefig(f'{path_images}/image.pdf')
+    plt.savefig(f'{path_results}/image.pdf')
     plt.close()
 
     # Creating tables
     num_columns = 11
     table = np.random.random((3, num_columns))
     df = pd.DataFrame(table)
-    df.to_latex(f'{path_tables}/table.tex', float_format="%.2f")
+    df.to_latex(f'{path_results}/table.tex', float_format="%.2f")
 
     # Creating variables
     df = pd.DataFrame({'key': ['num_samples', 'num_columns', 'mu', 'sigma'], 'value': [num_samples, num_columns, mu, sigma]})
-    df.to_csv(f'{path_paper}/keys_values.csv', index=False, float_format='%.1f')
+    df.to_csv(f'{path_results}/keys_values.csv', index=False, float_format='%.1f')

### 2020-06-05 main.py
test

@@ -9,7 +9,7 @@ from matplotlib import pyplot as plt
 plt.rcParams.update({'font.size': 12})
 
 if __name__ == '__main__':
-    np.random.seed(0)
+    #np.random.seed(0)
     path_results = 'results'
     if not os.path.exists(path_results):
         os.mkdir(path_results)

### 2020-06-05 main.py
test

@@ -9,7 +9,7 @@ from matplotlib import pyplot as plt
 plt.rcParams.update({'font.size': 12})
 
 if __name__ == '__main__':
-    #np.random.seed(0)
+    np.random.seed(0)
     path_results = 'results'
     if not os.path.exists(path_results):
         os.mkdir(path_results)

### 2020-06-30 main.py
change filename convention to hyphen

@@ -51,4 +51,4 @@ if __name__ == '__main__':
 
     # Creating variables
     df = pd.DataFrame({'key': ['num_samples', 'num_columns', 'mu', 'sigma'], 'value': [num_samples, num_columns, mu, sigma]})
-    df.to_csv(f'{path_results}/keys_values.csv', index=False, float_format='%.1f')
+    df.to_csv(f'{path_results}/keys-values.csv', index=False, float_format='%.1f')

### 2020-07-01 main.py
extract figure rcParams

@@ -7,7 +7,9 @@ import torch
 
 from matplotlib import pyplot as plt
 
-plt.rcParams.update({'font.size': 12})
+plt.rcParams['font.size'] = 20
+plt.rcParams['savefig.format'] = 'pdf'
+
 
 if __name__ == '__main__':
     torch.manual_seed(0)
@@ -40,7 +42,7 @@ if __name__ == '__main__':
     plt.ylabel('Y label')
     plt.ylim([-2, 7])
     plt.autoscale(enable=True, axis='x', tight=True)
-    plt.savefig(f'{path_results}/image.pdf')
+    plt.savefig(f'{path_results}/image')
     plt.close()
 
     # Creating tables

### 2020-07-01 main.py
fix fontsize

@@ -7,7 +7,7 @@ import torch
 
 from matplotlib import pyplot as plt
 
-plt.rcParams['font.size'] = 20
+plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
 

### 2020-07-24 main.py
revert to main.py

@@ -6,20 +6,21 @@ import torch
 
 from matplotlib import pyplot as plt
 
-from train import set_seed
-
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
-
 if __name__ == '__main__':
-    set_seed()
+    torch.manual_seed(0)
+    torch.backends.cudnn.deterministic = True
+    torch.backends.cudnn.benchmark = False
+    np.random.seed(0)
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
     parser.add_argument('--cache-dir', default='cache')
-    parser.add_argument('--results-train-dir', default='results-train')
     parser.add_argument('--results-dir', default='results')
     args = parser.parse_args()
+    if not os.path.exists(args.cache_dir):
+        os.mkdir(args.cache_dir)
     if not os.path.exists(args.results_dir):
         os.mkdir(args.results_dir)
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')

### 2020-07-24 train.py

@@ -1,30 +1,0 @@
-import argparse
-import numpy as np
-import os
-import pandas as pd
-import torch
-
-
-def set_seed():
-    torch.manual_seed(0)
-    torch.backends.cudnn.deterministic = True
-    torch.backends.cudnn.benchmark = False
-    np.random.seed(0)
-
-
-if __name__ == '__main__':
-    set_seed()
-    parser = argparse.ArgumentParser()
-    parser.add_argument('--full', default=False, action='store_true')
-    parser.add_argument('--cache-dir', default='cache')
-    parser.add_argument('--results-train-dir', default='results-train')
-    args = parser.parse_args()
-    if not os.path.exists(args.cache_dir):
-        os.mkdir(args.cache_dir)
-    if not os.path.exists(args.results_train_dir):
-        os.mkdir(args.results_train_dir)
-    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-    if args.full:
-        num_samples = 200
-    else:
-        num_samples = 20

### 2020-07-26 ms.tex
simplify repo
change filename convention to hyphen
fix github action versions

--- 2020-05-29 paper/ms.tex
@@
 \begin{document}
-\DTLloaddb{keys_values}{keys_values.csv}
+\DTLloaddb{keys_values}{results/keys-values.csv}
 
-\title{Reconciler: A Workflow for Certifying Computational Research Reproducibility}
+\title{Reconciler: A Workflow for writing Reproducible Computational Research Papers}
 
@@
 				child{node[draw, anchor=west, fill=blue!20]{main.py}}
-				child{node[draw, anchor=west, fill=red!20]{paper}
 				child{node[draw, anchor=west, fill=red!20]{ms.tex}}
-				child{node[draw, anchor=west, fill=red!20]{ms.bib}}
-				};
+				child{node[draw, anchor=west, fill=red!20]{ms.bib}};
 		\end{tikzpicture}
@@
 \begin{figure}[h]
-	\includegraphics[width=\linewidth]{images/image.pdf}
+	\includegraphics[width=\linewidth]{results/image.pdf}
 	\caption{Image example created from results code.}
@@
 	\setlength\tabcolsep{4.2pt}
-	\input{tables/table.tex}
+	\input{results/table.tex}
 \end{table}

### 2020-07-26 ms.tex
start fixing paper

@@
 
-\title{Reconciler: A Workflow for writing Reproducible Computational Research Papers}
+\title{Reconciler: A Workflow for Writing Reproducible Computational Research Papers}
 
@@
 	\end{minipage}
-	\begin{minipage}{0.4\linewidth}
+	\begin{minipage}{0.8\linewidth}
 		\centering
@@
 			\node[draw, rounded corners, above of=localrepo] (remoterepo) {Remote Repo};
-			\node[draw, rounded corners, above left of=remoterepo, fill=blue!20] (builddocker1) {Build Docker};
+			\node[draw, rounded corners, above left=1cm of remoterepo, fill=blue!20] (builddocker1) {Build Docker};
 			\node[draw, rounded corners, above of=builddocker1, fill=red!20] (compilelatex1) {Compile \LaTeX};
-			\node[draw, rounded corners, above right of=compilelatex1, fill=white] (comparison) {Comparison};
-			\node[draw, rounded corners, above right of=remoterepo, fill=blue!20] (builddocker2) {Build Docker};
+			\node[draw, rounded corners, above of=remoterepo, fill=blue!20] (builddocker2) {Build Docker};
 			\node[draw, rounded corners, above of=builddocker2, fill=red!20] (compilelatex2) {Compile \LaTeX};
+			\node[draw, rounded corners, above right=1cm of remoterepo] (arxivrepo) {arXiv Repo};
+			\node[draw, rounded corners, above of=arxivrepo, fill=red!30] (compilelatex3) {Compile \LaTeX};
+			\node[draw, rounded corners, above of=compilelatex2, fill=white] (comparison) {Comparison};
 			\path[draw, ->] (localrepo) -- node[left]{push} (remoterepo);
@@
 			\path[draw, ->] (compilelatex1) |- node[left]{pdf} (comparison);
-			\path[draw, ->] (remoterepo) -| node[right]{checkout} (builddocker2);
+			\path[draw, ->] (remoterepo) -- node[right]{checkout} (builddocker2);
+			\path[draw, ->, dashed] (remoterepo) -| node[right]{checkout} (arxivrepo);
 			\path[draw, ->] (builddocker2) -- node[right]{\LaTeX+results} (compilelatex2);
-			\path[draw, ->] (compilelatex2) |- node[right]{pdf} (comparison);
+			\path[draw, ->, dashed] (arxivrepo) -- node[right]{\LaTeX+results} (compilelatex3);
+			\path[draw, ->] (compilelatex2) -- node[right]{pdf} (comparison);
+			\path[draw, ->, dashed] (compilelatex3) |- node[right]{pdf} (comparison);
 			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_1$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker2) (compilelatex2) (builddocker2.west), label={[black!50]70:$VM_2$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_3$}]{};
+				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_{OS_1}$}]{};
+				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker2) (compilelatex2) (builddocker2.west), label={[black!50]70:$VM_{OS_n}$}]{};
+				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(compilelatex3), label={[black!50]50:$VM_{arxiv}$}]{};
+				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_{comp}$}]{};
 			\end{scope}
@@
 	\end{minipage}
-	\begin{minipage}{0.4\linewidth}
-		\centering
-		\subfloat[]{\begin{tikzpicture}[node distance=1.9cm, minimum height=1cm]
-			\node[draw, rounded corners] (localrepo) {Local Repo};
-			\node[draw, rounded corners, above of=localrepo] (remoterepo) {Remote Repo};
-			\node[draw, rounded corners, above of=remoterepo, fill=blue!20] (builddocker1) {Build Docker};
-			\node[draw, rounded corners, above of=builddocker1, fill=red!20] (compilelatex1) {Compile \LaTeX};
-			\node[draw, rounded corners, above right of=compilelatex1, fill=white] (comparison) {Comparison};
-			\node[draw, rounded corners, below right of=comparison, fill=red!20] (compilelatex2) {Compile \LaTeX};
-			\node[draw, rounded corners, below = 2.8cm of compilelatex2] (arxivrepo) {arXiv Repo};
-			\path[draw, ->] (localrepo) -- node[left]{push} (remoterepo);
-			\path[draw, ->] (remoterepo) -- node[left]{checkout} (builddocker1);
-			\path[draw, ->] (builddocker1) -- node[left]{\LaTeX+results}(compilelatex1);
-			\path[draw, ->] (compilelatex1) |- node[left]{pdf} (comparison);
-			\path[draw, ->] (arxivrepo) -- node[right]{\LaTeX+results} (compilelatex2);
-			\path[draw, ->] (compilelatex2) |- node[right]{pdf} (comparison);
-			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_1$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(compilelatex2), label={[black!50]50:$VM_2$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_3$}]{};
-			\end{scope}
-		\end{tikzpicture}
-		\label{subfig:workflowarxiv}}
-	\end{minipage}
-	\caption{In (a) the template Reconciler file hierarchy is depicted as a file tree directory.
+	\caption{In \protect\subref{subfig:filehierarchy} the template Reconciler file hierarchy is depicted as a file tree directory.
 	Results and \LaTeX\ code reside in the same repository but this is optional.
-	In (b) the proposed Reconciler workflow with the two independent branches is depicted, and in (c) a variation of the Reconciler applied on certifying arXiv papers, where the right branch fetches the results and the \LaTeX\ code from the arXiv servers.
+	In \protect\subref{subfig:workflow} the proposed Reconciler workflow with the $n$ independent branches is depicted one for each VM and the optional branch for certifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
 	Blue denotes results code file or procedure, red denotes \LaTeX\ code file or procedure and gray background denotes that the encapsulated procedures is happening in a VM.
-	Arrows in (b) and (c) denote the data flow direction, complemented by descriptive labels.}
+	Arrows in \protect\subref{subfig:workflow} denote the data flow direction, complemented by descriptive labels, while the dashed arrows on the right denote the optional branch for the arxiv.}
 	\label{fig:filehierarchyworkflow}
@@
 \begin{itemize}
-	\item preprint server (such as arXiv) results reproducibility certification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflowarxiv}.
+	\item preprint server (such as arXiv) results reproducibility certification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}.
 		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the results code.
@@
 # SYNTAX
-make [docker] [ARGS="[--full] [--gpu]"] [GPU="--gpus all"]
-
+make [docker[-gpu]] [ARGS=--full]
 # where [...] denotes an optional argument.
 
-# For example you can choose one of the following:
+# Requires local installation of texlive-full
+# and it populates the figures and tables.
 make
-# Requires local installation of
-# requirements.txt and texlive-full.
-# Takes ~1 minute and populates the figures and table.
-make ARGS="--full --gpu"
-# Requires local installation of
-# requirements.txt and texlive-full.
-# Takes ~1 minute on an NVIDIA Titan X.
+# Requires local installation of texlive-full.
+# and it populates the figures and tables.
+make ARGS=--full
+# Requires local installation of docker
+# and populates the figures and tables.
 make docker
-# Requires local installation of docker.
-# Takes ~1 minute.
-make docker ARGS="--full --gpu" GPU="--gpus all"
 # Requires local installation of nvidia-container-toolkit.
-# Takes ~1 minute on an NVIDIA Titan X.
+make docker-gpu ARGS=--full
+# Restores <repo> in its initial state
+# by removing all figures, tables and downloaded datasets.
 make clean
-# Restores the repo in its initial state by removing
-# all figures, tables and downloaded datasets.
+
 \end{lstlisting}

### 2020-07-26 ms.tex
fix pip in Dockerfile and url link in ms.tex

@@
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
+We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-writing-reproducible-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

### 2020-07-27 ms.tex
change paper title

--- 2020-07-26 ms.tex
@@
 
-\title{Reconciler: A Workflow for Writing Reproducible Computational Research Papers}
+\title{Reconciler: A Template for Reproducible Computational Research Papers}
 
@@
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
+We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-template-for-reproducible-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

### 2020-07-28 main.py
fix reconciler

@@ -16,6 +16,7 @@ if __name__ == '__main__':
     np.random.seed(0)
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
+    parser.add_argument('--use-cuda', default=False, action='store_true')
     parser.add_argument('--cache-dir', default='cache')
     parser.add_argument('--results-dir', default='results')
     args = parser.parse_args()
@@ -23,7 +24,7 @@ if __name__ == '__main__':
         os.mkdir(args.cache_dir)
     if not os.path.exists(args.results_dir):
         os.mkdir(args.results_dir)
-    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+    device = torch.device('cuda' if (torch.cuda.is_available() and args.use_cuda) else 'cpu')
     if args.full:
         num_samples = 200
     else:

### 2020-08-05 ms.tex
extract reproducibility code from ms.tex to Makefile
[2005.12660]

@@
 \usepackage[hyphens]{url}
-\usepackage{hyperref}
 
@@
 	commentstyle=\color{gray}}
-
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
 
@@
 	Previous work in reproducibility focused on providing frameworks to make research reproducible, however fewer work was done on reproducibility certification.
-	We propose the Reconciler, that certifies the reproducibility of computational research papers written in \LaTeX.
-	Two Docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
-	Then the results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
+	We propose the Reconciler, which is a template for writing reproducible computational research papers written in \LaTeX.
+	A predetermined number of docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
+	The previous results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
 	Lastly a third VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
@@
 A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named num\_samples.}, captionpos=b]
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named lr.}, captionpos=b]
 \DTLloaddb{keys_values}{keys_values.csv}
-\DTLfetch{keys_values}{key}{num_samples}{value}
+\DTLfetch{keys_values}{key}{lr}{value}
 \end{lstlisting}
@@
 \begin{itemize}
-	\item number of samples of Fig.~\ref{fig:image} is $\DTLfetch{keys_values}{key}{num_samples}{value}$ and
-	\item the number of columns of Table~\ref{table:table} is $\DTLfetch{keys_values}{key}{num_columns}{value}$.
+	\item the learning rate is $\DTLfetch{keys_values}{key}{lr}{value}$ and
+	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$.
+	\item the validation accuracy of the best model is $\DTLfetch{keys_values}{key}{validation_accuracy_best}{value}$.
 \end{itemize}
@@
 Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
-For example Fig.~\ref{fig:image} depicts the signal:
-\begin{equation}
-	f(t) = \DTLfetch{keys_values}{key}{mu}{value} + \DTLfetch{keys_values}{key}{sigma}{value} * Z(t) + t
-\end{equation}
-
-,where $Z(t)\sim\mathcal{N}$.
-
+For example Fig.~\ref{fig:image} depicts the train and validation loss:
 \begin{figure}[h]

### 2020-08-05 main.py

@@ -5,9 +5,37 @@ import pandas as pd
 import torch
 
 from matplotlib import pyplot as plt
+from torch import nn
+from torch import optim
+from torch.nn import functional as F
+from torch.utils.data import DataLoader
+from torch.utils.data.sampler import SubsetRandomSampler
+from torchvision import transforms
+from torchvision.datasets import CIFAR10
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
+
+
+class CustomModel(nn.Module):
+    def __init__(self):
+        super(CustomModel, self).__init__()
+        self.conv1 = nn.Conv2d(3, 4, 5, 1)
+        self.dropout1 = nn.Dropout2d(0.25)
+        self.dropout2 = nn.Dropout2d(0.5)
+        self.fc1 = nn.Linear(3136, 128)
+        self.fc2 = nn.Linear(128, 10)
+
+    def forward(self, x):
+        x = self.conv1(x)
+        x = self.dropout1(x)
+        x = torch.flatten(x, 1)
+        x = self.fc1(x)
+        x = F.relu(x)
+        x = self.dropout2(x)
+        x = self.fc2(x)
+        return x
+
 
 if __name__ == '__main__':
     torch.manual_seed(0)
@@ -27,29 +55,84 @@ if __name__ == '__main__':
     device = torch.device('cuda' if (torch.cuda.is_available() and args.use_cuda) else 'cpu')
     if args.full:
         num_samples = 200
+        num_epochs = 10
+        train_range = range(40000)
+        validation_range = range(40000, 50000)
+        test_range = range(10000)
     else:
         num_samples = 20
+        num_epochs = 1
+        train_range = range(10)
+        validation_range = range(10)
+        test_range = range(10)
+
+    lr = 0.01
+    batch_size = 64
+    transform = transforms.Compose([transforms.ToTensor(), transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010))])
+    train_dataset = CIFAR10(args.cache_dir, train=True, transform=transform, download=True)
+    validation_dataset = CIFAR10(args.cache_dir, train=True, transform=transform)
+    train_dataloader = DataLoader(train_dataset, batch_size=batch_size, sampler=SubsetRandomSampler(train_range))
[…]

### 2020-08-14 ms.tex
fix

@@
 
-\title{Reconciler: A Template for Reproducible Computational Research Papers}
+\title{Reproducible builds for computational research papers}
 
@@
 \begin{abstract}
-	Previous work in reproducibility focused on providing frameworks to make research reproducible, however fewer work was done on reproducibility certification.
-	We propose the Reconciler, which is a template for writing reproducible computational research papers written in \LaTeX.
-	A predetermined number of docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
+	Previous work in reproducibility focused on providing frameworks to make research reproducible, however without taking in consideration the cost of extra work that needs to be done by the authors.
+	We propose applying the concept of reproducible builds on computational research papers written in \LaTeX.
+	The authors use a template that allows them to verify the reproducibility of their paper locally.
+	The authors can share the reproducibility status of their paper with reviewers using the following procedure.
+	When they push their code to their remote repository a predetermined number of docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
 	The previous results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
-	Lastly a third VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
-	The two builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
-	We release an open source implementation of the Reconciler, that certifies the reproducibility of this paper.
+	Lastly another VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
+	The first builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
+	We release an open source implementation of this procedure and certify the reproducibility of this paper.
 \end{abstract}
@@
 
-We propose the Reconciler workflow, that certifies the reproducibility of computational research papers written in \LaTeX.
-The Reconciler workflow consists of two separate Virtual Machines (VMs) that build and run the Docker container which produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce two pdf files.
-Lastly, a third VM compares the pdf files and certifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.
+We propose reproducible builds that certify the reproducibility of computational research papers written in \LaTeX.
+The workflow consists of multiple separate Virtual Machines (VMs) that build and run the Docker container which produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
+Lastly, another VM compares the pdf files and certifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-template-for-reproducible-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
+We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
@@
 		\begin{enumerate}
-			\item two VMs (builders) independently build and run the Dockerfile of the results code,
+			\item multiple VMs (builders) independently build and run the Dockerfile of the results code,
 			\item the results along with the \LaTeX\ code are used to compile the pdf files,
@@
 Docker usage in the Reconciler provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
-The reason that two independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the certifier VM report the paper as non-reproducible.
+The reason that multiple independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the certifier VM report the paper as non-reproducible.
 

### 2020-08-15 ms.tex
fix Makefile
various fixes

@@
 
-\title{Reproducible builds for computational research papers}
+\title{Reproducible Builds for\\ Computational Research Papers}
 
@@
 	We propose applying the concept of reproducible builds on computational research papers written in \LaTeX.
-	The authors use a template that allows them to verify the reproducibility of their paper locally.
-	The authors can share the reproducibility status of their paper with reviewers using the following procedure.
-	When they push their code to their remote repository a predetermined number of docker containers are built and run in separate Virtual Machines (VMs) reproducing the figures, tables and variables (results) of the paper.
-	The previous results are used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
-	Lastly another VM certifies the research paper as reproducible, if and only if the resulted pdf files are identical.
-	The first builds are needed to enable comparison between different builds of the same source code and any non-deterministic stochasticity would produce different pdf files for different builds, thus making the certifier VM report the paper as non-reproducible.
-	We release an open source implementation of this procedure and certify the reproducibility of this paper.
+	A Makefile allows the authors to verify the reproducibility of their paper locally.
+	The authors may also share the reproducibility status of their paper with reviewers using the following procedure.
+	When a code update is pushed on the remote repository, a predetermined number of Virtual Machines (VMs) build and run the code that reproduces the figures, tables and variables (results) of the paper.
+	These results are then used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
+	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
+	The two builds in each VM are needed to enable comparison between different builds of the same source code.
+	Any non-deterministic stochasticity would produce different pdf files for different builds, thus making the paper non-reproducible.
+	We release an open source implementation of this procedure and verify the reproducibility of this paper.
 \end{abstract}
@@
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms them creating the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but this is not enough to certify its reproducibility.
-A common workflow among researchers for certifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but this is not enough to verify its reproducibility.
+A common workflow among researchers for verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
 
-We propose reproducible builds that certify the reproducibility of computational research papers written in \LaTeX.
+We propose reproducible builds that verify the reproducibility of computational research papers written in \LaTeX.
 The workflow consists of multiple separate Virtual Machines (VMs) that build and run the Docker container which produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
-Lastly, another VM compares the pdf files and certifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.
+Lastly, another VM compares the pdf files and verifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
+We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}} of the Reconciler, that verifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
@@
 	Results and \LaTeX\ code reside in the same repository but this is optional.
-	In \protect\subref{subfig:workflow} the proposed Reconciler workflow with the $n$ independent branches is depicted one for each VM and the optional branch for certifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
+	In \protect\subref{subfig:workflow} the proposed Reconciler workflow with the $n$ independent branches is depicted one for each VM and the optional branch for verifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
 	Blue denotes results code file or procedure, red denotes \LaTeX\ code file or procedure and gray background denotes that the encapsulated procedures is happening in a VM.
@@
 			\item the results along with the \LaTeX\ code are used to compile the pdf files,
-			\item the pdf files are sent to a third VM (certifier),
-			\item the certifier VM certifies the research paper as reproducible if and only if the pdf files are the same using bit comparison.
+			\item the pdf files are sent to a third VM (verifier),
+			\item the verifier VM verifies the research paper as reproducible if and only if the pdf files are the same using bit comparison.
 		\end{enumerate}
@@
 Docker usage in the Reconciler provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
-The reason that multiple independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the certifier VM report the paper as non-reproducible.
+The reason that multiple independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the verifier VM report the paper as non-reproducible.
 
@@
 \begin{itemize}
-	\item preprint server (such as arXiv) results reproducibility certification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}.
+	\item preprint server (such as arXiv) results reproducibility verification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}.
 		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the results code.
-	\item one branch local certification where the last VM returns the hash of the resulted pdf enabling reviewers certifying the pdf output of their local branch.
+	\item one branch local verification where the last VM returns the hash of the resulted pdf enabling reviewers verifying the pdf output of their local branch.
 		Using the previous workflow the Reconciler could also be used for regression testing and debugging, to ensure that changes to the code do not alter the results.
@@
 
-Regarding research that is computational costly or when reproducibility certification is required from the first stages of the research, the Reconciler template provides a debug flag that certifies the reproducibility of a smaller scale of the computational experiment.
+Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the Reconciler template provides a debug flag that verifies the reproducibility of a smaller scale of the computational experiment.
 E.g.\ the debug flag in the concept of neural networks could set the number of epochs and number of training samples to a low value.
@@
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-The Reconciler provides a simple solution in certifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
+The Reconciler provides a simple solution in verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
 Future work needs to be done regarding improving the use of the Reconciler on reproducibility on the following:
@@
 \section{Conclusion}
-Automating research reproducibility certification is becoming more important due to the increasing research output that has been observed the last few years.
+Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed the last few years.
 Few works were done on this area, mostly proposing trust on an external third party.
-The Reconciler certifies research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.
+The Reconciler verifies research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.
 

### 2020-08-15 main.py

@@ -11,7 +11,7 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import CIFAR10
+from torchvision.datasets import MNIST
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
@@ -20,10 +20,10 @@ plt.rcParams['savefig.format'] = 'pdf'
 class CustomModel(nn.Module):
     def __init__(self):
         super(CustomModel, self).__init__()
-        self.conv1 = nn.Conv2d(3, 4, 5, 1)
+        self.conv1 = nn.Conv2d(1, 4, 5, 1)
         self.dropout1 = nn.Dropout2d(0.25)
         self.dropout2 = nn.Dropout2d(0.5)
-        self.fc1 = nn.Linear(3136, 128)
+        self.fc1 = nn.Linear(2304, 128)
         self.fc2 = nn.Linear(128, 10)
 
     def forward(self, x):
@@ -38,20 +38,20 @@ class CustomModel(nn.Module):
 
 
 if __name__ == '__main__':
+    # Set random seeds.
+    np.random.seed(0)
     torch.manual_seed(0)
+    torch.cuda.manual_seed_all(0)
     torch.backends.cudnn.deterministic = True
     torch.backends.cudnn.benchmark = False
-    np.random.seed(0)
+
+    # Parse arguments.
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
     parser.add_argument('--use-cuda', default=False, action='store_true')
     parser.add_argument('--cache-dir', default='cache')
     parser.add_argument('--results-dir', default='results')
     args = parser.parse_args()
-    if not os.path.exists(args.cache_dir):
-        os.mkdir(args.cache_dir)
-    if not os.path.exists(args.results_dir):
-        os.mkdir(args.results_dir)
     device = torch.device('cuda' if (torch.cuda.is_available() and args.use_cuda) else 'cpu')
     if args.full:
         num_samples = 200
@@ -68,9 +68,9 @@ if __name__ == '__main__':
 
     lr = 0.01
     batch_size = 64
-    transform = transforms.Compose([transforms.ToTensor(), transforms.Normalize((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010))])
-    train_dataset = CIFAR10(args.cache_dir, train=True, transform=transform, download=True)
[…]

### 2020-08-15 main.py
fix gitignores

@@ -49,18 +49,16 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
     parser.add_argument('--use-cuda', default=False, action='store_true')
-    parser.add_argument('--cache-dir', default='cache')
-    parser.add_argument('--results-dir', default='results')
+    parser.add_argument('--cache-dir')
+    parser.add_argument('--results-dir')
     args = parser.parse_args()
     device = torch.device('cuda' if (torch.cuda.is_available() and args.use_cuda) else 'cpu')
     if args.full:
-        num_samples = 200
         num_epochs = 10
         train_range = range(40000)
         validation_range = range(40000, 50000)
         test_range = range(10000)
     else:
-        num_samples = 20
         num_epochs = 1
         train_range = range(10)
         validation_range = range(10)

### 2020-08-15 main.py
fix Makefile and improve main.py

@@ -120,16 +120,21 @@ if __name__ == '__main__':
     plt.plot(train_loss_array)
     plt.plot(validation_loss_array)
     plt.grid(True)
-    plt.xlabel('Loss')
-    plt.ylabel('Epochs')
+    plt.xlabel('Epochs')
+    plt.ylabel('Loss')
     plt.autoscale(enable=True, axis='x', tight=True)
+    plt.ylim([0, 3])
+    plt.legend(['Train', 'Validation'])
     plt.savefig(f'{args.results_dir}/image')
     plt.close()
 
     # Create tables.
     table = [train_loss_array[-1], validation_loss_array[-1], validation_accuracy_best]
-    df = pd.DataFrame(table)
-    df.to_latex(f'{args.results_dir}/table.tex', float_format="%.2f")
+    index = ['Train Loss', 'Val Loss', 'Val Acc']
+    columns = ['MNIST']
+    df = pd.DataFrame(table, index=index, columns=columns)
+    df.index.names = ['Metric']
+    df.to_latex(f'{args.results_dir}/table.tex', float_format="%.2f", bold_rows=True)
 
     # Create variables.
     df = pd.DataFrame({'key': ['lr', 'batch_size', 'validation_accuracy_best'], 'value': [lr, batch_size, validation_accuracy_best]})

### 2020-08-15 ms.tex
improve paper

@@
 \usepackage[hyphens]{url}
+\usepackage{hyperref}
 
@@
 	Previous work in reproducibility focused on providing frameworks to make research reproducible, however without taking in consideration the cost of extra work that needs to be done by the authors.
-	We propose applying the concept of reproducible builds on computational research papers written in \LaTeX.
+	We propose applying the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
 	A Makefile allows the authors to verify the reproducibility of their paper locally.
@@
 A research paper is considered reproducible when reviewers are able to reproduce its results, given the data and experimental procedure.
-More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms them creating the figures, tables and variables of the paper.
+More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
 Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but this is not enough to verify its reproducibility.
-A common workflow among researchers for verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+The use of a common template for verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
 
-We propose reproducible builds that verify the reproducibility of computational research papers written in \LaTeX.
-The workflow consists of multiple separate Virtual Machines (VMs) that build and run the Docker container which produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
-Lastly, another VM compares the pdf files and verifies the research paper as reproducible, if and only if the pdf files are identical bit by bit.
+We propose the use of `reproducible builds' (RBs) that verify the reproducibility of computational research papers written in \LaTeX.
+The workflow consists of multiple Virtual Machines (VMs) that execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
+The previous procedure is executed twice and the research paper is verified as reproducible, if and only if the resulting pdf files are identical.
 
-We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}} of the Reconciler, that verifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
-We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
+We provide a template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
+We use Python~\cite{van2007python} for producing the results, however other scientific oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
 
@@
 
-\section{The Reconciler Workflow}
+\section{Reproducible Builds}
 
@@
 	\end{minipage}
-	\caption{In \protect\subref{subfig:filehierarchy} the template Reconciler file hierarchy is depicted as a file tree directory.
+	\caption{In \protect\subref{subfig:filehierarchy} the RBs template file hierarchy is depicted as a file tree directory.
 	Results and \LaTeX\ code reside in the same repository but this is optional.
-	In \protect\subref{subfig:workflow} the proposed Reconciler workflow with the $n$ independent branches is depicted one for each VM and the optional branch for verifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
+	In \protect\subref{subfig:workflow} the proposed workflow with the $n$ independent branches is depicted one for each VM and the optional branch for verifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
 	Blue denotes results code file or procedure, red denotes \LaTeX\ code file or procedure and gray background denotes that the encapsulated procedures is happening in a VM.
@@
 
-The Reconciler workflow can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container.
+The proposed workflow can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
@@
 
-A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:filehierarchy}) is used in this paper however this is optional, as the Reconciler only needs to know the directories of the main files of the \LaTeX\ and results code through its configuration file \textit{workflow.yml}.
-The Reconciler workflow fits in the researcher workflow in the following way (as also shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}):
+A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:filehierarchy}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and results code through its configuration file \textit{workflow.yml}.
+The workflow fits in the researcher workflow in the following way (as also shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}):
 \begin{enumerate}
 	\item the researcher writes or edits code,
-	\item the researcher commits and pushes the changes to the remote repository, which triggers the Reconciler workflow:
+	\item the researcher commits and pushes the changes to the remote repository, which triggers the workflow:
 		\begin{enumerate}
@@
 			\item the pdf files are sent to a third VM (verifier),
-			\item the verifier VM verifies the research paper as reproducible if and only if the pdf files are the same using bit comparison.
+			\item the verifier VM verifies the research paper as reproducible if and only if the pdf files are identical.
 		\end{enumerate}
@@
 
-Docker usage in the Reconciler provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
+Docker usage in RBs provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
 The reason that multiple independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the verifier VM report the paper as non-reproducible.
@@
 
-Variations of the Reconciler main workflow include:
+Variations of the RBs main workflow include:
 \begin{itemize}
@@
 	\item one branch local verification where the last VM returns the hash of the resulted pdf enabling reviewers verifying the pdf output of their local branch.
-		Using the previous workflow the Reconciler could also be used for regression testing and debugging, to ensure that changes to the code do not alter the results.
+		Using the previous workflow RBs could also be used for regression testing and debugging, to ensure that changes to the code do not alter the results.
 \end{itemize}
@@
 \subsection{Technical implementation}
-A template of the Reconciler is available using Github Actions and is applied on the arXiv version of this paper.
+A template of the RBs is available using Github Actions and is applied on the arXiv version of this paper.
 The builder VMs use different versions of Ubuntu (16.04 and 18.04) and pull a docker image for building \LaTeX\ from DockerHub.
 
-Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the Reconciler template provides a debug flag that verifies the reproducibility of a smaller scale of the computational experiment.
+Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the template provides a debug flag that verifies the reproducibility of a smaller scale of the computational experiment.
 E.g.\ the debug flag in the concept of neural networks could set the number of epochs and number of training samples to a low value.
-Some possible executions that the Reconciler provides are summarized in the following syntax:
+Some possible executions that RBs provide are summarized in the following syntax:
 \begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
@@
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-The Reconciler provides a simple solution in verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
-Future work needs to be done regarding improving the use of the Reconciler on reproducibility on the following:
-\begin{enumerate}
-	\item making scientific programming libraries reproducible,
-	\item regarding infrastructure: the use of VMs that support CUDA to enable the application of the Reconciler on deep neural network research.
-\end{enumerate}
+RBs provide a simple solution in verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
 
@@
 Few works were done on this area, mostly proposing trust on an external third party.
-The Reconciler verifies research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.
+RBs verify research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.
 
@@
 \begin{itemize}
-	\item the learning rate is $\DTLfetch{keys_values}{key}{lr}{value}$ and
-	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$.
-	\item the validation accuracy of the best model is $\DTLfetch{keys_values}{key}{validation_accuracy_best}{value}$.
+	\item the learning rate is $\DTLfetch{keys_values}{key}{lr}{value}$,
+	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
+	\item the validation accuracy of the best model is $\DTLfetch{keys_values}{key}{validation_accuracy_best}{value}\%$.
 \end{itemize}

### 2020-08-15 main.py

@@ -130,12 +130,12 @@ if __name__ == '__main__':
 
     # Create tables.
     table = [train_loss_array[-1], validation_loss_array[-1], validation_accuracy_best]
-    index = ['Train Loss', 'Val Loss', 'Val Acc']
+    index = ['Train Loss', 'Val Loss', 'Val Acc(%)']
     columns = ['MNIST']
     df = pd.DataFrame(table, index=index, columns=columns)
     df.index.names = ['Metric']
     df.to_latex(f'{args.results_dir}/table.tex', float_format="%.2f", bold_rows=True)
 
     # Create variables.
-    df = pd.DataFrame({'key': ['lr', 'batch_size', 'validation_accuracy_best'], 'value': [lr, batch_size, validation_accuracy_best]})
-    df.to_csv(f'{args.results_dir}/keys-values.csv', index=False, float_format='%.1f')
+    df = pd.DataFrame({'key': ['lr', 'batch_size', 'validation_accuracy_best'], 'value': [lr, str(int(batch_size)), validation_accuracy_best]})
+    df.to_csv(f'{args.results_dir}/keys-values.csv', index=False, float_format='%.2f')

### 2020-08-15 ms.tex
improve abstract

@@
 	We propose applying the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
-	A Makefile allows the authors to verify the reproducibility of their paper locally.
-	The authors may also share the reproducibility status of their paper with reviewers using the following procedure.
-	When a code update is pushed on the remote repository, a predetermined number of Virtual Machines (VMs) build and run the code that reproduces the figures, tables and variables (results) of the paper.
-	These results are then used during the \LaTeX\ compilation in each VM, to produce corresponding pdf files.
+	The reproducibility of a paper can be verified locally with the use of a Makefile and remotely through a workflow that uses Virtual Machines (VMs) in the cloud.
+	The verifier (author or reviewer) may execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce corresponding pdf files.
 	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
-	The two builds in each VM are needed to enable comparison between different builds of the same source code.
-	Any non-deterministic stochasticity would produce different pdf files for different builds, thus making the paper non-reproducible.
-	We release an open source implementation of this procedure and verify the reproducibility of this paper.
+	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
+	We release an open source template of RBs and use it to write and verify the reproducibility of this paper.
 \end{abstract}

### 2020-08-16 ms.tex
improve abstract and main text

@@
 \begin{abstract}
-	Previous work in reproducibility focused on providing frameworks to make research reproducible, however without taking in consideration the cost of extra work that needs to be done by the authors.
-	We propose applying the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
-	The reproducibility of a paper can be verified locally with the use of a Makefile and remotely through a workflow that uses Virtual Machines (VMs) in the cloud.
-	The verifier (author or reviewer) may execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce corresponding pdf files.
+	Previous work in reproducibility focused on providing frameworks to help writing reproducible research papers, however without taking in consideration the cost of extra work that needs to be done by the authors.
+	We propose a template that applies the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
+	The template provides a Makefile that allows the verifier (author or reviewer) to execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce corresponding pdf files.
 	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
 	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
+	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
 	We release an open source template of RBs and use it to write and verify the reproducibility of this paper.
@@
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but this is not enough to verify its reproducibility.
-The use of a common template for verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but it is not enough to verify its reproducibility.
+The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
 
 We propose the use of `reproducible builds' (RBs) that verify the reproducibility of computational research papers written in \LaTeX.
-The workflow consists of multiple Virtual Machines (VMs) that execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
+The template consists of a Makefile that allows the verifier (author or reviewer) to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
 The previous procedure is executed twice and the research paper is verified as reproducible, if and only if the resulting pdf files are identical.
+This procedure can be executed either locally in the verifier machine or remotely in Virtual Machines (VMs) in the cloud.
 
 We provide a template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
-We use Python~\cite{van2007python} for producing the results, however other scientific oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
+We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
 

### 2020-08-16 ms.tex
improve main text

@@
 
-\begin{figure*}[!t]
-	\begin{minipage}{0.2\linewidth}
+\begin{figure}[!t]
 	\centering
-		\subfloat[]{\begin{tikzpicture}[%
-				grow via three points={one child at (0.5,-0.7) and
-				two children at (0.5,-0.7) and (0.5,-1.4)},
+	\begin{tikzpicture}[%
+			grow via three points={one child at (0.5,-0.7) and two children at (0.5,-0.7) and (0.5,-1.4)},
 			edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
-				\node[draw]{root}
-				child{node[draw, anchor=west]{workflow.yml}}
-				child{node[draw, anchor=west]{Makefile}}
-				child{node[draw, anchor=west, fill=blue!20]{Dockerfile}}
-				child{node[draw, anchor=west, fill=blue!20]{main.py}}
-				child{node[draw, anchor=west, fill=red!20]{ms.tex}}
-				child{node[draw, anchor=west, fill=red!20]{ms.bib}};
+			\node[draw](root){root}
+			child{node[draw, anchor=west](makefile){Makefile}}
+			child{node[draw, anchor=west, fill=red!20](tex){ms.tex}}
+			child{node[draw, anchor=west, fill=red!20](bib){ms.bib}}
+			child{node[draw, anchor=west, fill=blue!20](py){main.py}}
+			child{node[draw, anchor=west, fill=blue!20](venv){.venv}}
+			child{node[draw, anchor=west, fill=blue!20](dockerfile){Dockerfile}};
+			\begin{scope}[on background layer]
+				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=4pt, fit=(root) (dockerfile)]{};
+				\node[draw, rounded corners, dashed, fill=gray!70, inner sep=2pt, fit=(py) (dockerfile)](code){};
+				\node[draw, rounded corners, dashed, fill=gray!70, inner sep=2pt, fit=(tex) (bib)](paper){};
+			\end{scope}
+			\node[draw, right=2cm of code, fill=white] (results) {results};
+			\path[draw, ->] (code) -- node[above]{venv/docker} (results);
+			\node[draw, right=4cm of paper, fill=white] (pdf) {pdf};
+			\path[draw, ->] (results) |- (pdf);
+			\path[draw, ->] (paper) -- node[above]{docker} (pdf);
 	\end{tikzpicture}
-		\label{subfig:filehierarchy}}
-	\end{minipage}
-	\begin{minipage}{0.8\linewidth}
-		\centering
-		\subfloat[]{\begin{tikzpicture}[node distance=1.9cm, minimum height=1cm]
-			\node[draw, rounded corners] (localrepo) {Local Repo};
-			\node[draw, rounded corners, above of=localrepo] (remoterepo) {Remote Repo};
-			\node[draw, rounded corners, above left=1cm of remoterepo, fill=blue!20] (builddocker1) {Build Docker};
-			\node[draw, rounded corners, above of=builddocker1, fill=red!20] (compilelatex1) {Compile \LaTeX};
-			\node[draw, rounded corners, above of=remoterepo, fill=blue!20] (builddocker2) {Build Docker};
-			\node[draw, rounded corners, above of=builddocker2, fill=red!20] (compilelatex2) {Compile \LaTeX};
-			\node[draw, rounded corners, above right=1cm of remoterepo] (arxivrepo) {arXiv Repo};
-			\node[draw, rounded corners, above of=arxivrepo, fill=red!30] (compilelatex3) {Compile \LaTeX};
-			\node[draw, rounded corners, above of=compilelatex2, fill=white] (comparison) {Comparison};
-			\path[draw, ->] (localrepo) -- node[left]{push} (remoterepo);
-			\path[draw, ->] (remoterepo) -| node[left]{checkout} (builddocker1);
-			\path[draw, ->] (builddocker1) -- node[left]{\LaTeX+results}(compilelatex1);
-			\path[draw, ->] (compilelatex1) |- node[left]{pdf} (comparison);
-			\path[draw, ->] (remoterepo) -- node[right]{checkout} (builddocker2);
-			\path[draw, ->, dashed] (remoterepo) -| node[right]{checkout} (arxivrepo);
-			\path[draw, ->] (builddocker2) -- node[right]{\LaTeX+results} (compilelatex2);
-			\path[draw, ->, dashed] (arxivrepo) -- node[right]{\LaTeX+results} (compilelatex3);
-			\path[draw, ->] (compilelatex2) -- node[right]{pdf} (comparison);
-			\path[draw, ->, dashed] (compilelatex3) |- node[right]{pdf} (comparison);
-			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker1) (compilelatex1) (builddocker1.west), label={[black!50]110:$VM_{OS_1}$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(builddocker2) (compilelatex2) (builddocker2.west), label={[black!50]70:$VM_{OS_n}$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(compilelatex3), label={[black!50]50:$VM_{arxiv}$}]{};
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=3pt, fit=(comparison), label={[black!50]above:$VM_{comp}$}]{};
-			\end{scope}
-		\end{tikzpicture}
-		\label{subfig:workflow}}
-	\end{minipage}
-	\caption{In \protect\subref{subfig:filehierarchy} the RBs template file hierarchy is depicted as a file tree directory.
-	Results and \LaTeX\ code reside in the same repository but this is optional.
-	In \protect\subref{subfig:workflow} the proposed workflow with the $n$ independent branches is depicted one for each VM and the optional branch for verifying arXiv papers, where the branch fetches the results and the \LaTeX\ code from the arXiv servers.
-	Blue denotes results code file or procedure, red denotes \LaTeX\ code file or procedure and gray background denotes that the encapsulated procedures is happening in a VM.
-	Arrows in \protect\subref{subfig:workflow} denote the data flow direction, complemented by descriptive labels, while the dashed arrows on the right denote the optional branch for the arxiv.}
+	\caption{In this figure the RBs template file hierarchy is depicted in the light gray background along with the flow of pdf generation.
+	Blue denotes results code file, red denotes \LaTeX\ code file and dark gray background that the encapsulated files are used for a subsequent step.
+	Arrows denote the data flow direction, complemented by descriptive labels.}
 	\label{fig:filehierarchyworkflow}
-\end{figure*}
+\end{figure}
 
-The proposed workflow can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container.
+The proposed template can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container or a virtual environment.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
@@
 
-A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:filehierarchy}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and results code through its configuration file \textit{workflow.yml}.
-The workflow fits in the researcher workflow in the following way (as also shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}):
+A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and `results code' during its creation by the template.
+The template fits in the researcher workflow in the following way:
 \begin{enumerate}
@@
 		\begin{enumerate}
-			\item multiple VMs (builders) independently build and run the Dockerfile of the results code,
+			\item multiple VMs (builders) independently build and run the Dockerfile of the `results code',
 			\item the results along with the \LaTeX\ code are used to compile the pdf files,
@@
 \begin{itemize}
-	\item preprint server (such as arXiv) results reproducibility verification shown in Fig.~\ref{fig:filehierarchyworkflow}\subref{subfig:workflow}.
-		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the results code.
+	\item preprint server (such as arXiv) results reproducibility verification shown in Fig.~\ref{fig:filehierarchyworkflow}.
+		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the `results code'.
 	\item one branch local verification where the last VM returns the hash of the resulted pdf enabling reviewers verifying the pdf output of their local branch.
@@
 \section{APPENDIX - Improving Computational Research Reproducibility}
-This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the results code Programming language.
+This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the `results code' Programming language.
 A common culprit of reproducibility using \LaTeX\ is the time-date metadata of pdf output which can be disabled using the following into the \textit{.tex} code after the preamble:
@@
 A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a results code and getting the value of a key named lr.}, captionpos=b]
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a `results code' and getting the value of a key named lr.}, captionpos=b]
 \DTLloaddb{keys_values}{keys_values.csv}
@@
 
-For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the results code:
+For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the `results code':
 \begin{itemize}
@@
 
-Regarding the results code for Python random seeds need to be set to a specific value such as:
+Regarding the `results code' for Python random seeds need to be set to a specific value such as:
 \begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
@@
 	\includegraphics[width=\linewidth]{results/image.pdf}
-	\caption{Image example created from results code.}
+	\caption{Image example created from `results code'.}
 	\label{fig:image}
@@
 	\centering
-	\caption{Table example created from results code.}
+	\caption{Table example created from `results code'.}
 	\label{table:table}

### 2020-08-17 ms.tex
fix main text

@@
 	We propose a template that applies the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
-	The template provides a Makefile that allows the verifier (author or reviewer) to execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce corresponding pdf files.
+	The template provides a Makefile that allows the verifier (author or reviewer) to execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce a pdf.
 	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
@@
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper helps in increasing the credibility of the research results but it is not enough to verify its reproducibility.
+Open sourcing the code and the raw data of a computational research paper helps increasing its reproducibility confidence but it is not enough to verify it.
 The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
@@
 We propose the use of `reproducible builds' (RBs) that verify the reproducibility of computational research papers written in \LaTeX.
-The template consists of a Makefile that allows the verifier (author or reviewer) to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce pdf files.
+The template consists of a Makefile that allows the verifier (author or reviewer) to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce a pdf.
 The previous procedure is executed twice and the research paper is verified as reproducible, if and only if the resulting pdf files are identical.
@@
 
-We provide a template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
@@
 	\item `\LaTeX\ code' as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the research paper,
-	\item `results code' as the files containing the scientific-oriented programming language code that produces the results (\textit{*.py} files) and
+	\item `results code' as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the results and
 	\item `code' as both the `\LaTeX\ code' and `results code'.
@@
 	\end{tikzpicture}
-	\caption{In this figure the RBs template file hierarchy is depicted in the light gray background along with the flow of pdf generation.
-	Blue denotes results code file, red denotes \LaTeX\ code file and dark gray background that the encapsulated files are used for a subsequent step.
-	Arrows denote the data flow direction, complemented by descriptive labels.}
+	\caption{In this figure the RBs template file hierarchy is depicted in the light gray background and the arrows denote the data flow direction for the pdf generation, complemented by descriptive labels.
+	Blue denotes `results code' file, red denotes `\LaTeX\ code' file and the dark gray background that the encapsulated files are used for a subsequent step.}
 	\label{fig:filehierarchyworkflow}
@@
 
-The proposed template can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the results code can be executed within a Docker container or a virtual environment.
+The proposed template can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.

### 2020-08-18 ms.tex
improve main text

@@
 \begin{abstract}
-	Previous work in reproducibility focused on providing frameworks to help writing reproducible research papers, however without taking in consideration the cost of extra work that needs to be done by the authors.
-	We propose a template that applies the concept of `reproducible builds' (RBs) on computational research papers written in \LaTeX.
-	The template provides a Makefile that allows the verifier (author or reviewer) to execute the code that reproduces the figures, tables and variables (results) of the paper that are then used during the \LaTeX\ compilation, to produce a pdf.
+	Previous work in reproducibility focused on providing frameworks to help writing reproducible research papers, however without taking in consideration the cost of extra work by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
+	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
+	The template provides a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
 	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
@@
 	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
-	We release an open source template of RBs and use it to write and verify the reproducibility of this paper.
+	We release an open source template of `reproducible builds' (RBs) and use it to write and verify the reproducibility of this paper.
 \end{abstract}
@@
 
-We propose the use of `reproducible builds' (RBs) that verify the reproducibility of computational research papers written in \LaTeX.
-The template consists of a Makefile that allows the verifier (author or reviewer) to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce a pdf.
+We propose a template that uses the concept of `reproducible builds' (RBs) to verify the reproducibility of computational research papers written in \LaTeX.
+The template consists of a Makefile that allows the verifier to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce a pdf.
 The previous procedure is executed twice and the research paper is verified as reproducible, if and only if the resulting pdf files are identical.
@@
 
-\section{Reproducible Builds}
+\section{Reproducible Builds Template}
 
@@
 	\item the researcher writes or edits code,
+	\item the researcher verifies the reproducibility of the paper locally,
 	\item the researcher commits and pushes the changes to the remote repository, which triggers the workflow:
 		\begin{enumerate}
-			\item multiple VMs (builders) independently build and run the Dockerfile of the `results code',
+			\item two VMs (builders) execute the `results code',
 			\item the results along with the \LaTeX\ code are used to compile the pdf files,
-			\item the pdf files are sent to a third VM (verifier),
-			\item the verifier VM verifies the research paper as reproducible if and only if the pdf files are identical.
+			\item the pdf files are sent to another VM (verifier), which verifies the research paper as reproducible if and only if the pdf files are identical.
 		\end{enumerate}
@@
 Docker usage in RBs provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
-The reason that multiple independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the verifier VM report the paper as non-reproducible.
+The reason that two independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the verifier VM report the paper as non-reproducible.
 
@@
 \begin{itemize}
-	\item preprint server (such as arXiv) results reproducibility verification shown in Fig.~\ref{fig:filehierarchyworkflow}.
+	\item preprint server (such as arXiv) results reproducibility verification.
 		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the `results code'.
@@
 A template of the RBs is available using Github Actions and is applied on the arXiv version of this paper.
-The builder VMs use different versions of Ubuntu (16.04 and 18.04) and pull a docker image for building \LaTeX\ from DockerHub.
+The builder VMs use different versions of Ubuntu (18.04 and 20.04) and pull a docker image for building \LaTeX\ from DockerHub.
 
-Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the template provides a debug flag that verifies the reproducibility of a smaller scale of the computational experiment.
-E.g.\ the debug flag in the concept of neural networks could set the number of epochs and number of training samples to a low value.
+Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the experiment.
+E.g.\ the debug flag in the field of neural networks could set the number of epochs and number of training samples to a low value.
 Some possible executions that RBs provide are summarized in the following syntax:
 \begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
-# SYNTAX
-make [docker[-gpu]] [ARGS=--full]
-# where [...] denotes an optional argument.
 
-# Requires local installation of texlive-full
-# and it populates the figures and tables.
-make
-# Requires local installation of texlive-full.
-# and it populates the figures and tables.
-make ARGS=--full
-# Requires local installation of docker
-# and populates the figures and tables.
-make docker
-# Requires local installation of nvidia-container-toolkit.
-make docker-gpu ARGS=--full
-# Restores <repo> in its initial state
-# by removing all figures, tables and downloaded datasets.
-make clean
+make [OPTION] [ARGS=--full] [GPU='--gpus all']
 
+OPTIONS
+# (or empty OPTION) Generate pdf with results from venv.
+ms.pdf
+# Verify venv paper reproducibility.
+venv-verify
+# Generate pdf with results from docker.
+docker
+# Verify docker paper reproducibility.
+docker-verify
+# Remove cache, results, venv directories and tex aux files.
+clean
+# Show help.
+help
 \end{lstlisting}
@@
 RBs provide a simple solution in verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
+Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
 
@@
 \section{APPENDIX - Improving Computational Research Reproducibility}
-This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the `results code' Programming language.
+This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the `results code' programming language.
+For demonstration purposes we train and test a simple neural network on the MNIST~\cite{lecun2010mnist} dataset with PyTorch~\cite{paszke2019pytorch}.
+
 A common culprit of reproducibility using \LaTeX\ is the time-date metadata of pdf output which can be disabled using the following into the \textit{.tex} code after the preamble:

### 2020-08-19 ms.tex
improve text

@@
 \begin{abstract}
-	Previous work in reproducibility focused on providing frameworks to help writing reproducible research papers, however without taking in consideration the cost of extra work by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
+	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the extra work that needs to be done by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
 	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
-	The template provides a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
-	The previous procedure is completed twice and the research paper is verified as reproducible, if and only if the resulted pdf files are identical.
+	The template contains a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
+	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the resulted pdf files are identical.
 	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
@@
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper helps increasing its reproducibility confidence but it is not enough to verify it.
+Open sourcing the code and the raw data of a computational research paper helps increasing the confidence of its reproducibility but it is not enough to verify it.
 The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
@@
 
-The proposed template can be applied on computational research papers that are written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
+The proposed template can be applied on computational research papers written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.

### 2020-08-20 ms.tex
improve text

@@
 \begin{abstract}
-	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the extra work that needs to be done by the authors to make their paper reproducible and by the reviewers to verify the paper's reproducibility.
+	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the extra work that needs to be done by the author to make his paper reproducible and by the reviewer to verify the paper's reproducibility.
 	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
 	The template contains a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
-	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the resulted pdf files are identical.
+	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the pdf files are identical.
 	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
 	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
-	We release an open source template of `reproducible builds' (RBs) and use it to write and verify the reproducibility of this paper.
+	We release an open source template of \textit{reproducible builds} (RBs) and use it to write and verify the reproducibility of this paper.
 \end{abstract}
@@
 \section{Introduction}
-A research paper is considered reproducible when reviewers are able to reproduce its results, given the data and experimental procedure.
+A research paper is considered reproducible when any reviewer is able to reproduce its results, given the data and experimental procedure.
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper helps increasing the confidence of its reproducibility but it is not enough to verify it.
-The use of a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+Open sourcing the code and the raw data of a computational research paper increases its reproducibility confidence but it is not enough to verify it.
+Using a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
 
-We propose a template that uses the concept of `reproducible builds' (RBs) to verify the reproducibility of computational research papers written in \LaTeX.
+We propose a template that uses the concept of \textit{reproducible builds} (RBs) to verify the reproducibility of computational research papers written in \LaTeX.
 The template consists of a Makefile that allows the verifier to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce a pdf.
@@
 \begin{itemize}
-	\item `paper' as a computational research paper,
-	\item `results' as the figures, tables and variables that are shown in the paper,
-	\item `\LaTeX\ code' as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the research paper,
-	\item `results code' as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the results and
-	\item `code' as both the `\LaTeX\ code' and `results code'.
+	\item \textit{paper} as a computational research paper,
+	\item \textit{results} as the figures, tables and variables that are shown in the paper,
+	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the research paper,
+	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the results and
+	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code}.
+	\item \textit{author} as the author or authors of the \textit{paper},
+	\item \textit{reviewer} as the reviewer of the \textit{paper},
 \end{itemize}
@@
 	\end{tikzpicture}
-	\caption{In this figure the RBs template file hierarchy is depicted in the light gray background and the arrows denote the data flow direction for the pdf generation, complemented by descriptive labels.
-	Blue denotes `results code' file, red denotes `\LaTeX\ code' file and the dark gray background that the encapsulated files are used for a subsequent step.}
+	\caption{The RBs template file hierarchy is depicted in the light gray background and the arrows denote the data flow towards generating the pdf.
+	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background files that are used for a subsequent step.}
 	\label{fig:filehierarchyworkflow}
@@
 
-The proposed template can be applied on computational research papers written in \LaTeX~\cite{lamport1994latex} and the `results code' can be executed within a Docker container or a virtual environment.
-\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible science~\cite{boettiger2015introduction}.
-The corresponding Dockerfile can be provided by the researcher or generated by tools such as containerit~\cite{nust2019containerit}.
+The proposed template can be applied on computational research papers written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} can be executed within a Docker container or a virtual environment.
+\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
+The corresponding Dockerfile can be provided by the \textit{author} or generated by tools such as containerit~\cite{nust2019containerit}.
 
-A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and `results code' during its creation by the template.
-The template fits in the researcher workflow in the following way:
+A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation by the template.
+The template fits in the research writing and reproducibility verificatrion in the following way:
 \begin{enumerate}
-	\item the researcher writes or edits code,
-	\item the researcher verifies the reproducibility of the paper locally,
-	\item the researcher commits and pushes the changes to the remote repository, which triggers the workflow:
+	\item the \textit{author} writes or edits code in his local repository,
+	\item the \textit{author} may verify the reproducibility of the paper locally,
+	\item the \textit{author} may push the change to the remote repository, which optionally triggers the remote reproducibility verification:
 		\begin{enumerate}
-			\item two VMs (builders) execute the `results code',
-			\item the results along with the \LaTeX\ code are used to compile the pdf files,
+			\item two VMs (builders) execute the \textit{results code},
+			\item the results along with the \textit{\LaTeX\ code} are used to compile the pdf files,
 			\item the pdf files are sent to another VM (verifier), which verifies the research paper as reproducible if and only if the pdf files are identical.
 		\end{enumerate}
+	\item the \textit{reviewer} can check the remote reproducibility verifcation or if not available locally verify the reproducibility in his own machine.
 \end{enumerate}
@@
 
-Additional constraints could be imposed in the VMs such as disallowing images in the code and monitoring the network connections of the code to ensure that results are generated from the code and not fetching them from an external source.
-Alternatively the code could just be open source to enable reviewers inspect the result generation procedure.
+Additional constraints could be imposed in the VMs such as disallowing image files in the code and monitoring the network connections of the \textit{code} to help the \textit{reviewer} check whether the results are generated from the \textit{code} and are not fetched from an external source.
 
-Variations of the RBs main workflow include:
+Other potential uses of the RBs template include:
 \begin{itemize}
-	\item preprint server (such as arXiv) results reproducibility verification.
-		The difference with the main workflow is that one of the VMs checkouts the \LaTeX\ code and the results from the arXiv server instead of executing the `results code'.
-	\item one branch local verification where the last VM returns the hash of the resulted pdf enabling reviewers verifying the pdf output of their local branch.
-		Using the previous workflow RBs could also be used for regression testing and debugging, to ensure that changes to the code do not alter the results.
+	\item Preprint server (such as arXiv) results reproducibility verification.
+		The difference with the remote reproducibility verification is the presence of an additional VM that checkouts the \textit{\LaTeX\ code} and generates a pdf which is then compared with the one generated from \textit{code}.
+	\item Regression testing and debugging, to ensure that changes to the code do not alter the results.
 \end{itemize}
@@
 \subsection{Technical implementation}
-A template of the RBs is available using Github Actions and is applied on the arXiv version of this paper.
+An open source implementation of the RBs template is available in which the remote reproducibility verification is done using Github Actions.
 The builder VMs use different versions of Ubuntu (18.04 and 20.04) and pull a docker image for building \LaTeX\ from DockerHub.
+We demonstrate its use by writing and verifying the reproducibility of this paper and its arXiv version.
 
-Regarding research that is computational costly or when reproducibility verification is required from the first stages of the research, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the experiment.
-E.g.\ the debug flag in the field of neural networks could set the number of epochs and number of training samples to a low value.
+Regarding research that is computational costly, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the paper.
+This flag also helps in faster iterations during research writing and experimentation.
+An example of the debug flag in the field of neural networks is setting the number of epochs and number of training samples to a low value.
+
 Some possible executions that RBs provide are summarized in the following syntax:
@@
 
+The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
+The \textit{author} only needs to edit (or use the `touch' program to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered.
+
 \section{Discussion}
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-RBs provide a simple solution in verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
+RBs provide a simple solution for writing and verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
 Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
@@
 \section{Conclusion}
-Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed the last few years.
+Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed in the last few years.
 Few works were done on this area, mostly proposing trust on an external third party.
-RBs verify research reproducibility using the tools that most of the researchers already use (\LaTeX, Docker), outsourcing the procedure to VMs on the cloud.
+RBs help in writing and verifying reproducible research using the tools that most of the researchers already use (\LaTeX, Docker).
 
 \section{APPENDIX - Improving Computational Research Reproducibility}
-This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the `results code' programming language.
+This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the \textit{results code} programming language.
 For demonstration purposes we train and test a simple neural network on the MNIST~\cite{lecun2010mnist} dataset with PyTorch~\cite{paszke2019pytorch}.
 
-A common culprit of reproducibility using \LaTeX\ is the time-date metadata of pdf output which can be disabled using the following into the \textit{.tex} code after the preamble:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands for preamble.}, captionpos=b]
+A common culprit against reproducibility in \LaTeX\ is the time-date metadata of pdf output.
+These can be disabled using the following into the \textit{\LaTeX\ code} after the preamble or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
 \pdfinfoomitdate=1
@@
 
-A useful \LaTeX\ package for automatically embedding code results variables in \LaTeX\ code is \textit{datatool}.
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a `results code' and getting the value of a key named lr.}, captionpos=b]
+A useful \LaTeX\ package for automatically embedding code results variables in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a \textit{results code} and getting the value of a key named lr.}, captionpos=b]
 \DTLloaddb{keys_values}{keys_values.csv}
@@
 
-For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the `results code':
+For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the \textit{results code}:
 \begin{itemize}
@@
 
-Regarding the `results code' for Python random seeds need to be set to a specific value such as:
+Regarding the \textit{results code} for Python, random seeds need to be set to a specific value such as:
 \begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
-random.seed(0) # for build-in random module
-np.random.seed(0) # for numpy
-torch.manual_seed(0) # for pytorch
-torch.backends.cudnn.deterministic = True # for pytorch
-torch.backends.cudnn.benchmark = False # for pytorch
-tf.random.set_seed(0) # for Tensorflow
+# for build-in random module
+random.seed(0)
+# for numpy
+np.random.seed(0)
+# for pytorch
+torch.backends.cudnn.benchmark = False
+torch.backends.cudnn.deterministic = True
+torch.cuda.manual_seed_all(0)
+torch.manual_seed(0)
+# for Tensorflow
+tf.random.set_seed(0)
 \end{lstlisting}
@@
 	\includegraphics[width=\linewidth]{results/image.pdf}
-	\caption{Image example created from `results code'.}
+	\caption{Image example created from \textit{results code}.}
 	\label{fig:image}
@@
 	\centering
-	\caption{Table example created from `results code'.}
+	\caption{Table example created from \textit{results code}.}
 	\label{table:table}

### 2020-08-20 main.py

@@ -123,7 +123,7 @@ if __name__ == '__main__':
     plt.xlabel('Epochs')
     plt.ylabel('Loss')
     plt.autoscale(enable=True, axis='x', tight=True)
-    plt.ylim([0, 3])
+    plt.ylim([0, 1])
     plt.legend(['Train', 'Validation'])
     plt.savefig(f'{args.results_dir}/image')
     plt.close()

### 2020-08-22 ms.tex
improve text

@@
 \begin{abstract}
-	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the extra work that needs to be done by the author to make his paper reproducible and by the reviewer to verify the paper's reproducibility.
+	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the cost of extra work that needs to be done by the author to make his paper reproducible and by the reviewer to verify the paper's reproducibility.
 	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
-	The template contains a Makefile that allows the verifier to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
+	The template contains a Makefile that allows the reviewer to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
 	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the pdf files are identical.
 	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
-	The reproducibility of a paper can be verified either locally on the machine of the verifier or remotely using Virtual Machines (VMs) in the cloud.
+	The reproducibility of a paper can be verified either locally on the machine of the reviewer or remotely using Virtual Machines (VMs) in the cloud.
 	We release an open source template of \textit{reproducible builds} (RBs) and use it to write and verify the reproducibility of this paper.
@@
 
-We propose a template that uses the concept of \textit{reproducible builds} (RBs) to verify the reproducibility of computational research papers written in \LaTeX.
-The template consists of a Makefile that allows the verifier to execute the source code that produces the figures, tables, variables (results), and later compile the \LaTeX\ to produce a pdf.
-The previous procedure is executed twice and the research paper is verified as reproducible, if and only if the resulting pdf files are identical.
-This procedure can be executed either locally in the verifier machine or remotely in Virtual Machines (VMs) in the cloud.
-
+We propose a template that uses the concept of \textit{reproducible builds} (RBs) to verify the reproducibility of computational research papers written in \LaTeX in a local or remote computational environment.
 We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
-We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
+We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
 
@@
 	\item \textit{paper} as a computational research paper,
-	\item \textit{results} as the figures, tables and variables that are shown in the paper,
-	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the research paper,
-	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the results and
-	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code}.
-	\item \textit{author} as the author or authors of the \textit{paper},
-	\item \textit{reviewer} as the reviewer of the \textit{paper},
+	\item \textit{results} as the figures, tables and variables that are shown in the \textit{paper},
+	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the \textit{paper},
+	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the \textit{results},
+	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code},
+	\item \textit{author} as the author(s) of the \textit{paper} and
+	\item \textit{reviewer} as the reviewer(s) of the \textit{paper} or anyone in interest of verifying the \textit{paper} (author(s), journal editors, other researchers).
 \end{itemize}
@@
 	\caption{The RBs template file hierarchy is depicted in the light gray background and the arrows denote the data flow towards generating the pdf.
-	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background files that are used for a subsequent step.}
+	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background, files that are used for a subsequent step.}
 	\label{fig:filehierarchyworkflow}
@@
 
-The proposed template can be applied on computational research papers written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} can be executed within a Docker container or a virtual environment.
+The proposed template can be applied on \textit{papers} written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} can be executed within a Docker container or a virtual environment.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
@@
 A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation by the template.
-The template fits in the research writing and reproducibility verificatrion in the following way:
+The template fits in the research writing and reproducibility verification in the following way:
 \begin{enumerate}
-	\item the \textit{author} writes or edits code in his local repository,
-	\item the \textit{author} may verify the reproducibility of the paper locally,
+	\item the \textit{author} edits the \textit{code} in the local repository,
+	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally:
+		\begin{enumerate}
+			\item the \textit{results code} is executed twice in the local machine,
+			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile the pdf files,
+			\item the \textit{paper} is verifed as locally reproducible if and only if the pdf files are identical.
+		\end{enumerate}
 	\item the \textit{author} may push the change to the remote repository, which optionally triggers the remote reproducibility verification:
 		\begin{enumerate}
-			\item two VMs (builders) execute the \textit{results code},
-			\item the results along with the \textit{\LaTeX\ code} are used to compile the pdf files,
-			\item the pdf files are sent to another VM (verifier), which verifies the research paper as reproducible if and only if the pdf files are identical.
+			\item the \textit{results code} is executed twice in two cloud VMs (builders),
+			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile the pdf files,
+			\item the \textit{paper} is verified as remotely reproducible if and only if the pdf files are identical.
 		\end{enumerate}
-	\item the \textit{reviewer} can check the remote reproducibility verifcation or if not available locally verify the reproducibility in his own machine.
+	\item the \textit{reviewer} may verify the reproducibility of the paper on a local or remote machine.
 \end{enumerate}
 
-Docker usage in RBs provides portability of the environment of the research while the VM provides trust in the procedure (in contrast in executing these local, thus having low credibility in reporting reproducibility).
-The reason that two independent builder VMs are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the verifier VM report the paper as non-reproducible.
+Docker usage in RBs provides portability of the environment of the research while the VM provides trust in the procedure (in contrast with verifying locally, thus having low credibility in reporting reproducibility).
+The reason that two local/remote compilations are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the \textit{paper} non-reproducible.
 
-Additional constraints could be imposed in the VMs such as disallowing image files in the code and monitoring the network connections of the \textit{code} to help the \textit{reviewer} check whether the results are generated from the \textit{code} and are not fetched from an external source.
+Additional constraints could be imposed in the VMs such as disallowing image files in the \textit{code} and monitoring the network connections of the \textit{code} to help the \textit{reviewer} check whether the \textit{results} are generated from the \textit{code} and are not fetched from an external source.
 
@@
 \begin{itemize}
-	\item Preprint server (such as arXiv) results reproducibility verification.
+	\item Preprint server (such as arXiv) \textit{paper} reproducibility verification.
 		The difference with the remote reproducibility verification is the presence of an additional VM that checkouts the \textit{\LaTeX\ code} and generates a pdf which is then compared with the one generated from \textit{code}.
-	\item Regression testing and debugging, to ensure that changes to the code do not alter the results.
+	\item Regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
 \end{itemize}
@@
 
-Regarding research that is computational costly, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the paper.
+Regarding research that is computational costly, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the \textit{paper}.
 This flag also helps in faster iterations during research writing and experimentation.
@@
 
-Some possible executions that RBs provide are summarized in the following syntax:
+A common culprit against reproducibility in \LaTeX\ is the time-date metadata of pdf output.
+These can be disabled using the following into the \textit{\LaTeX\ code} after the preamble or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
+\pdfinfoomitdate=1
+\pdfsuppressptexinfo=-1
+\pdftrailerid{}
+\end{lstlisting}
+
+Executing RBs can be done using the following:
 \begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
@@
 
-\section{Discussion}
-Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-RBs provide a simple solution for writing and verifying the reproducibility of a computational research paper as a whole, without having to trust a third-party.
-Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
-
-\section{Conclusion}
-Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed in the last few years.
-Few works were done on this area, mostly proposing trust on an external third party.
-RBs help in writing and verifying reproducible research using the tools that most of the researchers already use (\LaTeX, Docker).
-
-\section{APPENDIX - Improving Computational Research Reproducibility}
-This appendix provides suggestions for improving the reproducibility of computational research papers written in \LaTeX\ with Python as the \textit{results code} programming language.
+\section{Example Use Case of RBs}
+This sections provides a use case of RBs and also serves as a manual for creating reproducibility of \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
 For demonstration purposes we train and test a simple neural network on the MNIST~\cite{lecun2010mnist} dataset with PyTorch~\cite{paszke2019pytorch}.
 
-A common culprit against reproducibility in \LaTeX\ is the time-date metadata of pdf output.
-These can be disabled using the following into the \textit{\LaTeX\ code} after the preamble or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
-\end{lstlisting}
-
-A useful \LaTeX\ package for automatically embedding code results variables in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
+A useful \LaTeX\ package for automatically embedding variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
 \begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a \textit{results code} and getting the value of a key named lr.}, captionpos=b]
@@
 
-Another useful results function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}.
+Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}.
 
@@
 	\centering
-	\caption{Table example created from \textit{results code}.}
+	\caption{Table example created from results code.}
 	\label{table:table}
@@
 
+\section{Discussion}
+Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
+RBs provide a simple solution for writing and verifying the reproducibility of a \textit{paper} as a whole, without having to trust a third-party.
+Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
+Similar to RBs is ReDoc~\cite{schwab2000making} which however focuses on separate result file reproducibility and requires the author to write each rule in the Makefile for each result file.
+RBs on the other hand focus on `~\textit{paper} as a whole' reproducibility with an automatically generated Makefile.
+
+\section{Conclusion}
+Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed in the last few years.
+Few works were done on this area, mostly proposing trust on an external third party.
+RBs help in writing and verifying reproducible research using the tools that most of the researchers already use (\LaTeX, Docker).
+
 \bibliographystyle{IEEEtran}

### 2020-08-22 main.py

@@ -20,19 +20,18 @@ plt.rcParams['savefig.format'] = 'pdf'
 class CustomModel(nn.Module):
     def __init__(self):
         super(CustomModel, self).__init__()
-        self.conv1 = nn.Conv2d(1, 4, 5, 1)
-        self.dropout1 = nn.Dropout2d(0.25)
-        self.dropout2 = nn.Dropout2d(0.5)
-        self.fc1 = nn.Linear(2304, 128)
-        self.fc2 = nn.Linear(128, 10)
+        self.conv1 = nn.Conv2d(1, 20, 5, 1)
+        self.conv2 = nn.Conv2d(20, 50, 5, 1)
+        self.fc1 = nn.Linear(4*4*50, 500)
+        self.fc2 = nn.Linear(500, 10)
 
     def forward(self, x):
-        x = self.conv1(x)
-        x = self.dropout1(x)
+        x = F.relu(self.conv1(x))
+        x = F.max_pool2d(x, 2, 2)
+        x = F.relu(self.conv2(x))
+        x = F.max_pool2d(x, 2, 2)
         x = torch.flatten(x, 1)
-        x = self.fc1(x)
-        x = F.relu(x)
-        x = self.dropout2(x)
+        x = F.relu(self.fc1(x))
         x = self.fc2(x)
         return x
 

### 2020-09-07 main.py
fix main.py

@@ -36,21 +36,22 @@ class CustomModel(nn.Module):
 
 
 if __name__ == '__main__':
-    # Set random seeds.
+    # DO NOT EDIT BLOCK
     np.random.seed(0)
     torch.manual_seed(0)
     torch.cuda.manual_seed_all(0)
     torch.backends.cudnn.deterministic = True
     torch.backends.cudnn.benchmark = False
 
-    # Parse arguments.
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
-    parser.add_argument('--use-cuda', default=False, action='store_true')
-    parser.add_argument('--cache-dir')
-    parser.add_argument('--results-dir')
     args = parser.parse_args()
-    device = torch.device('cuda' if (torch.cuda.is_available() and args.use_cuda) else 'cpu')
+
+    cache_dir = 'cache'
+    results_dir = 'results'
+    # END OF DO NOT EDIT BLOCK
+
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     if args.full:
         num_epochs = 10
         train_range = range(40000)

### 2020-09-07 main.py
fix args

@@ -66,8 +66,8 @@ if __name__ == '__main__':
     lr = 0.01
     batch_size = 64
     transform = transforms.Compose([transforms.ToTensor(), transforms.Normalize((0.1307,), (0.3081,))])
-    train_dataset = MNIST(args.cache_dir, train=True, transform=transform, download=True)
-    validation_dataset = MNIST(args.cache_dir, train=True, transform=transform)
+    train_dataset = MNIST(cache_dir, train=True, transform=transform, download=True)
+    validation_dataset = MNIST(cache_dir, train=True, transform=transform)
     train_dataloader = DataLoader(train_dataset, batch_size=batch_size, sampler=SubsetRandomSampler(train_range))
     validation_dataloader = DataLoader(validation_dataset, batch_size=batch_size, sampler=SubsetRandomSampler(validation_range))
     model = CustomModel()
@@ -76,7 +76,7 @@ if __name__ == '__main__':
     train_loss_array = np.zeros((num_epochs))
     validation_loss_array = np.zeros((num_epochs))
     validation_loss_best = float('inf')
-    model_path = f'{args.results_dir}/model_best.pt'
+    model_path = f'{results_dir}/model_best.pt'
     for index_epoch, epoch in enumerate(range(num_epochs)):
         train_loss_sum = 0
         model.train()
@@ -124,7 +124,7 @@ if __name__ == '__main__':
     plt.autoscale(enable=True, axis='x', tight=True)
     plt.ylim([0, 1])
     plt.legend(['Train', 'Validation'])
-    plt.savefig(f'{args.results_dir}/image')
+    plt.savefig(f'{results_dir}/image')
     plt.close()
 
     # Create tables.
@@ -133,8 +133,8 @@ if __name__ == '__main__':
     columns = ['MNIST']
     df = pd.DataFrame(table, index=index, columns=columns)
     df.index.names = ['Metric']
-    df.to_latex(f'{args.results_dir}/table.tex', float_format="%.2f", bold_rows=True)
+    df.to_latex(f'{results_dir}/table.tex', float_format="%.2f", bold_rows=True)
 
     # Create variables.
     df = pd.DataFrame({'key': ['lr', 'batch_size', 'validation_accuracy_best'], 'value': [lr, str(int(batch_size)), validation_accuracy_best]})
-    df.to_csv(f'{args.results_dir}/keys-values.csv', index=False, float_format='%.2f')
+    df.to_csv(f'{results_dir}/keys-values.csv', index=False, float_format='%.2f')

### 2020-09-07 ms.tex
fix Dockerfile and ms.tex

@@
 \begin{abstract}
-	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the cost of extra work that needs to be done by the author to make his paper reproducible and by the reviewer to verify the paper's reproducibility.
+	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the cost of extra work that needs to be done by the author to make the paper reproducible and by the reviewer to verify the paper's reproducibility.
 	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
@@
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper increases its reproducibility confidence but it is not enough to verify it.
-Using a template for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+Open sourcing the code and the raw data of a computational research paper increases the confidence in its reproducibility but it is not enough to verify it.
+Using a template both for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
 
-We propose a template that uses the concept of \textit{reproducible builds} (RBs) to verify the reproducibility of computational research papers written in \LaTeX in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} for writing papers with RBs and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
+We propose a template for writing computational research papers with \LaTeX and verifying the its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
@@
 	\item \textit{results} as the figures, tables and variables that are shown in the \textit{paper},
-	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex} files) and bibliography (\textit{*.bib} files) of the \textit{paper},
-	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py} files) that produces the \textit{results},
+	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex}) and bibliography (\textit{*.bib}) of the \textit{paper},
+	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py}) that produces the \textit{results},
 	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code},
@@
 			child{node[draw, anchor=west, fill=blue!20](py){main.py}}
-			child{node[draw, anchor=west, fill=blue!20](venv){.venv}}
 			child{node[draw, anchor=west, fill=blue!20](dockerfile){Dockerfile}};
 			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!30, inner sep=4pt, fit=(root) (dockerfile)]{};
-				\node[draw, rounded corners, dashed, fill=gray!70, inner sep=2pt, fit=(py) (dockerfile)](code){};
-				\node[draw, rounded corners, dashed, fill=gray!70, inner sep=2pt, fit=(tex) (bib)](paper){};
+				\node[draw, rounded corners, dashed, fill=gray!20, inner sep=4pt, fit=(root) (dockerfile)]{};
+				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(py) (dockerfile)](code){};
+				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(tex) (bib)](paper){};
 			\end{scope}
 			\node[draw, right=2cm of code, fill=white] (results) {results};
-			\path[draw, ->] (code) -- node[above]{venv/docker} (results);
+			\path[draw, ->] (code) -- node[above]{docker} (results);
 			\node[draw, right=4cm of paper, fill=white] (pdf) {pdf};
@@
 
-The proposed template can be applied on \textit{papers} written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} can be executed within a Docker container or a virtual environment.
+The proposed template can be applied on \textit{papers} written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} are executed within a Docker container.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
@@
 
-make [OPTION] [ARGS=--full] [GPU='--gpus all']
+SYNTAX
+make [OPTION] [ARGS=--full]
 
 OPTIONS
-# (or empty OPTION) Generate pdf with results from venv.
-ms.pdf
-# Verify venv paper reproducibility.
-venv-verify
-# Generate pdf with results from docker.
-docker
-# Verify docker paper reproducibility.
-docker-verify
-# Remove cache, results, venv directories and tex aux files.
-clean
-# Show help.
-help
+ms.pdf - Generate pdf.
+test   - Test whether the paper has a reproducible build.
+clean  - Remove cache, results directories and tex aux files.
+help   - Show help.
+
 \end{lstlisting}
@@
 \section{Discussion}
+RBs are based on plain text and are independent of any specific git and docker registry providor thus preventing `vendor lock-in' situations.
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.

### 2020-09-07 main.py
fix model device

@@ -70,7 +70,7 @@ if __name__ == '__main__':
     validation_dataset = MNIST(cache_dir, train=True, transform=transform)
     train_dataloader = DataLoader(train_dataset, batch_size=batch_size, sampler=SubsetRandomSampler(train_range))
     validation_dataloader = DataLoader(validation_dataset, batch_size=batch_size, sampler=SubsetRandomSampler(validation_range))
-    model = CustomModel()
+    model = CustomModel().to(device)
     optimizer = optim.SGD(model.parameters(), lr=lr)
     criterion = nn.CrossEntropyLoss()
     train_loss_array = np.zeros((num_epochs))

### 2020-09-11 ms.tex
[make test ARGS=--full]

@@
 \usepackage{datatool}
+\usepackage{diagbox}
 \usepackage{listings}
@@
 \lstdefinestyle{lststyle}{
-	aboveskip=20pt,
-	belowskip=20pt,
+	aboveskip=10pt,
+	belowskip=10pt,
 	frame=single,
@@
 	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
-	The template contains a Makefile that allows the reviewer to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
+	The template contains a Makefile that allows the author/reviewer to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
 	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the pdf files are identical.
@@
 	\item the \textit{author} edits the \textit{code} in the local repository,
-	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally:
+	\item the \textit{author} may execute \textit{make} during development and experimentation,
+	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally by executing \textit{make test} (or remotely by commiting with a message which contains \textit{[make test]}) which triggers the following:
 		\begin{enumerate}
-			\item the \textit{results code} is executed twice in the local machine,
-			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile the pdf files,
-			\item the \textit{paper} is verifed as locally reproducible if and only if the pdf files are identical.
-		\end{enumerate}
-	\item the \textit{author} may push the change to the remote repository, which optionally triggers the remote reproducibility verification:
-		\begin{enumerate}
-			\item the \textit{results code} is executed twice in two cloud VMs (builders),
-			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile the pdf files,
-			\item the \textit{paper} is verified as remotely reproducible if and only if the pdf files are identical.
+			\item the \textit{results code} is executed,
+			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile a pdf file,
+			\item the previous is executed twice,
+			\item the \textit{paper} is verifed as reproducible if and only if the pdf files are identical.
 		\end{enumerate}
@@
 An open source implementation of the RBs template is available in which the remote reproducibility verification is done using Github Actions.
-The builder VMs use different versions of Ubuntu (18.04 and 20.04) and pull a docker image for building \LaTeX\ from DockerHub.
+The builder VMs use the latest version of Ubuntu and pull a docker image for building \LaTeX\ from the Github Container Registry.
 We demonstrate its use by writing and verifying the reproducibility of this paper and its arXiv version.
 
-Regarding research that is computational costly, the template provides a debug flag that verifies the reproducibility of a computationally lighter version of the \textit{paper}.
-This flag also helps in faster iterations during research writing and experimentation.
-An example of the debug flag in the field of neural networks is setting the number of epochs and number of training samples to a low value.
+Regarding research that is computational costly, the template by default allows the execution and reproducibility verification of a computationally lighter version of the \textit{paper} and provides an argument for executing the whole experiment.
+This also helps in faster iterations during research writing and experimentation.
+An example of a computationally lighter version in the field of neural networks is setting the number of epochs and number of training samples to a low value.
 
@@
 \begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
-
 SYNTAX
@@
 
+\begin{table}[]
+	\centering
+	\caption{Makefile usage table.}
+	\label{table:usagetable}
+	\begin{tabular}{l|ll}
+		\toprule
+		\diagbox{\textbf{OPTION}}{\textbf{ARGS}} & \textbf{(empty)}              & \textbf{-{}-full}                    \\
+		\midrule
+		\textbf{(ms.pdf or empty)}          & debug/development    & release paper             \\
+		\textbf{test}                       & test reproducibility & test reproducibility full \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
 The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
-The \textit{author} only needs to edit (or use the `touch' program to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered.
+The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered.
 
 \section{Example Use Case of RBs}
-This sections provides a use case of RBs and also serves as a manual for creating reproducibility of \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
-For demonstration purposes we train and test a simple neural network on the MNIST~\cite{lecun2010mnist} dataset with PyTorch~\cite{paszke2019pytorch}.
+This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
+For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization with PyTorch~\cite{paszke2019pytorch}, on the following datasets:
+\begin{itemize}
+	\item MNIST~\cite{lecun2010mnist}
+	\item FashionMNIST~\cite{xiao2017fashion}
+	\item KMNIST~\cite{clanuwat2018deep}
+	\item QMNIST~\cite{yadav2019cold}
+\end{itemize}
 
@@
 	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
-	\item the validation accuracy of the best model is $\DTLfetch{keys_values}{key}{validation_accuracy_best}{value}\%$.
 \end{itemize}
@@
 For example Fig.~\ref{fig:image} depicts the train and validation loss:
-\begin{figure}[h]
-	\includegraphics[width=\linewidth]{results/image.pdf}
-	\caption{Image example created from \textit{results code}.}
+\begin{figure*}[!t]
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/MNIST-loss}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/KMNIST-loss}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/QMNIST-loss}}
+	\caption{Train validation lossses.
+	Image example created from \textit{results code}.}
 	\label{fig:image}
-\end{figure}
+\end{figure*}
 
@@
 df = pd.DataFrame(table)
-df.to_latex('table.tex', float_format="%.2f")
+df.to_latex('metrics.tex', float_format="%.2f")
 \end{lstlisting}
@@
 	\setlength\tabcolsep{4.2pt}
-	\input{results/table.tex}
+	\input{results/metrics.tex}
 \end{table}
@@
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-RBs provide a simple solution for writing and verifying the reproducibility of a \textit{paper} as a whole, without having to trust a third-party.
+RBs provide a simple solution for writing and verifying the reproducibility of a `\textit{paper} as a whole', without having to trust a third-party.
 Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
 Similar to RBs is ReDoc~\cite{schwab2000making} which however focuses on separate result file reproducibility and requires the author to write each rule in the Makefile for each result file.
-RBs on the other hand focus on `~\textit{paper} as a whole' reproducibility with an automatically generated Makefile.
+RBs on the other hand provides a Makefile that is automatically generated by the template.
 

### 2020-09-11 main.py

@@ -4,44 +4,73 @@ import pandas as pd
 import torch
 
 from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
 from torch import nn
 from torch import optim
 from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST
+from torchvision.models import vgg11_bn
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
+dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
+dataset_name_list = [dataset.__name__ for dataset in dataset_list]
+num_fc_list = [9216, 9216, 9216, 9216, 9216, 12544, 12544, 135424, 12544]
 
-class CustomModel(nn.Module):
-    def __init__(self):
-        super(CustomModel, self).__init__()
-        self.conv1 = nn.Conv2d(1, 20, 5, 1)
-        self.conv2 = nn.Conv2d(20, 50, 5, 1)
-        self.fc1 = nn.Linear(4*4*50, 500)
-        self.fc2 = nn.Linear(500, 10)
+mean_std_list = [
+        ((0.1307,), (0.3081,)),
+        ((0.1307,), (0.3081,)),
+        ((0.1307,), (0.3081,)),
+        ((0.1307,), (0.3081,)),
+        ]
 
-    def forward(self, x):
-        x = F.relu(self.conv1(x))
-        x = F.max_pool2d(x, 2, 2)
-        x = F.relu(self.conv2(x))
-        x = F.max_pool2d(x, 2, 2)
-        x = torch.flatten(x, 1)
-        x = F.relu(self.fc1(x))
-        x = self.fc2(x)
-        return x
+train_range_list = [
+        range(50000), 
+        range(50000),
+        range(50000),
+        range(50000),
+        ]
+
+validation_range_list = [
+        range(50000, 60000),
+        range(50000, 60000),
+        range(50000, 60000),
+        range(50000, 60000),
+        ]
+
+test_range_list = [
+        range(10000),
+        range(10000),
+        range(10000),
+        range(10000),
+        ]
+
+def save_loss(train_loss, validation_loss, dataset_name, results_dir):
[…]

### 2020-09-11 main.py
[make test]

@@ -82,7 +82,7 @@ if __name__ == '__main__':
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     if args.full:
-        num_epochs = 50
+        num_epochs = 20
     else:
         num_epochs = 1
         train_range_list = [train_range[:10] for train_range in train_range_list]

### 2020-09-14 ms.tex
[make test]

@@
 
-We propose a template for writing computational research papers with \LaTeX and verifying the its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
+We propose a template for writing computational research papers with \LaTeX\ and verifying the its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
 We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
@@
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
-The corresponding Dockerfile can be provided by the \textit{author} or generated by tools such as containerit~\cite{nust2019containerit}.
+The corresponding Dockerfile can be provided by the \textit{author} or generated by tools such as repo2docker~\cite{forde2018reproducible}.
 
-A specific file hierarchy (shown in Fig.~\ref{fig:filehierarchyworkflow}) is used in this paper however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation by the template.
+A specific file hierarchy is shown in Fig.~\ref{fig:filehierarchyworkflow} however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation.
 The template fits in the research writing and reproducibility verification in the following way:
@@
 		\end{enumerate}
-	\item the \textit{reviewer} may verify the reproducibility of the paper on a local or remote machine.
+	\item the \textit{reviewer} may verify the reproducibility of the paper locally (by cloning the repo) or remotely (by inspecting the result of \textit{[make test]}).
 \end{enumerate}
 
-Docker usage in RBs provides portability of the environment of the research while the VM provides trust in the procedure (in contrast with verifying locally, thus having low credibility in reporting reproducibility).
 The reason that two local/remote compilations are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the \textit{paper} non-reproducible.
+Moreover Docker usage in RBs provides portability of the environment of the research while third-party VMs are used when the verification needs to be shared (in contrast with verifying locally, thus having low credibility in reporting reproducibility).
 
@@
 
-Other potential uses of the RBs template include:
+Potential uses of the RBs template include:
 \begin{itemize}
-	\item Preprint server (such as arXiv) \textit{paper} reproducibility verification.
-		The difference with the remote reproducibility verification is the presence of an additional VM that checkouts the \textit{\LaTeX\ code} and generates a pdf which is then compared with the one generated from \textit{code}.
-	\item Regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
+	\item preprint server (e.g.\ arXiv) \textit{paper} reproducibility verification and
+	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
 \end{itemize}
@@
 \subsection{Technical implementation}
-An open source implementation of the RBs template is available in which the remote reproducibility verification is done using Github Actions.
-The builder VMs use the latest version of Ubuntu and pull a docker image for building \LaTeX\ from the Github Container Registry.
-We demonstrate its use by writing and verifying the reproducibility of this paper and its arXiv version.
-
-Regarding research that is computational costly, the template by default allows the execution and reproducibility verification of a computationally lighter version of the \textit{paper} and provides an argument for executing the whole experiment.
-This also helps in faster iterations during research writing and experimentation.
-An example of a computationally lighter version in the field of neural networks is setting the number of epochs and number of training samples to a low value.
-
-A common culprit against reproducibility in \LaTeX\ is the time-date metadata of pdf output.
-These can be disabled using the following into the \textit{\LaTeX\ code} after the preamble or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
-\end{lstlisting}
+We provide an open source implementation of the RBs template in which the remote reproducibility verification is done using Github Actions.
+The builder VM uses the latest version of Ubuntu and pulls a docker image for building \LaTeX\ from the Github Container Registry.
+We demonstrate its use by writing and verifying the reproducibility of this paper.
 
@@
 
+Regarding research that is computational costly, the template allows the execution and reproducibility verification of a computationally lighter version of the \textit{paper} by default.
+This also helps in faster iterations during research writing and experimentation.
+An example of computationally lighter versions in the field of neural networks is setting the number of epochs and number of training samples to a low value.
+The execution of the full experiment is done by providing an additional argument.
+
 The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
-The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered.
+The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.
 
@@
 This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
-For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization with PyTorch~\cite{paszke2019pytorch}, on the following datasets:
-\begin{itemize}
-	\item MNIST~\cite{lecun2010mnist}
-	\item FashionMNIST~\cite{xiao2017fashion}
-	\item KMNIST~\cite{clanuwat2018deep}
-	\item QMNIST~\cite{yadav2019cold}
-\end{itemize}
+For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
+
+Regarding \LaTeX\ a common culprit against reproducibility is the time-date metadata embedded in the pdf output.
+These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
+\pdfinfoomitdate=1
+\pdfsuppressptexinfo=-1
+\pdftrailerid{}
+\end{lstlisting}
 
@@
 \begin{itemize}
-	\item the learning rate is $\DTLfetch{keys_values}{key}{lr}{value}$,
+	\item the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$,
 	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
+	\item the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
 \end{itemize}
@@
 \begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
-# for build-in random module
-random.seed(0)
-# for numpy
-np.random.seed(0)
+random.seed(0) # for build-in random module
+np.random.seed(0) # for numpy
+tf.random.set_seed(0) # for Tensorflow
 # for pytorch
@@
 torch.manual_seed(0)
-# for Tensorflow
-tf.random.set_seed(0)
 \end{lstlisting}
@@
 	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
+	\\
 	\subfloat{\includegraphics[width=0.25\textwidth]{results/KMNIST-loss}}
 	\subfloat{\includegraphics[width=0.25\textwidth]{results/QMNIST-loss}}
-	\caption{Train validation lossses.
+	\caption{Train validation losses.
 	Image example created from \textit{results code}.}
@@
 
-Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}.
+Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
 

### 2020-09-14 main.py

@@ -82,7 +82,7 @@ if __name__ == '__main__':
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     if args.full:
-        num_epochs = 20
+        num_epochs = 10
     else:
         num_epochs = 1
         train_range_list = [train_range[:10] for train_range in train_range_list]
@@ -92,7 +92,7 @@ if __name__ == '__main__':
     batch_size = 64
     train_loss_array = np.zeros((len(dataset_list), num_epochs))
     validation_loss_array = np.zeros((len(dataset_list), num_epochs))
-    test_accuracy_array = np.zeros((len(dataset_list)))
+    test_accuracy_array = np.zeros((len(dataset_list), 1))
     test_batch_size = 1000
     criterion = nn.CrossEntropyLoss()
     for index_dataset, (dataset, dataset_name, train_range, validation_range, test_range, mean_std, num_fc) in enumerate(zip(dataset_list, dataset_name_list, train_range_list, validation_range_list, test_range_list, mean_std_list, num_fc_list)):
@@ -178,6 +178,6 @@ if __name__ == '__main__':
     for index_dataset_name, (dataset_name, train_loss, validation_loss) in enumerate(zip(dataset_name_list, train_loss_array, validation_loss_array)):
         save_loss(train_loss, validation_loss, dataset_name, results_dir)
 
-    max_per_column_list = test_accuracy_array.max(0)
-    df = pd.DataFrame(test_accuracy_array)
-    df.to_latex(f'{results_dir}/metrics.tex', bold_rows=True, column_format='r|r', multirow=True, escape=False)
+    test_accuracy_array = test_accuracy_array.T
+    df = pd.DataFrame(test_accuracy_array, index=['Accuracy'], columns=dataset_name_list)
+    df.to_latex(f'{results_dir}/metrics.tex', bold_rows=True, column_format='r|rrrr', multirow=True, escape=False)

### 2020-09-16 ms.tex
{make test}

@@
 
-We propose a template for writing computational research papers with \LaTeX\ and verifying the its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}} and use it to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
+We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
@@
 	\item \textit{author} as the author(s) of the \textit{paper} and
-	\item \textit{reviewer} as the reviewer(s) of the \textit{paper} or anyone in interest of verifying the \textit{paper} (author(s), journal editors, other researchers).
+	\item \textit{reviewer} as the reviewer(s) of the \textit{paper} or anyone interested in verifying the \textit{paper} (author(s), journal editors, other researchers).
 \end{itemize}
@@
 
-The proposed template can be applied on \textit{papers} written in \LaTeX~\cite{lamport1994latex} and the \textit{results code} are executed within a Docker container.
+The proposed template can be used for writing \textit{papers} with \LaTeX~\cite{lamport1994latex} and the \textit{results code} that can be executed within a Docker container.
 \LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
-The corresponding Dockerfile can be provided by the \textit{author} or generated by tools such as repo2docker~\cite{forde2018reproducible}.
 
 A specific file hierarchy is shown in Fig.~\ref{fig:filehierarchyworkflow} however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation.
-The template fits in the research writing and reproducibility verification in the following way:
+The Makefile and Dockerfile are automatically generated by the template after user prompts.
+For more complicated setups the Dockerfile can be provided by the \textit{author} or generated by tools such as repo2docker~\cite{forde2018reproducible}.
+
+The template fits in research writing and reproducibility verification in the following way:
 \begin{enumerate}
@@
 	\item the \textit{author} may execute \textit{make} during development and experimentation,
-	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally by executing \textit{make test} (or remotely by commiting with a message which contains \textit{[make test]}) which triggers the following:
+	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally by executing \textit{make test} (or remotely by commiting the code change with a message which contains \textit{\{make test\}}) which triggers the following:
 		\begin{enumerate}
@@
 		\end{enumerate}
-	\item the \textit{reviewer} may verify the reproducibility of the paper locally (by cloning the repo) or remotely (by inspecting the result of \textit{[make test]}).
+	\item the \textit{reviewer} may verify the reproducibility of the paper locally (by cloning the repo and executing \textit{make test}) or remotely (by inspecting the result of \textit{\{make test\}}).
 \end{enumerate}
@@
 \subsection{Technical implementation}
-We provide an open source implementation of the RBs template in which the remote reproducibility verification is done using Github Actions.
-The builder VM uses the latest version of Ubuntu and pulls a docker image for building \LaTeX\ from the Github Container Registry.
-We demonstrate its use by writing and verifying the reproducibility of this paper.
-
 Executing RBs can be done using the following:
@@
 The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.
+
+In this implementation of RBs the remote reproducibility verification is done using Github Actions, the builder VM uses the latest version of Ubuntu and pulls a docker image for building \LaTeX\ from the Github Container Registry.
 
@@
 Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
-For example Fig.~\ref{fig:image} depicts the train and validation loss:
-\begin{figure*}[!t]
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/MNIST-loss}}
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
-	\\
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/KMNIST-loss}}
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/QMNIST-loss}}
-	\caption{Train validation losses.
+For example Fig.~\ref{fig:image} depicts the train and validation loss for all datasets.
+\begin{figure}[!t]
+	\subfloat{\includegraphics[width=0.5\textwidth]{results/validation-loss}}
+	\caption{Validation losses.
 	Image example created from \textit{results code}.}
 	\label{fig:image}
-\end{figure*}
+\end{figure}
 
@@
 \section{Discussion}
-RBs are based on plain text and are independent of any specific git and docker registry providor thus preventing `vendor lock-in' situations.
+RBs are based on plain text files and are independent of any specific version control and docker registry providor thus preventing `vendor lock-in' situations.
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
 RBs provide a simple solution for writing and verifying the reproducibility of a `\textit{paper} as a whole', without having to trust a third-party.
-Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party verifications (such as cloud VMs) cannot be trusted.
+Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party VMs cannot be trusted.
 Similar to RBs is ReDoc~\cite{schwab2000making} which however focuses on separate result file reproducibility and requires the author to write each rule in the Makefile for each result file.

### 2020-09-16 main.py

@@ -49,21 +49,6 @@ test_range_list = [
         range(10000),
         ]
 
-def save_loss(train_loss, validation_loss, dataset_name, results_dir):
-    fig, ax = plt.subplots()
-    plt.grid(True)
-    plt.autoscale(enable=True, axis='x', tight=True)
-    plt.ylim([0, 1])
-    plt.xlabel('Epochs', fontsize=15)
-    plt.ylabel('Loss', fontsize=15)
-    plt.plot(train_loss)
-    plt.plot(validation_loss)
-    ax.tick_params(axis='both', which='major', labelsize='large')
-    ax.tick_params(axis='both', which='minor', labelsize='large')
-    ax.xaxis.set_major_locator(MaxNLocator(integer=True))
-    plt.savefig(f'{results_dir}/{dataset_name}-loss', bbox_inches='tight')
-    plt.close()
-
 
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK
@@ -90,7 +75,6 @@ if __name__ == '__main__':
         test_range_list = [test_range[:10] for test_range in test_range_list]
     lr = 0.01
     batch_size = 64
-    train_loss_array = np.zeros((len(dataset_list), num_epochs))
     validation_loss_array = np.zeros((len(dataset_list), num_epochs))
     test_accuracy_array = np.zeros((len(dataset_list), 1))
     test_batch_size = 1000
@@ -114,7 +98,6 @@ if __name__ == '__main__':
         validation_loss_best = float('inf')
         model_path = f'{results_dir}/{dataset.__name__}.pt'
         for index_epoch, epoch in enumerate(range(num_epochs)):
-            train_loss_sum = 0
             model.train()
             for data, target in train_dataloader:
                 data = data.to(device)
@@ -124,9 +107,6 @@ if __name__ == '__main__':
                 loss = criterion(output, target)
                 loss.backward()
                 optimizer.step()
-                train_loss_sum += loss.item()
-            train_loss = train_loss_sum / len(train_dataloader)
-            train_loss_array[index_dataset, index_epoch] = train_loss
             model.eval()
             validation_loss_sum = 0
             correct = 0
@@ -175,8 +155,20 @@ if __name__ == '__main__':
             lr]})
     df_keys_values.to_csv(f'{results_dir}/keys-values.csv')
 
[…]

### 2020-09-17 main.py
{make test}

@@ -11,27 +11,38 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, STL10, SVHN
 from torchvision.models import vgg11_bn
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
-dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
+dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, STL10, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
 num_fc_list = [9216, 9216, 9216, 9216, 9216, 12544, 12544, 135424, 12544]
+activation_function_list = ['ReLU', 'SELU']
 
 mean_std_list = [
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
+        ((0.1307,), (0.3081,)),
+        ((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
+        ((0.5071, 0.4865, 0.4409), (0.2673, 0.2564, 0.2762)),
+        ((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)),
+        ((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)),
         ]
 
 train_range_list = [
         range(50000), 
         range(50000),
         range(50000),
+        range(50000),
+        range(600000),
+        range(40000),
+        range(40000),
+        range(4000),
         range(50000),
         ]
 
@@ -40,6 +51,11 @@ validation_range_list = [
         range(50000, 60000),
         range(50000, 60000),
         range(50000, 60000),
+        range(600000, 697932),
+        range(40000, 50000),
+        range(40000, 50000),
+        range(4000, 5000),
+        range(50000, 60000),
         ]
 
 test_range_list = [
@@ -47,7 +63,37 @@ test_range_list = [
         range(10000),
         range(10000),
         range(10000),
+        range(116323),
+        range(10000),
[…]

### 2020-09-18 main.py
{make test}

@@ -11,13 +11,13 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, STL10, SVHN
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, SVHN
 from torchvision.models import vgg11_bn
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
-dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, STL10, SVHN]
+dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
 num_fc_list = [9216, 9216, 9216, 9216, 9216, 12544, 12544, 135424, 12544]
 activation_function_list = ['ReLU', 'SELU']
@@ -141,7 +141,7 @@ if __name__ == '__main__':
                 transforms.ToTensor(),
                 transforms.Normalize(mean_std[0], mean_std[1])
                 ])
-        if dataset_name in ['STL10', 'SVHN']:
+        if dataset_name == 'SVHN':
             train_dataset = dataset(cache_dir, split='train', transform=transform, download=True)
             validation_dataset = dataset(cache_dir, split='train', transform=transform)
             test_dataset = dataset(cache_dir, split='test', transform=transform, download=True)

### 2020-09-19 ms.tex
{make test}
{make test ARGS=--full}

@@
 	\label{table:usagetable}
-	\begin{tabular}{l|ll}
+	\begin{tabular}{l|l|l}
 		\toprule
@@
 		\textbf{(ms.pdf or empty)}          & debug/development    & release paper             \\
+		\midrule
 		\textbf{test}                       & test reproducibility & test reproducibility full \\
@@
 This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
-For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
+For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
+\begin{itemize}
+	\item MNIST~\cite{lecun2010mnist},
+	\item FashionMNIST~\cite{xiao2017fashion},
+	\item KMNIST~\cite{clanuwat2018deep},
+	\item QMNIST~\cite{yadav2019cold},
+	\item EMNIST~\cite{cohen2017emnist},
+	\item CIFAR10~\cite{krizhevsky2009learning},
+	\item CIFAR100~\cite{krizhevsky2009learning} and
+	\item SVHN~\cite{netzer2011reading}.
+\end{itemize}
 
@@
 \begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
-random.seed(0) # for build-in random module
-np.random.seed(0) # for numpy
-tf.random.set_seed(0) # for Tensorflow
+# for build-in random module
+random.seed(0)
+# for numpy
+np.random.seed(0)
+# for tensorflow
+tf.random.set_seed(0)
 # for pytorch
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\textwidth]{results/validation-loss}}
-	\caption{Validation losses.
-	Image example created from \textit{results code}.}
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/MNIST-loss}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
+	\caption{Train and validation losses for MNIST and FashionMNIST.}
 	\label{fig:image}
@@
 	\setlength\tabcolsep{4.2pt}
-	\input{results/metrics.tex}
+	\scalebox{0.72}{\input{results/metrics.tex}}
 \end{table}

### 2020-09-19 main.py

@@ -19,7 +19,6 @@ plt.rcParams['savefig.format'] = 'pdf'
 
 dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
-num_fc_list = [9216, 9216, 9216, 9216, 9216, 12544, 12544, 135424, 12544]
 activation_function_list = ['ReLU', 'SELU']
 
 mean_std_list = [
@@ -79,8 +78,9 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
     if dataset_name == 'MNIST':
         plt.ylabel('loss', fontsize=15)
     for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
-        plt.plot(train_loss_, label=activation_function, color=color)
-        plt.plot(validation_loss_, label=activation_function, color=color)
+        plt.plot(train_loss_, label=f'Train {activation_function}', color=color)
+        plt.plot(validation_loss_, label=f'Validation {activation_function}', linestyle='--', color=color)
+    plt.title(dataset_name)
     ax.tick_params(axis='both', which='major', labelsize='large')
     ax.tick_params(axis='both', which='minor', labelsize='large')
     ax.xaxis.set_major_locator(MaxNLocator(integer=True))
@@ -113,9 +113,9 @@ if __name__ == '__main__':
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     if args.full:
-        num_epochs = 10
+        num_epochs = 20
     else:
-        num_epochs = 1
+        num_epochs = 2
         train_range_list = [train_range[:10] for train_range in train_range_list]
         validation_range_list = [validation_range[:10] for validation_range in validation_range_list]
         test_range_list = [test_range[:10] for test_range in test_range_list]
@@ -127,7 +127,7 @@ if __name__ == '__main__':
     test_batch_size = 1000
     num_parameters = np.zeros((len(activation_function_list)))
     criterion = nn.CrossEntropyLoss()
-    for index_dataset, (dataset, dataset_name, train_range, validation_range, test_range, mean_std, num_fc) in enumerate(zip(dataset_list, dataset_name_list, train_range_list, validation_range_list, test_range_list, mean_std_list, num_fc_list)):
[…]

### 2020-09-20 ms.tex
{make test}

@@
 The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
-The \textit{author} only needs to edit (or use the `touch' UNIX utility to force) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.
+The \textit{author} only needs to edit (or use the `touch' UNIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.
 
@@
 
+We split to train, validation and test datasets and compare the use of ReLU and SELU activation functions in a VGG11 model.
+The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
 Regarding \LaTeX\ a common culprit against reproducibility is the time-date metadata embedded in the pdf output.

### 2020-10-28 main.py
{make test} remove QMNIST and EMNIST to fit in github action runner

@@ -11,19 +11,17 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, SVHN
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN
 from torchvision.models import vgg11_bn
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
 
-dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST, EMNIST, CIFAR10, CIFAR100, SVHN]
+dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
 activation_function_list = ['ReLU', 'SELU']
 
 mean_std_list = [
-        ((0.1307,), (0.3081,)),
-        ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
@@ -37,8 +35,6 @@ train_range_list = [
         range(50000), 
         range(50000),
         range(50000),
-        range(50000),
-        range(600000),
         range(40000),
         range(40000),
         range(4000),
@@ -49,8 +45,6 @@ validation_range_list = [
         range(50000, 60000),
         range(50000, 60000),
         range(50000, 60000),
-        range(50000, 60000),
-        range(600000, 697932),
         range(40000, 50000),
         range(40000, 50000),
         range(4000, 5000),
@@ -61,8 +55,6 @@ test_range_list = [
         range(10000),
         range(10000),
         range(10000),
-        range(10000),
-        range(116323),
         range(10000),
         range(10000),
         range(8000),
@@ -128,7 +120,7 @@ if __name__ == '__main__':
     num_parameters = np.zeros((len(activation_function_list)))
     criterion = nn.CrossEntropyLoss()
[…]

### 2020-11-17 main.py
further simplification

@@ -89,18 +89,19 @@ def change_relu_to_selu(model):
 
 
 if __name__ == '__main__':
-    # DO NOT EDIT BLOCK
-    np.random.seed(0)
-    torch.backends.cudnn.benchmark = False
-    torch.backends.cudnn.deterministic = True
-    torch.manual_seed(0)
-
+    # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
     parser.add_argument('cache_dir')
     parser.add_argument('results_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
+
+    # Set random seeds for reproducibility.
+    np.random.seed(0)
+    torch.backends.cudnn.benchmark = False
+    torch.backends.cudnn.deterministic = True
+    torch.manual_seed(0)
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     if args.full:

### 2020-11-18 ms.tex
{make test} remove QMNIST and EMNIST to fit in github action runner
change name of project

@@
 
-\title{Reproducible Builds for\\ Computational Research Papers}
+\title{Docker as a Development Environment for Research Papers}
 
@@
 We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
@@
 	\item KMNIST~\cite{clanuwat2018deep},
-	\item QMNIST~\cite{yadav2019cold},
-	\item EMNIST~\cite{cohen2017emnist},
 	\item CIFAR10~\cite{krizhevsky2009learning},

### 2020-11-25 ms.tex
fix README.md and change title

@@
 
-\title{Docker as a Development Environment for Research Papers}
+\title{Docker as a Development Environment for Documenting Results}
 
@@
 We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers}}.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
@@
 \bibliographystyle{IEEEtran}
-\bibliography{ms}
+\bibliography{ms.bib}
 

### 2020-11-29 ms.tex
Makefile simplification and title change

@@
 
-\title{Docker as a Development Environment for Documenting Results}
+\title{Documenting Results Generation using \LaTeX\ and Docker}
 
@@
 \begin{abstract}
-	Previous works in research reproducibility provided frameworks for writing reproducible research papers, however without considering the cost of extra work that needs to be done by the author to make the paper reproducible and by the reviewer to verify the paper's reproducibility.
-	We propose a simple template for writing computational research papers in \LaTeX\ that are easily verifiable in terms of their reproducibility.
-	The template contains a Makefile that allows the author/reviewer to execute the code that reproduces the figures, tables and variables (results) of the paper, which are then used during the \LaTeX\ compilation, to produce a pdf.
-	The previous procedure is completed twice and the paper is verified as reproducible, if and only if the pdf files are identical.
-	The two builds are needed to enable comparison between different builds of the same source code such that any non-deterministic stochasticity would produce different pdf files, thus making the paper non-reproducible.
-	The reproducibility of a paper can be verified either locally on the machine of the reviewer or remotely using Virtual Machines (VMs) in the cloud.
-	We release an open source template of \textit{reproducible builds} (RBs) and use it to write and verify the reproducibility of this paper.
+	Documenting computational results should be done in an as much as possible automatic way to ease the work of coauthors to write the document and the reviewing process.
+	We propose a simple template for documenting computational results using Docker and \LaTeX\ that can be used for generating reports and research papers.
+	The template contains a Makefile that allows the author/reviewer to execute the code that reproduces the figures, tables and variables (results) of the document, which are then used during the \LaTeX\ compilation, to produce the document.
+	We release an open source repository of the template and use it to write this paper.
 \end{abstract}
@@
 \section{Introduction}
-A research paper is considered reproducible when any reviewer is able to reproduce its results, given the data and experimental procedure.
+A document is considered reproducible when any reviewer is able to reproduce its results, given the data and experimental procedure.
 More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
@@
 We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results}}.
+We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/documenting-results-generation-using-latex-and-docker-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/documenting-results-generation-using-latex-and-docker}}.
 We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
@@
 \begin{itemize}
-	\item \textit{paper} as a computational research paper,
-	\item \textit{results} as the figures, tables and variables that are shown in the \textit{paper},
-	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex}) and bibliography (\textit{*.bib}) of the \textit{paper},
+	\item \textit{document} as a document embedded with computational results,
+	\item \textit{results} as the figures, tables and variables that are shown in the \textit{document},
+	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex}) and bibliography (\textit{*.bib}) of the \textit{document},
 	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py}) that produces the \textit{results},
 	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code},
-	\item \textit{author} as the author(s) of the \textit{paper} and
-	\item \textit{reviewer} as the reviewer(s) of the \textit{paper} or anyone interested in verifying the \textit{paper} (author(s), journal editors, other researchers).
+	\item \textit{author} as the author(s) of the \textit{document} and
+	\item \textit{reviewer} as the reviewer(s) of the \textit{document} or anyone interested in verifying the \textit{document} (author(s), journal editors, other researchers).
 \end{itemize}
@@
 				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(py) (dockerfile)](code){};
-				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(tex) (bib)](paper){};
+				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(tex) (bib)](document){};
 			\end{scope}
@@
 			\path[draw, ->] (code) -- node[above]{docker} (results);
-			\node[draw, right=4cm of paper, fill=white] (pdf) {pdf};
+			\node[draw, right=4cm of document, fill=white] (pdf) {pdf};
 			\path[draw, ->] (results) |- (pdf);
-			\path[draw, ->] (paper) -- node[above]{docker} (pdf);
+			\path[draw, ->] (document) -- node[above]{docker} (pdf);
 	\end{tikzpicture}
@@
 	\item the \textit{author} may execute \textit{make} during development and experimentation,
-	\item the \textit{author} may verify the reproducibility of the \textit{paper} locally by executing \textit{make test} (or remotely by commiting the code change with a message which contains \textit{\{make test\}}) which triggers the following:
+	\item the \textit{author} may verify the reproducibility of the \textit{document} locally by executing \textit{make test} (or remotely by commiting the code change with a message which contains \textit{\{make test\}}) which triggers the following:
 		\begin{enumerate}
@@
 			\item the previous is executed twice,
-			\item the \textit{paper} is verifed as reproducible if and only if the pdf files are identical.
+			\item the \textit{document} is verifed as reproducible if and only if the pdf files are identical.
 		\end{enumerate}
-	\item the \textit{reviewer} may verify the reproducibility of the paper locally (by cloning the repo and executing \textit{make test}) or remotely (by inspecting the result of \textit{\{make test\}}).
+	\item the \textit{reviewer} may verify the reproducibility of the document locally (by cloning the repo and executing \textit{make test}) or remotely (by inspecting the result of \textit{\{make test\}}).
 \end{enumerate}
 
-The reason that two local/remote compilations are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the \textit{paper} non-reproducible.
+The reason that two local/remote compilations are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the \textit{document} non-reproducible.
 Moreover Docker usage in RBs provides portability of the environment of the research while third-party VMs are used when the verification needs to be shared (in contrast with verifying locally, thus having low credibility in reporting reproducibility).
@@
 \begin{itemize}
-	\item preprint server (e.g.\ arXiv) \textit{paper} reproducibility verification and
+	\item preprint server (e.g.\ arXiv) \textit{document} reproducibility verification and
 	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
@@
 \begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
-SYNTAX
-make [OPTION] [ARGS=--full]
-
-OPTIONS
-ms.pdf - Generate pdf.
-test   - Test whether the paper has a reproducible build.
-clean  - Remove cache, results directories and tex aux files.
-help   - Show help.
-
+make             # Generate pdf.
+make ARGS=--full # Generate full pdf.
+make clean       # Remove results and tmp directories.
 \end{lstlisting}
 
-\begin{table}[]
-	\centering
-	\caption{Makefile usage table.}
-	\label{table:usagetable}
-	\begin{tabular}{l|l|l}
-		\toprule
-		\diagbox{\textbf{OPTION}}{\textbf{ARGS}} & \textbf{(empty)}              & \textbf{-{}-full}                    \\
-		\midrule
-		\textbf{(ms.pdf or empty)}          & debug/development    & release paper             \\
-		\midrule
-		\textbf{test}                       & test reproducibility & test reproducibility full \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Regarding research that is computational costly, the template allows the execution and reproducibility verification of a computationally lighter version of the \textit{paper} by default.
+Regarding research that is computational costly, the template allows the execution and reproducibility verification of a computationally lighter version of the \textit{document} by default.
 This also helps in faster iterations during research writing and experimentation.
@@
 Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-RBs provide a simple solution for writing and verifying the reproducibility of a `\textit{paper} as a whole', without having to trust a third-party.
+RBs provide a simple solution for writing and verifying the reproducibility of a `\textit{document} as a whole', without having to trust a third-party.
 Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party VMs cannot be trusted.

### 2020-11-29 main.py

@@ -19,7 +19,7 @@ plt.rcParams['savefig.format'] = 'pdf'
 
 dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
-activation_function_list = ['ReLU', 'SELU']
+activation_function_list = ['ReLU', 'SiLU']
 
 mean_std_list = [
         ((0.1307,), (0.3081,)),
@@ -83,7 +83,7 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
 def change_relu_to_selu(model):
     for child_name, child in model.named_children():
         if isinstance(child, nn.ReLU):
-            setattr(model, child_name, nn.SELU())
+            setattr(model, child_name, nn.SiLU())
         else:
             change_relu_to_selu(child)
 
@@ -91,8 +91,8 @@ def change_relu_to_selu(model):
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('cache_dir')
     parser.add_argument('results_dir')
+    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -134,13 +134,13 @@ if __name__ == '__main__':
                 transforms.Normalize(mean_std[0], mean_std[1])
                 ])
         if dataset_name == 'SVHN':
-            train_dataset = dataset(args.cache_dir, split='train', transform=transform, download=True)
-            validation_dataset = dataset(args.cache_dir, split='train', transform=transform)
-            test_dataset = dataset(args.cache_dir, split='test', transform=transform, download=True)
+            train_dataset = dataset(args.tmp_dir, split='train', transform=transform, download=True)
+            validation_dataset = dataset(args.tmp_dir, split='train', transform=transform)
+            test_dataset = dataset(args.tmp_dir, split='test', transform=transform, download=True)
         else:
-            train_dataset = dataset(args.cache_dir, train=True, transform=transform, download=True)
-            validation_dataset = dataset(args.cache_dir, train=True, transform=transform)
-            test_dataset = dataset(args.cache_dir, train=False, transform=transform, download=True)
+            train_dataset = dataset(args.tmp_dir, train=True, transform=transform, download=True)
+            validation_dataset = dataset(args.tmp_dir, train=True, transform=transform)
[…]

### 2020-11-30 main.py
simplify Makefile

@@ -61,7 +61,7 @@ test_range_list = [
         range(10000),
         ]
 
-def save_loss(train_loss, validation_loss, dataset_name, activation_function_list, results_dir):
+def save_loss(train_loss, validation_loss, dataset_name, activation_function_list):
     fig, ax = plt.subplots()
     plt.grid(True)
     plt.autoscale(enable=True, axis='x', tight=True)
@@ -77,7 +77,7 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
     ax.tick_params(axis='both', which='minor', labelsize='large')
     ax.xaxis.set_major_locator(MaxNLocator(integer=True))
     ax.legend()
-    plt.savefig(f'{results_dir}/{dataset_name}-loss', bbox_inches='tight')
+    plt.savefig(f'tmp/{dataset_name}-loss', bbox_inches='tight')
     plt.close()
 
 def change_relu_to_selu(model):
@@ -91,8 +91,6 @@ def change_relu_to_selu(model):
 if __name__ == '__main__':
     # DO NOT EDIT BLOCK - Required by the Makefile
     parser = argparse.ArgumentParser()
-    parser.add_argument('results_dir')
-    parser.add_argument('tmp_dir')
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
     # END OF DO NOT EDIT BLOCK
@@ -134,13 +132,13 @@ if __name__ == '__main__':
                 transforms.Normalize(mean_std[0], mean_std[1])
                 ])
         if dataset_name == 'SVHN':
-            train_dataset = dataset(args.tmp_dir, split='train', transform=transform, download=True)
-            validation_dataset = dataset(args.tmp_dir, split='train', transform=transform)
-            test_dataset = dataset(args.tmp_dir, split='test', transform=transform, download=True)
+            train_dataset = dataset('tmp', split='train', transform=transform, download=True)
+            validation_dataset = dataset('tmp', split='train', transform=transform)
+            test_dataset = dataset('tmp', split='test', transform=transform, download=True)
         else:
-            train_dataset = dataset(args.tmp_dir, train=True, transform=transform, download=True)
-            validation_dataset = dataset(args.tmp_dir, train=True, transform=transform)
-            test_dataset = dataset(args.tmp_dir, train=False, transform=transform, download=True)
+            train_dataset = dataset('tmp', train=True, transform=transform, download=True)
[…]

### 2020-12-07 ms.tex
simplify Makefile
major changes

@@
 \usepackage{datatool}
-\usepackage{diagbox}
+\usepackage{flushend}
 \usepackage{listings}
-\usepackage{makecell}
 \usepackage{tikz}
@@
 
-\lstdefinestyle{lststyle}{
-	aboveskip=10pt,
-	belowskip=10pt,
-	frame=single,
-	basicstyle=\tt\scriptsize,
-	commentstyle=\color{gray}}
+\lstdefinestyle{lststyle}{basicstyle=\tt\footnotesize, captionpos=b, frame=single}
 
 \begin{document}
-\DTLloaddb{keys_values}{results/keys-values.csv}
+\DTLloaddb{keys_values}{tmp/keys-values.csv}
 
-\title{Documenting Results Generation using \LaTeX\ and Docker}
+\title{\LaTeX\ Technical Documents with Docker and Make}
 
@@
 \begin{abstract}
-	Documenting computational results should be done in an as much as possible automatic way to ease the work of coauthors to write the document and the reviewing process.
-	We propose a simple template for documenting computational results using Docker and \LaTeX\ that can be used for generating reports and research papers.
-	The template contains a Makefile that allows the author/reviewer to execute the code that reproduces the figures, tables and variables (results) of the document, which are then used during the \LaTeX\ compilation, to produce the document.
+	We propose a template for writing portable \LaTeX\ technical documents with Docker and \textit{Make} in POSIX-oriented operating systems.
+	The template provides a Makefile that allows the author to execute the code that generates the figures, tables and variables (results), which are then used during the \LaTeX\ compilation, to produce the fast/draft and slow/final versions of the document.
 	We release an open source repository of the template and use it to write this paper.
@@
 \section{Introduction}
-A document is considered reproducible when any reviewer is able to reproduce its results, given the data and experimental procedure.
-More specifically, computational research reproducibility requires the presence of source code that produces or fetches data from external sources which then transforms into the figures, tables and variables of the paper.
-Open sourcing the code and the raw data of a computational research paper increases the confidence in its reproducibility but it is not enough to verify it.
-Using a template both for writing and verifying computational research papers will push the direction towards creating reproducible research, thus tackling the `reproducibility crisis' problem.
+There are multiple ways for writing technical documents that present both computationally generated results (figures, tables and variables) and natural text.
+One programming paradigm that tries to solve this task is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its executed output alongside natural text.
+Some applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
 
-We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
-We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/documenting-results-generation-using-latex-and-docker-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/documenting-results-generation-using-latex-and-docker}}.
-We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.
+Although \textit{literate programming} provides many advantages for demonstrative projects and easy visual feedback during experimentation, its `dual nature' makes it difficult to debug and constrains authors in using specific text editors and programming languages thus leading to `app/vendor lock-in` situations.
+
+We propose a template for writing portable \LaTeX\ technical documents with Docker and \textit{Make} in POSIX-oriented operating systems and provide an open source implementation\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}}.
+We write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}} using this template and choose the Python programming language~\cite{van2007python} for generating the results.
 
@@
 \begin{itemize}
-	\item \textit{document} as a document embedded with computational results,
-	\item \textit{results} as the figures, tables and variables that are shown in the \textit{document},
-	\item \textit{\LaTeX\ code} as the files containing the main text (\textit{*.tex}) and bibliography (\textit{*.bib}) of the \textit{document},
-	\item \textit{results code} as the files containing the scientific-oriented programming language code (\textit{*.py}) that produces the \textit{results},
+	\item \textit{results} as the figures, tables and variables that are generated from a computation,
+	\item \textit{results code} as the scientific-oriented programming language code (\textit{main.py}) that produces the \textit{results},
+	\item \textit{\LaTeX\ code} as the natural text (\textit{ms.tex}) and bibliography (\textit{ms.bib}),
 	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code},
-	\item \textit{author} as the author(s) of the \textit{document} and
-	\item \textit{reviewer} as the reviewer(s) of the \textit{document} or anyone interested in verifying the \textit{document} (author(s), journal editors, other researchers).
+	\item \textit{document} as the technical document that contains the rendered natural text and \textit{results} and
+	\item \textit{author} as the author of the \textit{document} that writes and develops the \textit{code}.
 \end{itemize}
 
-\section{Reproducible Builds Template}
+\section{Template}
 
@@
 			edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
-			\node[draw](root){root}
+			\node[draw](document){document/}
 			child{node[draw, anchor=west](makefile){Makefile}}
+			child{node[draw, anchor=west](tmp){tmp/}}
 			child{node[draw, anchor=west, fill=red!20](tex){ms.tex}}
@@
 			child{node[draw, anchor=west, fill=blue!20](py){main.py}}
-			child{node[draw, anchor=west, fill=blue!20](dockerfile){Dockerfile}};
+			child{node[draw, anchor=west, fill=blue!20](dockerfile){Dockerfile}}
+			child{node[draw, anchor=west, fill=blue!20](requirements){requirements.txt}};
 			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!20, inner sep=4pt, fit=(root) (dockerfile)]{};
-				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(py) (dockerfile)](code){};
+				\node[draw, rounded corners, dashed, fill=gray!20, inner sep=4pt, fit=(document) (requirements)]{};
+				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(py) (requirements)](code){};
 				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(tex) (bib)](document){};
 			\end{scope}
-			\node[draw, right=2cm of code, fill=white] (results) {results};
+			\node[draw, right=1.5cm of code, fill=white] (results) {tmp/results};
 			\path[draw, ->] (code) -- node[above]{docker} (results);
-			\node[draw, right=4cm of document, fill=white] (pdf) {pdf};
+			\node[draw, right=4cm of document, fill=white] (pdf) {tmp/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
@@
 	\end{tikzpicture}
-	\caption{The RBs template file hierarchy is depicted in the light gray background and the arrows denote the data flow towards generating the pdf.
-	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background, files that are used for a subsequent step.}
+	\caption{The file hierarchy of the template is depicted in the light gray background and the arrows denote the data flow towards generating the \textit{document}.
+	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background, files that are developed by the \textit{author}.}
 	\label{fig:filehierarchyworkflow}
@@
 
-The proposed template can be used for writing \textit{papers} with \LaTeX~\cite{lamport1994latex} and the \textit{results code} that can be executed within a Docker container.
-\LaTeX\ is a typesetting system for publishing high quality research papers, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments and has shown great promise in reproducible research~\cite{boettiger2015introduction}.
+\LaTeX~\cite{lamport1994latex} is a typesetting system for publishing high quality research documents, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments.
 
-A specific file hierarchy is shown in Fig.~\ref{fig:filehierarchyworkflow} however this is optional, as the template only needs to know the directories of the main files of the \LaTeX\ and \textit{results code} during its creation.
-The Makefile and Dockerfile are automatically generated by the template after user prompts.
-For more complicated setups the Dockerfile can be provided by the \textit{author} or generated by tools such as repo2docker~\cite{forde2018reproducible}.
+The proposed template can be used for writing \LaTeX\ \textit{documents} that present \textit{results} generated from \textit{results code} executed within a Docker container.
+The file hierarchy of the template is shown in Fig.\ref{fig:filehierarchyworkflow}.
 
-The template fits in research writing and reproducibility verification in the following way:
+The \textit{author} may use the template for writing \textit{documents} in the following way:
 \begin{enumerate}
-	\item the \textit{author} edits the \textit{code} in the local repository,
-	\item the \textit{author} may execute \textit{make} during development and experimentation,
-	\item the \textit{author} may verify the reproducibility of the \textit{document} locally by executing \textit{make test} (or remotely by commiting the code change with a message which contains \textit{\{make test\}}) which triggers the following:
+	\item clones the template,
+	\item specifies the name of the \textit{document} in the Makefile,
+	\item develops the Dockerfile,
+	\item develops the \textit{code} in the local repository,
 		\begin{enumerate}
-			\item the \textit{results code} is executed,
-			\item the \textit{results} along with the \textit{\LaTeX\ code} are used to compile a pdf file,
-			\item the previous is executed twice,
-			\item the \textit{document} is verifed as reproducible if and only if the pdf files are identical.
+			\item develops the fast/draft and slow/final version \textit{document} in \textit{code},
+			\item develops the saving/loading of \textit{results} in/from the \textit{tmp} directory,
 		\end{enumerate}
-	\item the \textit{reviewer} may verify the reproducibility of the document locally (by cloning the repo and executing \textit{make test}) or remotely (by inspecting the result of \textit{\{make test\}}).
+	\item executes \textit{make} for generating the fast/draft version \textit{document} used during development and experimentation,
+	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution.
+	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory,
 \end{enumerate}
 
-The reason that two local/remote compilations are needed is to enable comparison between different builds of the same source code and any non-deterministic stochasticity (such as not applying a specific seed to random generators) would produce different pdfs, thus making the \textit{document} non-reproducible.
-Moreover Docker usage in RBs provides portability of the environment of the research while third-party VMs are used when the verification needs to be shared (in contrast with verifying locally, thus having low credibility in reporting reproducibility).
+The fast/draft version \textit{document} helps in faster iterations during writing and experimentation.
+An example of creating a fast/draft version in the field of neural networks is setting the number of epochs and number of training samples to a low value.
 
-Additional constraints could be imposed in the VMs such as disallowing image files in the \textit{code} and monitoring the network connections of the \textit{code} to help the \textit{reviewer} check whether the \textit{results} are generated from the \textit{code} and are not fetched from an external source.
+The template makes use of the automatic generation of intermediate files of the \textit{Make} program.
+The \textit{author} only needs to edit (or use the \textit{touch} Unix utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with \textit{Make}.
 
-Potential uses of the RBs template include:
-\begin{itemize}
-	\item preprint server (e.g.\ arXiv) \textit{document} reproducibility verification and
-	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
-\end{itemize}
-
-\subsection{Technical implementation}
-Executing RBs can be done using the following:
-\begin{lstlisting}[language=Bash, style=lststyle, caption={Makefile call syntax from the shell.}, captionpos=b]
-make             # Generate pdf.
-make ARGS=--full # Generate full pdf.
-make clean       # Remove results and tmp directories.
+A useful \LaTeX\ package for automatically presenting variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (tmp/keys\_values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
+\DTLloaddb{keys_values}{tmp/keys_values.csv}
+\DTLfetch{keys_values}{key}{lr}{value}
 \end{lstlisting}
 
-Regarding research that is computational costly, the template allows the execution and reproducibility verification of a computationally lighter version of the \textit{document} by default.
-This also helps in faster iterations during research writing and experimentation.
-An example of computationally lighter versions in the field of neural networks is setting the number of epochs and number of training samples to a low value.
-The execution of the full experiment is done by providing an additional argument.
+Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
+\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}]
+df = pd.DataFrame(table)
+df.to_latex("tmp/metrics.tex", float_format="%.2f")
+\end{lstlisting}
 
-The RB template takes advantage of the automatic generation of intermediate files of the `make' program.
-The \textit{author} only needs to edit (or use the `touch' UNIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with `make'.
-
-In this implementation of RBs the remote reproducibility verification is done using Github Actions, the builder VM uses the latest version of Ubuntu and pulls a docker image for building \LaTeX\ from the Github Container Registry.
-
-\section{Example Use Case of RBs}
-This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
-For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
-\begin{itemize}
-	\item MNIST~\cite{lecun2010mnist},
-	\item FashionMNIST~\cite{xiao2017fashion},
-	\item KMNIST~\cite{clanuwat2018deep},
-	\item CIFAR10~\cite{krizhevsky2009learning},
-	\item CIFAR100~\cite{krizhevsky2009learning} and
-	\item SVHN~\cite{netzer2011reading}.
-\end{itemize}
-
-We split to train, validation and test datasets and compare the use of ReLU and SELU activation functions in a VGG11 model.
-The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
-Regarding \LaTeX\ a common culprit against reproducibility is the time-date metadata embedded in the pdf output.
-These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the RB Makefile):
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}, captionpos=b]
+Regarding \LaTeX\ a culprit against reproducibility is the time-date metadata embedded in the pdf output.
+These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the template Makefile):
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}]
 \pdfinfoomitdate=1
@@
 
-A useful \LaTeX\ package for automatically embedding variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (keys\_values.csv) generated by a \textit{results code} and getting the value of a key named lr.}, captionpos=b]
-\DTLloaddb{keys_values}{keys_values.csv}
-\DTLfetch{keys_values}{key}{lr}{value}
-\end{lstlisting}
-
-For example the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the \textit{results code}:
-\begin{itemize}
-	\item the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$,
-	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
-	\item the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
-\end{itemize}
-
 Regarding the \textit{results code} for Python, random seeds need to be set to a specific value such as:
-\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
+\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}]
 # for build-in random module
@@
 
-Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
-For example Fig.~\ref{fig:image} depicts the train and validation loss for all datasets.
+Setting the random seeds and the previously mentioned \LaTeX\ packages we could have deterministic stochasticity that generates figures, tables and variables.
+
+Potential uses of the template include:
+\begin{itemize}
+	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
+	\item common environment across multiple \textit{authors},
+	\item reviewer, coauthor(s), journal editors or other researchers can easily reproduce the \textit{document} with minimal requirements.
+\end{itemize}
+
+In cases where reproducibility is required, the potential differences in the resulting \textit{document} binary can be identified using tools such as diffoscope\footnote{\url{https://diffoscope.org/}} and the cache files saved at the tmp directory after execution.
+
+\section{Example use case of the template}
+This sections provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
+We train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
+\begin{itemize}
+	\item MNIST~\cite{lecun2010mnist},
+	\item FashionMNIST~\cite{xiao2017fashion},
+	\item KMNIST~\cite{clanuwat2018deep},
+	\item CIFAR10~\cite{krizhevsky2009learning},
+	\item CIFAR100~\cite{krizhevsky2009learning} and
+	\item SVHN~\cite{netzer2011reading}.
+\end{itemize}
+
+We use the default train, validation and test datasets and compare the use of ReLU\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
+The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
+
+Making use of the \textit{datatool} package the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the \textit{results code}:
+\begin{itemize}
+	\item the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$,
+	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
+	\item the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
+\end{itemize}
+
+Making use of setting the random seeds we consistenly get the same figures as shown in Fig.\ref{fig:image} which depicts the train and validation loss for all datasets.
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/MNIST-loss}}
-	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/MNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/FashionMNIST-loss.pdf}}
 	\caption{Train and validation losses for MNIST and FashionMNIST.}
@@
 \end{figure}
-
-Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
-
-\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}, captionpos=b]
-num_columns = 11
-table = np.random.random((7, num_columns))
-df = pd.DataFrame(table)
-df.to_latex('metrics.tex', float_format="%.2f")
-\end{lstlisting}
 
@@
 	\label{table:table}
-	\setlength\tabcolsep{4.2pt}
-	\scalebox{0.72}{\input{results/metrics.tex}}
+	\setlength\tabcolsep{2pt}
+	\input{tmp/metrics.tex}
 \end{table}
@@
 \section{Discussion}
-RBs are based on plain text files and are independent of any specific version control and docker registry providor thus preventing `vendor lock-in' situations.
-Previous works in this area such as Hurlin et al.~\cite{hurlin2019reproducibility} propose an `external certification agency' for economic studies.
-RBs provide a simple solution for writing and verifying the reproducibility of a `\textit{document} as a whole', without having to trust a third-party.
-Anyone can clone a repository written with RBs and locally verify its reproducibility, in case third party VMs cannot be trusted.
-Similar to RBs is ReDoc~\cite{schwab2000making} which however focuses on separate result file reproducibility and requires the author to write each rule in the Makefile for each result file.
-RBs on the other hand provides a Makefile that is automatically generated by the template.
+The proposed template is based on plain text files and can be used with any POSIX-oriented operating that supports Docker and \textit{Make}.
+Moreover it can be combined with any version control system, docker container registry providor and text editor thus preventing `app/vendor lock-in' situations.
 
 \section{Conclusion}
-Automating research reproducibility verification is becoming more important due to the increasing research output that has been observed in the last few years.
-Few works were done on this area, mostly proposing trust on an external third party.
-RBs help in writing and verifying reproducible research using the tools that most of the researchers already use (\LaTeX, Docker).
+Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
+The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker).
 

### 2020-12-07 main.py

@@ -96,7 +96,7 @@ if __name__ == '__main__':
     # END OF DO NOT EDIT BLOCK
 
     # Set random seeds for reproducibility.
-    np.random.seed(0)
+    #np.random.seed(0)
     torch.backends.cudnn.benchmark = False
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)

### 2020-12-07 main.py
fix README.md and seed

@@ -96,7 +96,7 @@ if __name__ == '__main__':
     # END OF DO NOT EDIT BLOCK
 
     # Set random seeds for reproducibility.
-    #np.random.seed(0)
+    np.random.seed(0)
     torch.backends.cudnn.benchmark = False
     torch.backends.cudnn.deterministic = True
     torch.manual_seed(0)

### 2020-12-08 ms.tex
various major changes

@@
 
-\author{Paschalis~Bizopoulos and Dimitris~Bizopoulos
-\thanks{P. Bizopoulos and D. Bizopoulos are Independent Researchers, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com, dimitrisbizopoulos@gmail.com}}
+\author{Paschalis~Bizopoulos
+\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com}}
 
@@
 \begin{abstract}
-	We propose a template for writing portable \LaTeX\ technical documents with Docker and \textit{Make} in POSIX-oriented operating systems.
-	The template provides a Makefile that allows the author to execute the code that generates the figures, tables and variables (results), which are then used during the \LaTeX\ compilation, to produce the fast/draft and slow/final versions of the document.
+	We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems.
+	The template provides a Makefile that allows the author to execute the code that generates the variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce the fast/draft and slow/final versions of the document.
 	We release an open source repository of the template and use it to write this paper.
@@
 \section{Introduction}
-There are multiple ways for writing technical documents that present both computationally generated results (figures, tables and variables) and natural text.
-One programming paradigm that tries to solve this task is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its executed output alongside natural text.
+There are multiple ways for writing technical documents that present both computationally generated results (variables, tables and figures) and natural text.
+One programming paradigm that tries to solve this task is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its execution output alongside natural text.
 Some applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
@@
 
-We propose a template for writing portable \LaTeX\ technical documents with Docker and \textit{Make} in POSIX-oriented operating systems and provide an open source implementation\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}}.
-We write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}} using this template and choose the Python programming language~\cite{van2007python} for generating the results.
+We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems and provide an open source implementation\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}}.
+We write this paper\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using this template and choose the Python programming language~\cite{van2007python} for generating the results.
 
@@
 \begin{itemize}
-	\item \textit{results} as the figures, tables and variables that are generated from a computation,
-	\item \textit{results code} as the scientific-oriented programming language code (\textit{main.py}) that produces the \textit{results},
+	\item \textit{results code} as the scientific-oriented programming language code (\textit{main.py}) that produces the variables, tables and figures,
+	\item \textit{results} as the variables, tables and figures that are generated by the \textit{results code},
 	\item \textit{\LaTeX\ code} as the natural text (\textit{ms.tex}) and bibliography (\textit{ms.bib}),
@@
 
-The template makes use of the automatic generation of intermediate files of the \textit{Make} program.
-The \textit{author} only needs to edit (or use the \textit{touch} Unix utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with \textit{Make}.
+The template makes use of the automatic generation of intermediate files of the Make program.
+The \textit{author} only needs to edit (or use the \textit{touch} POSIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.
 
@@
 
-Setting the random seeds and the previously mentioned \LaTeX\ packages we could have deterministic stochasticity that generates figures, tables and variables.
+Setting the random seeds and the previously mentioned \LaTeX\ packages we could have deterministic stochasticity that generates variables, tables and figures.
 
@@
 
-In cases where reproducibility is required, the potential differences in the resulting \textit{document} binary can be identified using tools such as diffoscope\footnote{\url{https://diffoscope.org/}} and the cache files saved at the tmp directory after execution.
+In cases where reproducibility checks are required, the POSIX utility \textit{cmp} can be used.
+For specifically identifying the sources of non-determinism an author can use tools such as diffoscope\footnote{\url{https://diffoscope.org/}} in the resulting \textit{document} binaries as follows:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Test fast/draft document reproducibility.}]
+# Generate the first fast/draft document version
+make
+# Backup the first resulting pdf
+cp tmp/ms.pdf tmp/ms-previous.pdf
+# Update the modification timestamp of main.py
+touch main.py
+# Generate the second fast/draft document version
+make
+# Compare fast/draft document versions byte by byte
+cmp tmp/ms.pdf tmp/ms-previous.pdf
+# Compare fast/draft document versions
+# in a human readable form
+diffoscope tmp/ms.pdf tmp/ms-previous.pdf
+\end{lstlisting}
 
@@
 \section{Discussion}
-The proposed template is based on plain text files and can be used with any POSIX-oriented operating that supports Docker and \textit{Make}.
+The proposed template is based on plain text files and can be used with any POSIX-oriented operating that supports Docker and Make.
 Moreover it can be combined with any version control system, docker container registry providor and text editor thus preventing `app/vendor lock-in' situations.
@@
 Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
-The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker).
+The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make).
 

### 2020-12-08 main.py

@@ -12,7 +12,7 @@ from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
 from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN
-from torchvision.models import vgg11_bn
+from torchvision.models import mobilenet_v2
 
 plt.rcParams['font.size'] = 12
 plt.rcParams['savefig.format'] = 'pdf'
@@ -80,12 +80,12 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
     plt.savefig(f'tmp/{dataset_name}-loss', bbox_inches='tight')
     plt.close()
 
-def change_relu_to_selu(model):
+def change_module(model, module_old, module_new):
     for child_name, child in model.named_children():
-        if isinstance(child, nn.ReLU):
-            setattr(model, child_name, nn.SiLU())
+        if isinstance(child, module_old):
+            setattr(model, child_name, module_new())
         else:
-            change_relu_to_selu(child)
+            change_module(child, module_old, module_new)
 
 
 if __name__ == '__main__':
@@ -147,9 +147,9 @@ if __name__ == '__main__':
         else:
             num_classes = len(train_dataset.classes)
         for index_activation_function, activation_function in enumerate(activation_function_list):
-            model = vgg11_bn().to(device)
+            model = mobilenet_v2().to(device)
             if activation_function == 'SiLU':
-                change_relu_to_selu(model)
+                change_module(model, nn.ReLU6, nn.SiLU)
             num_parameters[index_activation_function] = sum(p.numel() for p in model.parameters() if p.requires_grad)
             optimizer = optim.SGD(model.parameters(), lr=lr)
             validation_loss_best = float('inf')
@@ -189,9 +189,9 @@ if __name__ == '__main__':
                     validation_loss_best = validation_loss
                     torch.save(model.state_dict(), model_path)
                     print('saving as best model')
-            model = vgg11_bn().to(device)
+            model = mobilenet_v2().to(device)
             if activation_function == 'SiLU':
-                change_relu_to_selu(model)
+                change_module(model, nn.ReLU6, nn.SiLU)
             model.load_state_dict(torch.load(model_path))
             model.eval()
             correct = 0

### 2020-12-08 ms.tex
improve paper

@@
 \usepackage{datatool}
-\usepackage{flushend}
 \usepackage{listings}
@@
 	\item specifies the name of the \textit{document} in the Makefile,
-	\item develops the Dockerfile,
-	\item develops the \textit{code} in the local repository,
+	\item creates and develops the Dockerfile,
+	\item creates and develops the \textit{code} in the local repository including code for:
 		\begin{enumerate}
-			\item develops the fast/draft and slow/final version \textit{document} in \textit{code},
-			\item develops the saving/loading of \textit{results} in/from the \textit{tmp} directory,
+			\item generating fast/draft and slow/final version \textit{document} in \textit{code} and
+			\item saving/loading the \textit{results} in/from the \textit{tmp} directory,
 		\end{enumerate}
 	\item executes \textit{make} for generating the fast/draft version \textit{document} used during development and experimentation,
-	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution.
-	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory,
+	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution and
+	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory.
 \end{enumerate}
@@
 The template makes use of the automatic generation of intermediate files of the Make program.
-The \textit{author} only needs to edit (or use the \textit{touch} POSIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.
+The \textit{author} only needs to edit a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.
+Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time.
+
+\section{Template utilities}
 
@@
 
-Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
+Another useful function when using Python for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
 \begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}]
@@
 
-Potential uses of the template include:
-\begin{itemize}
-	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
-	\item common environment across multiple \textit{authors},
-	\item reviewer, coauthor(s), journal editors or other researchers can easily reproduce the \textit{document} with minimal requirements.
-\end{itemize}
-
-In cases where reproducibility checks are required, the POSIX utility \textit{cmp} can be used.
-For specifically identifying the sources of non-determinism an author can use tools such as diffoscope\footnote{\url{https://diffoscope.org/}} in the resulting \textit{document} binaries as follows:
+An \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, OS or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test fast/draft document reproducibility.}]
@@
 This sections provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
-We train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
+We train and test a MobilenetV2 neural network~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
 \begin{itemize}
@@
 
-We use the default train, validation and test datasets and compare the use of ReLU\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
+We use the default train, validation and test datasets and compare the use of ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
 The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
@@
 	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/FashionMNIST-loss.pdf}}
-	\caption{Train and validation losses for MNIST and FashionMNIST.}
+	\\
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/KMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/CIFAR10-loss.pdf}}
+	\\
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/CIFAR100-loss.pdf}}
+	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/SVHN-loss.pdf}}
+	\caption{Comparison of ReLU6 and SiLU train and validation losses for all datasets.}
 	\label{fig:image}
@@
 
+Potential uses of the template include:
+\begin{itemize}
+	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
+	\item common environment across multiple \textit{authors},
+	\item reviewer, coauthor(s), journal editors or other researchers can easily reproduce the \textit{document} with minimal requirements.
+\end{itemize}
+
 \section{Conclusion}
 Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
-The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make).
+The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make) in a portable and efficient way.
 

### 2020-12-08 main.py

@@ -67,7 +67,7 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
     plt.autoscale(enable=True, axis='x', tight=True)
     plt.ylim([0, 1])
     plt.xlabel('Epochs', fontsize=15)
-    if dataset_name == 'MNIST':
+    if dataset_name in ['MNIST', 'KMNIST', 'CIFAR100']:
         plt.ylabel('loss', fontsize=15)
     for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
         plt.plot(train_loss_, label=f'Train {activation_function}', color=color)

### 2020-12-10 ms.tex
fix ms.tex main.py

--- 2020-12-08 ms.tex
@@
 	We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems.
-	The template provides a Makefile that allows the author to execute the code that generates the variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce the fast/draft and slow/final versions of the document.
+	The template provides a Makefile for executing the code that generates variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce either the draft (fast) or full (slow) version of the document.
+	We also present various utilities that aid in automating the results generation and increasing the reproducibility of the document.
 	We release an open source repository of the template and use it to write this paper.
@@
 \section{Introduction}
-There are multiple ways for writing technical documents that present both computationally generated results (variables, tables and figures) and natural text.
-One programming paradigm that tries to solve this task is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its execution output alongside natural text.
+Writing technical documents that present both computationally generated results (variables, tables and figures) and natural text, is one of the central aspects of computational research.
+One programming paradigm that has been proposed as a solution is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its execution output alongside natural text.
 Some applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
 
-Although \textit{literate programming} provides many advantages for demonstrative projects and easy visual feedback during experimentation, its `dual nature' makes it difficult to debug and constrains authors in using specific text editors and programming languages thus leading to `app/vendor lock-in` situations.
+Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors thus leading to `app/vendor lock-in` situations.
+Moreover this overlap between natural text and results code makes \textit{literate programming} difficult to debug and version control.
 
-We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems and provide an open source implementation\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}}.
-We write this paper\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using this template and choose the Python programming language~\cite{van2007python} for generating the results.
+We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems.
+We write this paper\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using this template\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}} and choose the Python programming language~\cite{van2007python} for generating the results.
 
@@
 			child{node[draw, anchor=west](makefile){Makefile}}
-			child{node[draw, anchor=west](tmp){tmp/}}
+			child{node[draw, anchor=west, fill=green!20](tmp){tmp/}}
 			child{node[draw, anchor=west, fill=red!20](tex){ms.tex}}
@@
 			\end{scope}
-			\node[draw, right=1.5cm of code, fill=white] (results) {tmp/results};
+			\node[draw, right=1.5cm of code, fill=green!20] (results) {tmp/results};
 			\path[draw, ->] (code) -- node[above]{docker} (results);
-			\node[draw, right=4cm of document, fill=white] (pdf) {tmp/ms.pdf};
+			\node[draw, right=4cm of document, fill=green!20] (pdf) {tmp/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
@@
 	\end{tikzpicture}
-	\caption{The file hierarchy of the template is depicted in the light gray background and the arrows denote the data flow towards generating the \textit{document}.
-	Blue indicates a \textit{results code} file, red a \textit{\LaTeX\ code} file and within the dark gray background, files that are developed by the \textit{author}.}
-	\label{fig:filehierarchyworkflow}
+	\caption{The files of the template is depicted in the light gray background and the arrows denote the data flow towards generating the \textit{document}.
+	Green indicates temporary cache/generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}
+	\label{fig:templatefiles}
 \end{figure}
@@
 
-The proposed template can be used for writing \LaTeX\ \textit{documents} that present \textit{results} generated from \textit{results code} executed within a Docker container.
-The file hierarchy of the template is shown in Fig.\ref{fig:filehierarchyworkflow}.
+The proposed template can be used for writing \LaTeX\ \textit{documents} that present \textit{results} generated from \textit{results code} executed within a Docker container with a consistent (across different hardware, OS and programming language), minimal user interface as follows:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Template make options.}]
+make             # Generate the draft (fast) version.
+make ARG=--full  # Generate the full (slow) version.
+make clean       # Remove the tmp/ directory.
+\end{lstlisting}
 
@@
 \begin{enumerate}
-	\item clones the template,
+	\item clones the template which consists of a set of files as depicted in Fig.\ref{fig:templatefiles},
 	\item specifies the name of the \textit{document} in the Makefile,
-	\item develops the Dockerfile,
-	\item develops the \textit{code} in the local repository,
+	\item creates and develops the \textit{results code} which includes:
 		\begin{enumerate}
-			\item develops the fast/draft and slow/final version \textit{document} in \textit{code},
-			\item develops the saving/loading of \textit{results} in/from the \textit{tmp} directory,
+			\item \textit{main.py},
+			\item \textit{Dockerfile},
+			\item generating the draft and full version \textit{document} in \textit{results code} and
+			\item saving \textit{results} in the \textit{tmp/} directory.
 		\end{enumerate}
-	\item executes \textit{make} for generating the fast/draft version \textit{document} used during development and experimentation,
-	\item executes \textit{make ARG=-{}-full} for generating the slow/final version \textit{document} used for distribution.
-	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp} directory,
+	\item creates and develops the \textit{\LaTeX\ code} which includes:
+		\begin{enumerate}
+			\item \textit{ms.tex} and \textit{ms.bib},
+			\item loading \textit{results} from the \textit{tmp/} directory.
+		\end{enumerate}
+	\item executes \textit{make} for generating the draft version \textit{document} used during development and experimentation,
+	\item executes \textit{make ARG=-{}-full} for generating the full version \textit{document} used for distribution or publication and
+	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp/} directory.
 \end{enumerate}
 
-The fast/draft version \textit{document} helps in faster iterations during writing and experimentation.
-An example of creating a fast/draft version in the field of neural networks is setting the number of epochs and number of training samples to a low value.
+The only restriction that the template imposes on the \textit{results code} is that the default execution should generate the draft version \textit{document} and the presence of an optional argument (-{}-full) for generating the full version.
+The draft version \textit{document} (generated when calling \textit{make}) helps in faster iterations during writing and experimentation.
+An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
 
-The template makes use of the automatic generation of intermediate files of the Make program.
-The \textit{author} only needs to edit (or use the \textit{touch} POSIX utility to update the modification time) a file from \textit{results code} or \textit{\LaTeX\ code} and the corresponding compilation is automatically triggered with Make.
+The template makes use of the automatic generation of intermediate target files of the Make program.
+When the \textit{author} edits a file from \textit{results code} or \textit{\LaTeX\ code}, only the required compilation is automatically triggered with Make.
+Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time of a file.
+
+\section{Template utilities}
+In this section we present useful utilities that can be combined with the template to automate \textit{results} generation and improve the reproducibility of the \textit{document}.
 
@@
 
-Another useful function for Python is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}).
-\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame to \LaTeX\ table.}]
+When using Python, a useful function for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table:
+\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (tmp/metrics.tex) in \textit{results code}.}]
 df = pd.DataFrame(table)
@@
 
-Regarding \LaTeX\ a culprit against reproducibility is the time-date metadata embedded in the pdf output.
-These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done in the template Makefile):
+There are some considerations need to be taken into account when reproducibility is needed.
+Regarding \LaTeX\, a culprit against reproducibility is the time-date metadata embedded in the pdf output.
+These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done by default in the template Makefile):
 \begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}]
@@
 
-Setting the random seeds and the previously mentioned \LaTeX\ packages we could have deterministic stochasticity that generates variables, tables and figures.
+Setting the random seeds and the previously mentioned \LaTeX\ packages, we could have deterministic stochasticity that generates the \textit{results}.
 
-Potential uses of the template include:
-\begin{itemize}
-	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter the results.
-	\item common environment across multiple \textit{authors},
-	\item reviewer, coauthor(s), journal editors or other researchers can easily reproduce the \textit{document} with minimal requirements.
-\end{itemize}
-
-In cases where reproducibility checks are required, the POSIX utility \textit{cmp} can be used.
-For specifically identifying the sources of non-determinism an author can use tools such as diffoscope\footnote{\url{https://diffoscope.org/}} in the resulting \textit{document} binaries as follows:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Test fast/draft document reproducibility.}]
-# Generate the first fast/draft document version
+Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, OS or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility.
+This can also be used as a test script for pushed commits and pull requests to a remote repository.}]
+# Generate the first draft document version
 make
@@
 touch main.py
-# Generate the second fast/draft document version
+# Generate the second draft document version
 make
-# Compare fast/draft document versions byte by byte
+# Compare draft document versions byte by byte
 cmp tmp/ms.pdf tmp/ms-previous.pdf
-# Compare fast/draft document versions
+# Compare draft document versions
 # in a human readable form
@@
 \section{Example use case of the template}
-This sections provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
-We train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
-\begin{itemize}
-	\item MNIST~\cite{lecun2010mnist},
-	\item FashionMNIST~\cite{xiao2017fashion},
-	\item KMNIST~\cite{clanuwat2018deep},
-	\item CIFAR10~\cite{krizhevsky2009learning},
-	\item CIFAR100~\cite{krizhevsky2009learning} and
-	\item SVHN~\cite{netzer2011reading}.
-\end{itemize}
+This section provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
+We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep}, CIFAR10~\cite{krizhevsky2009learning}, CIFAR100~\cite{krizhevsky2009learning} and SVHN~\cite{netzer2011reading}.
+We use the default train, validation and test datasets and compare the use of ReLU, ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in the MobilenetV2 model.
 
-We use the default train, validation and test datasets and compare the use of ReLU\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in a VGG11 model.
-The images from the MNIST variants are resized to $32\times 32$ to comply with the dimensions of VGG11.
+Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$, the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
+Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss}, Fig.\ref{fig:kernels} and Fig\ref{fig:featuremaps}.
+We also use the \textit{pandas.DataFrame.to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):
 
-Making use of the \textit{datatool} package the values of the following variables are not referred in the main \textit{.tex} file but they are read by an intermediate \textit{.tex} file created by the \textit{results code}:
-\begin{itemize}
-	\item the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$,
-	\item the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and
-	\item the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
-\end{itemize}
+\begin{figure}[!t]
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/MNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-loss.pdf}}
+	\caption{Comparison of MobilenetV2 with ReLU, ReLU6 and SiLU train and validation losses for MNIST and FashionMNIST.}
+	\label{fig:loss}
+\end{figure}
 
-Making use of setting the random seeds we consistenly get the same figures as shown in Fig.\ref{fig:image} which depicts the train and validation loss for all datasets.
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/MNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.25\textwidth]{tmp/FashionMNIST-loss.pdf}}
-	\caption{Train and validation losses for MNIST and FashionMNIST.}
-	\label{fig:image}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR10-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR100-ReLU-kernels.pdf}}
+	\caption{The first 16 kernels of the first convolutional layer of MobilenetV2 with ReLU for CIFAR10 and CIFAR100.}
+	\label{fig:kernels}
+\end{figure}
+
+\begin{figure}[!t]
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR10-ReLU-feature-maps.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR100-ReLU-feature-maps.pdf}}
+	\caption{The first 9 feature maps of the first channel of the first convolutional layer of MobilenetV2 with ReLU for images from CIFAR10 and CIFAR100.}
+	\label{fig:featuremaps}
 \end{figure}
@@
 	\centering
-	\caption{Table example created from results code.}
+	\caption{MobilenetV2 test dataset accuracies.}
 	\label{table:table}
@@
 \section{Discussion}
-The proposed template is based on plain text files and can be used with any POSIX-oriented operating that supports Docker and Make.
-Moreover it can be combined with any version control system, docker container registry providor and text editor thus preventing `app/vendor lock-in' situations.
+The proposed template is based on plain text files and can be used with any POSIX-oriented operating system that supports Docker and Make.
+POSIX and Make have existed for decades and have passed the test of time, while for Docker there are open standards such as the Open Container Initiative\footnote{\url{https://opencontainers.org/}} that could fill in a potential development discontinuation.
+Moreover this template can be combined with any version control system, docker container registry provider and text editor thus preventing `app/vendor lock-in' situations.
+
+Use cases of the template include:
+\begin{itemize}
+	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter \textit{results},
+	\item common development environment across multiple \textit{authors},
+	\item coauthor(s), reviewers, journal editors or other researchers can easily reproduce the \textit{document} with few requirements.
+\end{itemize}
 
@@
 Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
-The proposed template aids to this purpose in writing reproducible technical documents using the tools that most of academics already use (\LaTeX, Docker, Make).
+The proposed template aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.
 

### 2020-12-10 main.py

@@ -13,13 +13,14 @@ from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
 from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN
 from torchvision.models import mobilenet_v2
+from torchvision.utils import save_image
 
-plt.rcParams['font.size'] = 12
+plt.rcParams['font.size'] = 18
 plt.rcParams['savefig.format'] = 'pdf'
 
 dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
-activation_function_list = ['ReLU', 'SiLU']
+activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
 
 mean_std_list = [
         ((0.1307,), (0.3081,)),
@@ -66,9 +67,9 @@ def save_loss(train_loss, validation_loss, dataset_name, activation_function_lis
     plt.grid(True)
     plt.autoscale(enable=True, axis='x', tight=True)
     plt.ylim([0, 1])
-    plt.xlabel('Epochs', fontsize=15)
-    if dataset_name in ['MNIST', 'KMNIST', 'CIFAR100']:
-        plt.ylabel('loss', fontsize=15)
+    plt.xlabel('Epochs', fontsize=18)
+    if dataset_name == 'MNIST':
+        plt.ylabel('loss', fontsize=18)
     for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
         plt.plot(train_loss_, label=f'Train {activation_function}', color=color)
         plt.plot(validation_loss_, label=f'Validation {activation_function}', linestyle='--', color=color)
@@ -86,6 +87,12 @@ def change_module(model, module_old, module_new):
             setattr(model, child_name, module_new())
         else:
             change_module(child, module_old, module_new)
+
+activations = {}
+def get_activations(name):
+    def hook(model, input, output):
+        activations[name] = output.detach()
+    return hook
 
 
 if __name__ == '__main__':
@@ -120,14 +127,12 @@ if __name__ == '__main__':
     for index_dataset, (dataset, dataset_name, train_range, validation_range, test_range, mean_std) in enumerate(zip(dataset_list, dataset_name_list, train_range_list, validation_range_list, test_range_list, mean_std_list)):
[…]

### 2020-12-11 ms.tex
change title

@@
 
-\title{\LaTeX\ Technical Documents with Docker and Make}
+\title{A Makefile for Developing Containerized \LaTeX\ Technical Documents}
 
@@
 \begin{abstract}
-	We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems.
-	The template provides a Makefile for executing the code that generates variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce either the draft (fast) or full (slow) version of the document.
-	We also present various utilities that aid in automating the results generation and increasing the reproducibility of the document.
-	We release an open source repository of the template and use it to write this paper.
+	We propose a Makefile for developing containerized \LaTeX\ technical documents in POSIX-oriented operating systems.
+	The Makefile allows the author to execute the code that generates variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce either the draft (fast) or full (slow) version of the document.
+	We also present various utilities that aid in automating the results generation and improve the reproducibility of the document.
+	We release an open source repository of a template that uses the Makefile and demonstrate its use by developing this paper.
 \end{abstract}
@@
 \section{Introduction}
-Writing technical documents that present both computationally generated results (variables, tables and figures) and natural text, is one of the central aspects of computational research.
-One programming paradigm that has been proposed as a solution is \textit{literate programming}~\cite{knuth1984literate} in which the author inserts snippets of code and its execution output alongside natural text.
+Developing technical documents that present both computationally generated results (variables, tables and figures) and natural text, is a central aspect of computational research.
+One programming paradigm that was proposed as a solution is \textit{literate programming}~\cite{knuth1984literate}, in which the author inserts snippets of code and the output of its execution, alongside natural text.
 Some applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
 
-Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors thus leading to `app/vendor lock-in` situations.
-Moreover this overlap between natural text and results code makes \textit{literate programming} difficult to debug and version control.
+Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors and/or source code formats thus leading to `app/vendor lock-in` situations.
+Moreover, the overlap between natural text and results code makes \textit{literate programming} difficult to debug and version control.
 
-We propose a template for writing portable \LaTeX\ technical documents with Docker and Make in POSIX-oriented operating systems.
-We write this paper\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using this template\footnote{\url{https://github.com/pbizopoulos/latex-technical-documents-with-docker-and-make-template}} and choose the Python programming language~\cite{van2007python} for generating the results.
+We propose a Makefile for developing containerized \LaTeX\ technical documents in POSIX-oriented operating systems.
+By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
+We write this paper\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using a template consisting the Makefile\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents-template}} and choose Docker as the container technology and the Python programming language~\cite{van2007python} for generating the results.
 
@@
 	\item \textit{\LaTeX\ code} as the natural text (\textit{ms.tex}) and bibliography (\textit{ms.bib}),
-	\item \textit{code} as both the \textit{\LaTeX\ code} and \textit{results code},
-	\item \textit{document} as the technical document that contains the rendered natural text and \textit{results} and
-	\item \textit{author} as the author of the \textit{document} that writes and develops the \textit{code}.
+	\item \textit{code} as both the \textit{results code} and \textit{\LaTeX\ code},
+	\item \textit{document} as the technical document that contains the rendered \textit{results} and natural text and
+	\item \textit{author} as the author of the \textit{document} that develops the \textit{code}.
 \end{itemize}
 
-\section{Template}
+\section{The Makefile}
 
@@
 			\node[draw, right=1.5cm of code, fill=green!20] (results) {tmp/results};
-			\path[draw, ->] (code) -- node[above]{docker} (results);
+			\path[draw, ->] (code) -- (results);
 			\node[draw, right=4cm of document, fill=green!20] (pdf) {tmp/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
-			\path[draw, ->] (document) -- node[above]{docker} (pdf);
+			\path[draw, ->] (document) -- (pdf);
 	\end{tikzpicture}
-	\caption{The files of the template is depicted in the light gray background and the arrows denote the data flow towards generating the \textit{document}.
+	\caption{The files of a Docker container template that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
 	Green indicates temporary cache/generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}
@@
 
-\LaTeX~\cite{lamport1994latex} is a typesetting system for publishing high quality research documents, and Docker~\cite{merkel2014docker} is a container system that allows portable execution of a codebase between different operating systems/environments.
+The three tools that are used by the Makefile are the Make program\footnote{\url{https://www.gnu.org/software/make/}} which is a build automation tool, \LaTeX~\cite{lamport1994latex} which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems(OSs) and environments.
 
-The proposed template can be used for writing \LaTeX\ \textit{documents} that present \textit{results} generated from \textit{results code} executed within a Docker container with a consistent (across different hardware, OS and programming language), minimal user interface as follows:
+The pseudoalgorithm of the Makefile is as follows:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Pseudoalgorithm of the Makefile.}]
+tmp/$(document_pdf): $(latex_code) tmp/$(results)
+	run container latex
+
+tmp/$(results): $(results_code)
+	build image $(results_image)
+	run container $(results_image)
+
+clean:
+	rm -rf tmp/
+\end{lstlisting}
+
+The default target runs the container for the \LaTeX\ compilation while the \textit{results} target builds the image and runs the container that generates the \textit{results}.
+When the \textit{author} edits a file from \textit{results code} or \textit{\LaTeX\ code}, only the required compilation is automatically triggered with Make.
+Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time of a file.
+
+The proposed Makefile can be used for developing \LaTeX\ \textit{documents} that consist of \textit{results} generated from \textit{results code} executed within a container with a consistent (across different hardware, OS and programming language), minimal user interface as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Template make options.}]
 make             # Generate the draft (fast) version.
-make ARG=--full  # Generate the full (slow) version.
+make VER=--full  # Generate the full (slow) version.
 make clean       # Remove the tmp/ directory.
@@
 
-The \textit{author} may use the template for writing \textit{documents} in the following way:
+The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
 \begin{enumerate}
-	\item clones the template which consists of a set of files as depicted in Fig.\ref{fig:templatefiles},
+	\item clones/downloads the template repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:templatefiles},
 	\item specifies the name of the \textit{document} in the Makefile,
-	\item creates and develops the \textit{results code} which includes:
-		\begin{enumerate}
-			\item \textit{main.py},
-			\item \textit{Dockerfile},
-			\item generating the draft and full version \textit{document} in \textit{results code} and
-			\item saving \textit{results} in the \textit{tmp/} directory.
-		\end{enumerate}
-	\item creates and develops the \textit{\LaTeX\ code} which includes:
-		\begin{enumerate}
-			\item \textit{ms.tex} and \textit{ms.bib},
-			\item loading \textit{results} from the \textit{tmp/} directory.
-		\end{enumerate}
-	\item executes \textit{make} for generating the draft version \textit{document} used during development and experimentation,
-	\item executes \textit{make ARG=-{}-full} for generating the full version \textit{document} used for distribution or publication and
-	\item executes \textit{make clean} to restore to a clean state by removing the \textit{tmp/} directory.
+	\item creates and develops the \textit{results code}.
+	\item creates and develops the \textit{\LaTeX\ code}.
+	\item executes \textit{make} for fast development iterations and experimentation,
+	\item executes \textit{make VER=-{}-full} for distribution or publication and
+	\item executes \textit{make clean} to restore to a clean state.
 \end{enumerate}
 
-The only restriction that the template imposes on the \textit{results code} is that the default execution should generate the draft version \textit{document} and the presence of an optional argument (-{}-full) for generating the full version.
-The draft version \textit{document} (generated when calling \textit{make}) helps in faster iterations during writing and experimentation.
+The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
 An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
 
-The template makes use of the automatic generation of intermediate target files of the Make program.
-When the \textit{author} edits a file from \textit{results code} or \textit{\LaTeX\ code}, only the required compilation is automatically triggered with Make.
-Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time of a file.
-
-\section{Template utilities}
-In this section we present useful utilities that can be combined with the template to automate \textit{results} generation and improve the reproducibility of the \textit{document}.
+\section{The Makefile utilities}
+In this section we present useful utilities that can be combined with the Makefile to automate \textit{results} generation and improve the reproducibility of the \textit{document}.
 
@@
 Regarding \LaTeX\, a culprit against reproducibility is the time-date metadata embedded in the pdf output.
-These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done by default in the template Makefile):
+These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done by default in the Makefile):
 \begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}]
@@
 
-Regarding the \textit{results code} for Python, random seeds need to be set to a specific value such as:
-\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}]
+Regarding the \textit{results code} for Python, we can achieve deterministic stochasticity by setting the random seeds to a specific value such as:
+\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for popular libraries.}]
 # for build-in random module
@@
 
-Setting the random seeds and the previously mentioned \LaTeX\ packages, we could have deterministic stochasticity that generates the \textit{results}.
-
 Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, OS or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility.
-This can also be used as a test script for pushed commits and pull requests to a remote repository.}]
+\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
 # Generate the first draft document version
@@
 
-\section{Example use case of the template}
-This section provides a use case of the template and also serves as a manual for writing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
-We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep}, CIFAR10~\cite{krizhevsky2009learning}, CIFAR100~\cite{krizhevsky2009learning} and SVHN~\cite{netzer2011reading}.
+\section{Example use case of the Makefile}
+This section provides a use case of the Makefile and also serves as a manual for developing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
+We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep}, CIFAR10~\cite{krizhevsky2009learning} and CIFAR100~\cite{krizhevsky2009learning}.
 We use the default train, validation and test datasets and compare the use of ReLU, ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in the MobilenetV2 model.
@@
 Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$, the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
-Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss}, Fig.\ref{fig:kernels} and Fig\ref{fig:featuremaps}.
+Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.
 We also use the \textit{pandas.DataFrame.to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):
@@
 
-\begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR10-ReLU-feature-maps.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR100-ReLU-feature-maps.pdf}}
-	\caption{The first 9 feature maps of the first channel of the first convolutional layer of MobilenetV2 with ReLU for images from CIFAR10 and CIFAR100.}
-	\label{fig:featuremaps}
-\end{figure}
-
 \begin{table}[h]
@@
 	\label{table:table}
-	\setlength\tabcolsep{2pt}
+	\setlength\tabcolsep{4pt}
 	\input{tmp/metrics.tex}
@@
 \section{Discussion}
-The proposed template is based on plain text files and can be used with any POSIX-oriented operating system that supports Docker and Make.
-POSIX and Make have existed for decades and have passed the test of time, while for Docker there are open standards such as the Open Container Initiative\footnote{\url{https://opencontainers.org/}} that could fill in a potential development discontinuation.
-Moreover this template can be combined with any version control system, docker container registry provider and text editor thus preventing `app/vendor lock-in' situations.
+The proposed Makefile is based on plain text file editing and can be used with any POSIX-oriented operating system that supports containers and Make.
+POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives that could be used as drop-in replacements for Docker.
+Moreover this Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.
 
-Use cases of the template include:
+Use cases of the Makefile include:
 \begin{itemize}
@@
 Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
-The proposed template aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.
+The proposed Makefile aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.
 

### 2020-12-11 main.py

@@ -11,14 +11,14 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100
 from torchvision.models import mobilenet_v2
 from torchvision.utils import save_image
 
 plt.rcParams['font.size'] = 18
 plt.rcParams['savefig.format'] = 'pdf'
 
-dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100, SVHN]
+dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
 activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
 
@@ -28,8 +28,6 @@ mean_std_list = [
         ((0.1307,), (0.3081,)),
         ((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
         ((0.5071, 0.4865, 0.4409), (0.2673, 0.2564, 0.2762)),
-        ((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)),
-        ((0.5, 0.5, 0.5), (0.5, 0.5, 0.5)),
         ]
 
 train_range_list = [
@@ -38,8 +36,6 @@ train_range_list = [
         range(50000),
         range(40000),
         range(40000),
-        range(4000),
-        range(50000),
         ]
 
 validation_range_list = [
@@ -48,8 +44,6 @@ validation_range_list = [
         range(50000, 60000),
         range(40000, 50000),
         range(40000, 50000),
-        range(4000, 5000),
-        range(50000, 60000),
         ]
 
 test_range_list = [
@@ -57,8 +51,6 @@ test_range_list = [
         range(10000),
         range(10000),
         range(10000),
-        range(10000),
-        range(8000),
         range(10000),
         ]
 
@@ -87,12 +79,6 @@ def change_module(model, module_old, module_new):
             setattr(model, child_name, module_new())
         else:
             change_module(child, module_old, module_new)
-
-activations = {}
-def get_activations(name):
-    def hook(model, input, output):
-        activations[name] = output.detach()
[…]

### 2020-12-13 ms.tex
improve ms.tex

@@
 One programming paradigm that was proposed as a solution is \textit{literate programming}~\cite{knuth1984literate}, in which the author inserts snippets of code and the output of its execution, alongside natural text.
-Some applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
+Applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
 
@@
 By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
-We write this paper\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using a template consisting the Makefile\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents-template}} and choose Docker as the container technology and the Python programming language~\cite{van2007python} for generating the results.
+We write this paper\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using a template that consists of the Makefile\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents-template}} and choose Docker as the container technology and the Python programming language~\cite{van2007python} for generating the results.
 
@@
 			child{node[draw, anchor=west, fill=blue!20](py){main.py}}
-			child{node[draw, anchor=west, fill=blue!20](dockerfile){Dockerfile}}
+			child{node[draw, anchor=west, fill=blue!20](containerfile){Containerfile}}
 			child{node[draw, anchor=west, fill=blue!20](requirements){requirements.txt}};
@@
 	\end{tikzpicture}
-	\caption{The files of a Docker container template that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
-	Green indicates temporary cache/generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}
+	\caption{The files of a template that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
+	Green indicates temporary cache or generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}
 	\label{fig:templatefiles}
@@
 
-The three tools that are used by the Makefile are the Make program\footnote{\url{https://www.gnu.org/software/make/}} which is a build automation tool, \LaTeX~\cite{lamport1994latex} which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems(OSs) and environments.
+The proposed Makefile can be used for developing \textit{documents} that consist of \textit{results} generated from \textit{results code} executed within a container.
+The three tools that are used by the Makefile are the Make program\footnote{\url{https://www.gnu.org/software/make/}} which is a build automation tool, \LaTeX~\cite{lamport1994latex} which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems and environments.
 
@@
 	build image $(results_image)
-	run container $(results_image)
+	run container $(results_image) $(VER)
 
@@
 
-The proposed Makefile can be used for developing \LaTeX\ \textit{documents} that consist of \textit{results} generated from \textit{results code} executed within a container with a consistent (across different hardware, OS and programming language), minimal user interface as follows:
+The Makefile consists of the following minimal user interface:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Template make options.}]
@@
 \begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for popular libraries.}]
-# for build-in random module
+# build-in random module
 random.seed(0)
-# for numpy
+# numpy
 np.random.seed(0)
-# for tensorflow
+# tensorflow
 tf.random.set_seed(0)
-# for pytorch
+# pytorch
 torch.backends.cudnn.benchmark = False
@@
 
-Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, OS or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
+Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
-# Generate the first draft document version
+# Generate the first draft document version.
 make
-# Backup the first resulting pdf
+# Backup the first resulting pdf.
 cp tmp/ms.pdf tmp/ms-previous.pdf
-# Update the modification timestamp of main.py
+# Update the modification timestamp of main.py.
 touch main.py
-# Generate the second draft document version
+# Generate the second draft document version.
 make
-# Compare draft document versions byte by byte
+# Compare draft document versions byte by byte.
 cmp tmp/ms.pdf tmp/ms-previous.pdf
 # Compare draft document versions
-# in a human readable form
+# in a human readable form.
 diffoscope tmp/ms.pdf tmp/ms-previous.pdf
@@
 	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-loss.pdf}}
-	\caption{Comparison of MobilenetV2 with ReLU, ReLU6 and SiLU train and validation losses for MNIST and FashionMNIST.}
+	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for MNIST and FashionMNIST.}
 	\label{fig:loss}
@@
 	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR100-ReLU-kernels.pdf}}
-	\caption{The first 16 kernels of the first convolutional layer of MobilenetV2 with ReLU for CIFAR10 and CIFAR100.}
+	\caption{The first 16 kernels of the first convolutional layer of MobilenetV2 with ReLU for CIFAR10 (left) and CIFAR100 (right).}
 	\label{fig:kernels}
@@
 The proposed Makefile is based on plain text file editing and can be used with any POSIX-oriented operating system that supports containers and Make.
-POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives that could be used as drop-in replacements for Docker.
-Moreover this Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.
+POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives\footnote{\url{https://podman.io/}} that could be used as drop-in replacements for Docker.
+Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.
 

### 2020-12-13 ms.tex
remove numbering from conclusions

@@
 
-\section{Conclusion}
+\section*{Conclusion}
 Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.

### 2020-12-23 ms.tex
fix ms.tex

@@
 
-The Makefile consists of the following minimal user interface:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Template make options.}]
+The Makefile can be called with the following options:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
 make             # Generate the draft (fast) version.
@@
 
-The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
+The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
 An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
@@
 
-Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
+Additionally, an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]

### 2020-12-24 ms.tex
reduce to 12 citations and remove footnotes

@@
 By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
-We write this paper\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents}}\footnote{\url{https://arxiv.org/abs/2005.12660}} using a template that consists of the Makefile\footnote{\url{https://github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents-template}} and choose Docker as the container technology and the Python programming language~\cite{van2007python} for generating the results.
+We write this paper using a template that consists of the Makefile and choose Docker as the container technology and the Python programming language for generating the results.
 
@@
 The proposed Makefile can be used for developing \textit{documents} that consist of \textit{results} generated from \textit{results code} executed within a container.
-The three tools that are used by the Makefile are the Make program\footnote{\url{https://www.gnu.org/software/make/}} which is a build automation tool, \LaTeX~\cite{lamport1994latex} which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems and environments.
+The three tools that are used by the Makefile are the Make program which is a build automation tool, \LaTeX\ which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems and environments.
 
@@
 
-Additionally, an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
+Additionally, an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope for identifying sources of non-determinism as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
@@
 This section provides a use case of the Makefile and also serves as a manual for developing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
-We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep}, CIFAR10~\cite{krizhevsky2009learning} and CIFAR100~\cite{krizhevsky2009learning}.
+We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
 We use the default train, validation and test datasets and compare the use of ReLU, ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in the MobilenetV2 model.
@@
 	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-loss.pdf}}
-	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for MNIST and FashionMNIST.}
+	\\
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/KMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-loss.pdf}}
+	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}
 	\label{fig:loss}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR10-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/CIFAR100-ReLU-kernels.pdf}}
-	\caption{The first 16 kernels of the first convolutional layer of MobilenetV2 with ReLU for CIFAR10 (left) and CIFAR100 (right).}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/MNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-ReLU-kernels.pdf}}
+	\\
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/KMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-ReLU-kernels.pdf}}
+	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}
 	\label{fig:kernels}
@@
 The proposed Makefile is based on plain text file editing and can be used with any POSIX-oriented operating system that supports containers and Make.
-POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives\footnote{\url{https://podman.io/}} that could be used as drop-in replacements for Docker.
+POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
 Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.

### 2020-12-24 main.py

@@ -11,14 +11,14 @@ from torch.nn import functional as F
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
 from torchvision import transforms
-from torchvision.datasets import MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100
+from torchvision.datasets import MNIST, FashionMNIST, KMNIST, QMNIST
 from torchvision.models import mobilenet_v2
 from torchvision.utils import save_image
 
 plt.rcParams['font.size'] = 18
 plt.rcParams['savefig.format'] = 'pdf'
 
-dataset_list = [MNIST, FashionMNIST, KMNIST, CIFAR10, CIFAR100]
+dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
 dataset_name_list = [dataset.__name__ for dataset in dataset_list]
 activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
 
@@ -26,28 +26,24 @@ mean_std_list = [
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
         ((0.1307,), (0.3081,)),
-        ((0.4914, 0.4822, 0.4465), (0.2023, 0.1994, 0.2010)),
-        ((0.5071, 0.4865, 0.4409), (0.2673, 0.2564, 0.2762)),
+        ((0.1307,), (0.3081,)),
         ]
 
 train_range_list = [
         range(50000), 
         range(50000),
         range(50000),
-        range(40000),
-        range(40000),
+        range(50000),
         ]
 
 validation_range_list = [
         range(50000, 60000),
         range(50000, 60000),
         range(50000, 60000),
-        range(40000, 50000),
-        range(40000, 50000),
+        range(50000, 60000),
         ]
 
 test_range_list = [
-        range(10000),
         range(10000),
         range(10000),
         range(10000),
@@ -111,17 +107,11 @@ if __name__ == '__main__':
     num_parameters = np.zeros((len(activation_function_list)))
     criterion = nn.CrossEntropyLoss()
     for index_dataset, (dataset, dataset_name, train_range, validation_range, test_range, mean_std) in enumerate(zip(dataset_list, dataset_name_list, train_range_list, validation_range_list, test_range_list, mean_std_list)):
-        if dataset_name in ['MNIST', 'FashionMNIST', 'KMNIST']:
-            transform = transforms.Compose([
[…]

### 2021-01-04 ms.tex
remove unused package in ms.tex
fix

@@
 \usetikzlibrary{backgrounds}
-\usepackage[hyphens]{url}
 \usepackage{hyperref}
@@
 	\item clones/downloads the template repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:templatefiles},
-	\item specifies the name of the \textit{document} in the Makefile,
 	\item creates and develops the \textit{results code}.
@@
 \section*{Conclusion}
-Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
 The proposed Makefile aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.

### 2021-02-17 main.py
increase overall clarity

@@ -78,11 +78,17 @@ def change_module(model, module_old, module_new):
 
 
 if __name__ == '__main__':
-    # DO NOT EDIT BLOCK - Required by the Makefile
+    # Set appropriate variables (e.g. num_samples) to a lower value to reduce the computational cost of the draft (fast) version document.
     parser = argparse.ArgumentParser()
     parser.add_argument('--full', default=False, action='store_true')
     args = parser.parse_args()
-    # END OF DO NOT EDIT BLOCK
+    if args.full:
+        num_epochs = 20
+    else:
+        num_epochs = 2
+        train_range_list = [train_range[:10] for train_range in train_range_list]
+        validation_range_list = [validation_range[:10] for validation_range in validation_range_list]
+        test_range_list = [test_range[:10] for test_range in test_range_list]
 
     # Set random seeds for reproducibility.
     np.random.seed(0)
@@ -91,13 +97,6 @@ if __name__ == '__main__':
     torch.manual_seed(0)
 
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-    if args.full:
-        num_epochs = 20
-    else:
-        num_epochs = 2
-        train_range_list = [train_range[:10] for train_range in train_range_list]
-        validation_range_list = [validation_range[:10] for validation_range in validation_range_list]
-        test_range_list = [test_range[:10] for test_range in test_range_list]
     lr = 0.01
     batch_size = 64
     train_loss_array = np.zeros((len(dataset_list), len(activation_function_list), num_epochs))

### 2021-02-17 ms.tex
fix
adjust paper to changes

--- 2020-12-24 ms.tex
@@
 	build image $(results_image)
-	run container $(results_image) $(VER)
+	run container $(results_image) $(VERSION)
 
@@
 make                # Generate the draft (fast) version.
-make VER=--full  # Generate the full (slow) version.
+make VERSION=--full # Generate the full (slow) version.
 make clean          # Remove the tmp/ directory.
@@
 	\item executes \textit{make} for fast development iterations and experimentation,
-	\item executes \textit{make VER=-{}-full} for distribution or publication and
+	\item executes \textit{make VERSION=-{}-full} for distribution or publication and
 	\item executes \textit{make clean} to restore to a clean state.

### 2021-02-19 ms.tex
fix README.md

@@
 \begin{abstract}
-	We propose a Makefile for developing containerized \LaTeX\ technical documents in POSIX-oriented operating systems.
+	We propose a Makefile for developing containerized \LaTeX\ technical documents.
 	The Makefile allows the author to execute the code that generates variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce either the draft (fast) or full (slow) version of the document.
@@
 
-We propose a Makefile for developing containerized \LaTeX\ technical documents in POSIX-oriented operating systems.
+We propose a Makefile for developing containerized \LaTeX\ technical documents.
 By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
@@
 When the \textit{author} edits a file from \textit{results code} or \textit{\LaTeX\ code}, only the required compilation is automatically triggered with Make.
-Forced compilations without change could be done using the \textit{touch} POSIX utility that updates the modification time of a file.
+Forced compilations without change could be done using the \textit{touch} utility that updates the modification time of a file.
 
@@
 
-Additionally, an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope for identifying sources of non-determinism as follows:
+Additionally, an \textit{author} can use the \textit{cmp} utility to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope for identifying sources of non-determinism as follows:
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
@@
 \section{Discussion}
-The proposed Makefile is based on plain text file editing and can be used with any POSIX-oriented operating system that supports containers and Make.
-POSIX and Make have existed for decades and have passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
+The proposed Makefile is based on plain text file editing and can be used with any operating system that supports containers and Make.
+Make has existed for decades and has passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
 Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.

### 2021-08-31 ms.tex
init

@@
 \begin{document}
-\DTLloaddb{keys_values}{tmp/keys-values.csv}
+\DTLloaddb{keys-values}{tmp/keys-values.csv}
 
@@
 	We also present various utilities that aid in automating the results generation and improve the reproducibility of the document.
-	We release an open source repository of a template that uses the Makefile and demonstrate its use by developing this paper.
+	We lastly release an open source repository of this paper that uses the Makefile.
 \end{abstract}
@@
 
-Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors and/or source code formats thus leading to `app/vendor lock-in` situations.
+Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors and/or source code formats thus leading to `app/vendor lock-in' situations.
 Moreover, the overlap between natural text and results code makes \textit{literate programming} difficult to debug and version control.
@@
 By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
-We write this paper using a template that consists of the Makefile and choose Docker as the container technology and the Python programming language for generating the results.
+We write this paper using a repository that consists of the Makefile and choose Docker as the container technology and the Python programming language for generating the results.
 
@@
 			child{node[draw, anchor=west](makefile){Makefile}}
-			child{node[draw, anchor=west, fill=green!20](tmp){tmp/}}
 			child{node[draw, anchor=west, fill=red!20](tex){ms.tex}}
@@
 	\end{tikzpicture}
-	\caption{The files of a template that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
-	Green indicates temporary cache or generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}
-	\label{fig:templatefiles}
+	\caption{The files of a repository that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
+	Green indicates temporary cache or generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}\label{fig:repositoryfiles}
 \end{figure}
@@
 \begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
-make                # Generate the draft (fast) version.
-make VERSION=--full # Generate the full (slow) version.
-make clean          # Remove the tmp/ directory.
+make                # Generate draft (fast) version.\ 
+make VERSION=--full # Generate full (slow) version.\ 
+make clean          # Remove tmp/ directory.
 \end{lstlisting}
@@
 \begin{enumerate}
-	\item clones/downloads the template repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:templatefiles},
+	\item clones/downloads the repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:repositoryfiles},
 	\item creates and develops the \textit{results code}.
@@
 A useful \LaTeX\ package for automatically presenting variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (tmp/keys\_values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
-\DTLloaddb{keys_values}{tmp/keys_values.csv}
-\DTLfetch{keys_values}{key}{lr}{value}
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (tmp/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
+\DTLloaddb{keys-values}{tmp/keys-values.csv}
+\DTLfetch{keys-values}{key}{lr}{value}
 \end{lstlisting}
@@
 \begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
-# Generate the first draft document version.
+# Generate the first draft document version.\ 
 make
-# Backup the first resulting pdf.
+# Backup the first resulting pdf.\ 
 cp tmp/ms.pdf tmp/ms-previous.pdf
-# Update the modification timestamp of main.py.
+# Update the modification timestamp of main.py.\ 
 touch main.py
-# Generate the second draft document version.
+# Generate the second draft document version.\ 
 make
-# Compare draft document versions byte by byte.
+# Compare draft document versions byte by byte.\ 
 cmp tmp/ms.pdf tmp/ms-previous.pdf
 # Compare draft document versions
-# in a human readable form.
+# in a human readable form.\ 
 diffoscope tmp/ms.pdf tmp/ms-previous.pdf
@@
 
-Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys_values}{key}{num_epochs}{value}$, the batch size is $\DTLfetch{keys_values}{key}{batch_size}{value}$ and the learning rate for SGD is $\DTLfetch{keys_values}{key}{lr}{value}$.
+Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys-values}{key}{num-epochs}{value}$, the batch size is $\DTLfetch{keys-values}{key}{batch-size}{value}$ and the learning rate for SGD is $\DTLfetch{keys-values}{key}{lr}{value}$.
 Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.
@@
 	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-loss.pdf}}
-	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}
-	\label{fig:loss}
+	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
 \end{figure}
@@
 	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-ReLU-kernels.pdf}}
-	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}
-	\label{fig:kernels}
+	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
 \end{figure}
 
-\begin{table}[h]
+\begin{table}[ht]
 	\centering
-	\caption{MobilenetV2 test dataset accuracies.}
-	\label{table:table}
+	\caption{MobilenetV2 test dataset accuracies.}\label{table:table}
 	\setlength\tabcolsep{4pt}
@@
 	\item common development environment across multiple \textit{authors},
-	\item coauthor(s), reviewers, journal editors or other researchers can easily reproduce the \textit{document} with few requirements.
+	\item coauthors, reviewers, journal editors or other researchers can easily reproduce the \textit{document} with few requirements.
 \end{itemize}

### 2021-08-31 main.py

@@ -1,0 +1,174 @@
+import argparse
+
+import numpy as np
+import pandas as pd
+import torch
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from torch import nn, optim
+from torch.utils.data import DataLoader
+from torch.utils.data.sampler import SubsetRandomSampler
+from torchvision import transforms
+from torchvision.datasets import KMNIST, MNIST, QMNIST, FashionMNIST
+from torchvision.models import mobilenet_v2
+from torchvision.utils import save_image
+
+plt.rcParams['font.size'] = 18
+plt.rcParams['savefig.format'] = 'pdf'
+
+
+def save_loss(train_loss, validation_loss, dataset_name, activation_function_list):
+    _, ax = plt.subplots()
+    plt.grid(True)
+    plt.autoscale(enable=True, axis='x', tight=True)
+    plt.ylim([0, 1])
+    plt.xlabel('Epochs', fontsize=18)
+    if dataset_name == 'MNIST':
+        plt.ylabel('loss', fontsize=18)
+    for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
+        plt.plot(train_loss_, label=f'Train {activation_function}', color=color)
+        plt.plot(validation_loss_, label=f'Validation {activation_function}', linestyle='--', color=color)
+    plt.title(dataset_name)
+    ax.tick_params(axis='both', which='major', labelsize='large')
+    ax.tick_params(axis='both', which='minor', labelsize='large')
+    ax.xaxis.set_major_locator(MaxNLocator(integer=True))
+    ax.legend()
+    plt.savefig(f'tmp/{dataset_name}-loss', bbox_inches='tight')
+    plt.close()
+
+
+def change_module(model, module_old, module_new):
+    for child_name, child in model.named_children():
+        if isinstance(child, module_old):
+            setattr(model, child_name, module_new())
+        else:
+            change_module(child, module_old, module_new)
+
+
+def main():
+    dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
+    dataset_name_list = [dataset.__name__ for dataset in dataset_list]
+    activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
+    mean_std_list = [((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,))]
[…]

### 2021-09-21 ms.tex
init

@@
 	build image $(results_image)
-	run container $(results_image) $(VERSION)
+	run container $(results_image)
 
@@
 make                # Generate draft (fast) version.\ 
-make VERSION=--full # Generate full (slow) version.\ 
+make FULL=1         # Generate full (slow) version.\ 
 make clean          # Remove tmp/ directory.
@@
 	\item executes \textit{make} for fast development iterations and experimentation,
-	\item executes \textit{make VERSION=-{}-full} for distribution or publication and
+	\item executes \textit{make FULL=1} for distribution or publication and
 	\item executes \textit{make clean} to restore to a clean state.

### 2021-09-21 main.py

@@ -1,0 +1,165 @@
+import os
+
+import numpy as np
+import pandas as pd
+import torch
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from torch import nn, optim
+from torch.utils.data import DataLoader
+from torch.utils.data.sampler import SubsetRandomSampler
+from torchvision import transforms
+from torchvision.datasets import KMNIST, MNIST, QMNIST, FashionMNIST
+from torchvision.models import mobilenet_v2
+from torchvision.utils import save_image
+
+tmpdir = os.getenv('TMPDIR')
+full = os.getenv('FULL')
+
+plt.rcParams['font.size'] = 18
+plt.rcParams['savefig.format'] = 'pdf'
+
+
+def save_loss(train_loss, validation_loss, dataset_name, activation_function_list):
+    _, ax = plt.subplots()
+    plt.grid(True)
+    plt.autoscale(enable=True, axis='x', tight=True)
+    plt.ylim([0, 1])
+    plt.xlabel('Epochs', fontsize=18)
+    if dataset_name == 'MNIST':
+        plt.ylabel('loss', fontsize=18)
+    for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
+        plt.plot(train_loss_, label=f'Train {activation_function}', color=color)
+        plt.plot(validation_loss_, label=f'Validation {activation_function}', linestyle='--', color=color)
+    plt.title(dataset_name)
+    ax.tick_params(axis='both', which='major', labelsize='large')
+    ax.tick_params(axis='both', which='minor', labelsize='large')
+    ax.xaxis.set_major_locator(MaxNLocator(integer=True))
+    ax.legend()
+    plt.savefig(f'{tmpdir}/{dataset_name}-loss', bbox_inches='tight')
+    plt.close()
+
+
+def change_module(model, module_old, module_new):
+    for child_name, child in model.named_children():
+        if isinstance(child, module_old):
+            setattr(model, child_name, module_new())
+        else:
+            change_module(child, module_old, module_new)
+
+
+def main():
+    dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
+    dataset_name_list = [dataset.__name__ for dataset in dataset_list]
+    activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
[…]

### 2022-03-21 ms.tex
Makefile major change

@@
 \begin{document}
-\DTLloaddb{keys-values}{tmp/keys-values.csv}
+\DTLloaddb{keys-values}{artifacts/keys-values.csv}
 
@@
 			\end{scope}
-			\node[draw, right=1.5cm of code, fill=green!20] (results) {tmp/results};
+			\node[draw, right=1.5cm of code, fill=green!20] (results) {artifacts/results};
 			\path[draw, ->] (code) -- (results);
-			\node[draw, right=4cm of document, fill=green!20] (pdf) {tmp/ms.pdf};
+			\node[draw, right=4cm of document, fill=green!20] (pdf) {artifacts/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
@@
 \begin{lstlisting}[language=bash, style=lststyle, caption={Pseudoalgorithm of the Makefile.}]
-tmp/$(document_pdf): $(latex_code) tmp/$(results)
+artifacts/$(document_pdf): $(latex_code) artifacts/$(results)
 	run container latex
 
-tmp/$(results): $(results_code)
+artifacts/$(results): $(results_code)
 	build image $(results_image)
@@
 clean:
-	rm -rf tmp/
+	rm -rf artifacts/
 \end{lstlisting}
@@
 
-The Makefile can be called with the following options:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
-make                # Generate draft (fast) version.\ 
-make FULL=1         # Generate full (slow) version.\ 
-make clean          # Remove tmp/ directory.
+The basic commands of the Makefile are the following:
+\begin{lstlisting}[language=bash, style=lststyle, caption={Basic Makefile commands.}]
+make                # Generate draft artifacts (fast).\ 
+make FULL=1         # Generate full artifacts (slow).\ 
+make clean          # Remove artifacts/ directory.
 \end{lstlisting}
@@
 
-The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
+The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{artifacts/} respectively.
 An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
@@
 A useful \LaTeX\ package for automatically presenting variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (tmp/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
-\DTLloaddb{keys-values}{tmp/keys-values.csv}
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (artifacts/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
+\DTLloaddb{keys-values}{artifacts/keys-values.csv}
 \DTLfetch{keys-values}{key}{lr}{value}
@@
 When using Python, a useful function for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table:
-\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (tmp/metrics.tex) in \textit{results code}.}]
+\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (artifacts/metrics.tex) in \textit{results code}.}]
 df = pd.DataFrame(table)
-df.to_latex("tmp/metrics.tex", float_format="%.2f")
+df.to_latex("artifacts/metrics.tex", float_format="%.2f")
 \end{lstlisting}
@@
 # Backup the first resulting pdf.\ 
-cp tmp/ms.pdf tmp/ms-previous.pdf
+cp artifacts/ms.pdf artifacts/ms-previous.pdf
 # Update the modification timestamp of main.py.\ 
@@
 # Compare draft document versions byte by byte.\ 
-cmp tmp/ms.pdf tmp/ms-previous.pdf
+cmp artifacts/ms.pdf artifacts/ms-previous.pdf
 # Compare draft document versions
 # in a human readable form.\ 
-diffoscope tmp/ms.pdf tmp/ms-previous.pdf
+diffoscope artifacts/ms.pdf artifacts/ms-previous.pdf
 \end{lstlisting}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/MNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-loss.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/KMNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-loss.pdf}}
 	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/MNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/FashionMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-ReLU-kernels.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/KMNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{tmp/QMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-ReLU-kernels.pdf}}
 	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
@@
 	\setlength\tabcolsep{4pt}
-	\input{tmp/metrics.tex}
+	\input{artifacts/metrics.tex}
 \end{table}

### 2022-03-21 main.py

@@ -1,4 +1,5 @@
 import os
+from os.path import join
 
 import numpy as np
 import pandas as pd
@@ -13,30 +14,10 @@ from torchvision.datasets import KMNIST, MNIST, QMNIST, FashionMNIST
 from torchvision.models import mobilenet_v2
 from torchvision.utils import save_image
 
-tmpdir = os.getenv('TMPDIR')
+artifacts_dir = os.getenv('ARTIFACTSDIR')
 full = os.getenv('FULL')
 plt.rcParams['font.size'] = 18
 plt.rcParams['savefig.format'] = 'pdf'
-
-
-def save_loss(train_loss, validation_loss, dataset_name, activation_function_list):
-    _, ax = plt.subplots()
-    plt.grid(True)
-    plt.autoscale(enable=True, axis='x', tight=True)
-    plt.ylim([0, 1])
-    plt.xlabel('Epochs', fontsize=18)
-    if dataset_name == 'MNIST':
-        plt.ylabel('loss', fontsize=18)
-    for train_loss_, validation_loss_, activation_function, color in zip(train_loss, validation_loss, activation_function_list, ['b', 'orange']):
-        plt.plot(train_loss_, label=f'Train {activation_function}', color=color)
-        plt.plot(validation_loss_, label=f'Validation {activation_function}', linestyle='--', color=color)
-    plt.title(dataset_name)
-    ax.tick_params(axis='both', which='major', labelsize='large')
-    ax.tick_params(axis='both', which='minor', labelsize='large')
-    ax.xaxis.set_major_locator(MaxNLocator(integer=True))
-    ax.legend()
-    plt.savefig(f'{tmpdir}/{dataset_name}-loss', bbox_inches='tight')
-    plt.close()
 
 
 def change_module(model, module_old, module_new):
@@ -76,8 +57,8 @@ def main():
     criterion = nn.CrossEntropyLoss()
     for index_dataset, (dataset, dataset_name, train_range, validation_range, test_range, mean_std) in enumerate(zip(dataset_list, dataset_name_list, train_range_list, validation_range_list, test_range_list, mean_std_list)):
         transform = transforms.Compose([transforms.ToTensor(), transforms.Lambda(lambda x: torch.cat([x, x, x], 0)), transforms.Normalize(mean_std[0], mean_std[1])])
-        train_dataset = dataset(tmpdir, train=True, transform=transform, download=True)
-        test_dataset = dataset(tmpdir, train=False, transform=transform, download=True)
[…]

### 2022-04-21 ms.tex
fix names

@@
 
-Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys-values}{key}{num-epochs}{value}$, the batch size is $\DTLfetch{keys-values}{key}{batch-size}{value}$ and the learning rate for SGD is $\DTLfetch{keys-values}{key}{lr}{value}$.
+Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys-values}{key}{epochs-num}{value}$, the batch size is $\DTLfetch{keys-values}{key}{batch-size}{value}$ and the learning rate for SGD is $\DTLfetch{keys-values}{key}{lr}{value}$.
 Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.

### 2022-04-21 main.py

@@ -9,9 +9,9 @@ from matplotlib.ticker import MaxNLocator
 from torch import nn, optim
 from torch.utils.data import DataLoader
 from torch.utils.data.sampler import SubsetRandomSampler
-from torchvision import transforms
 from torchvision.datasets import KMNIST, MNIST, QMNIST, FashionMNIST
 from torchvision.models import mobilenet_v2
+from torchvision.transforms import Compose, Lambda, Normalize, ToTensor
 from torchvision.utils import save_image
 
 
@@ -32,12 +32,12 @@ def main():
     dataset_name_list = [dataset.__name__ for dataset in dataset_list]
     activation_function_list = ['ReLU', 'ReLU6', 'SiLU']
     mean_std_list = [((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,))]
-    num_epochs = 20
+    epochs_num = 20
     training_range_list = [range(50000), range(50000), range(50000), range(50000)]
     validation_range_list = [range(50000, 60000), range(50000, 60000), range(50000, 60000), range(50000, 60000)]
     test_range_list = [range(10000), range(10000), range(10000), range(10000)]
     if not full:
-        num_epochs = 2
+        epochs_num = 2
         training_range_list = [training_range[:10] for training_range in training_range_list]
         validation_range_list = [validation_range[:10] for validation_range in validation_range_list]
         test_range_list = [test_range[:10] for test_range in test_range_list]
@@ -48,31 +48,29 @@ def main():
     device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
     lr = 0.01
     batch_size = 64
-    training_loss_array = np.zeros((len(dataset_list), len(activation_function_list), num_epochs))
-    validation_loss_array = np.zeros((len(dataset_list), len(activation_function_list), num_epochs))
+    training_loss_array = np.zeros((len(dataset_list), len(activation_function_list), epochs_num))
+    validation_loss_array = np.zeros((len(dataset_list), len(activation_function_list), epochs_num))
     test_accuracy_array = np.zeros((len(dataset_list), len(activation_function_list)))
     test_batch_size = 1000
-    num_parameters = np.zeros(len(activation_function_list))
     criterion = nn.CrossEntropyLoss()
[…]

### 2022-05-16 ms.tex
major changes

@@
 \usepackage[caption=false,font=footnotesize]{subfig}
+\usepackage[nopdftrailerid=true]{pdfprivacy}
 \usepackage{booktabs}
@@
 \begin{document}
-\DTLloaddb{keys-values}{artifacts/keys-values.csv}
+\DTLloaddb{keys-values}{python/artifacts/keys-values.csv}
 
@@
 			\end{scope}
-			\node[draw, right=1.5cm of code, fill=green!20] (results) {artifacts/results};
+			\node[draw, right=1.5cm of code, fill=green!20] (results) {python/artifacts/results};
 			\path[draw, ->] (code) -- (results);
-			\node[draw, right=4cm of document, fill=green!20] (pdf) {artifacts/ms.pdf};
+			\node[draw, right=4cm of document, fill=green!20] (pdf) {python/artifacts/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/MNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/FashionMNIST-loss.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/KMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/QMNIST-loss.pdf}}
 	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/MNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/FashionMNIST-ReLU-kernels.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/KMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/artifacts/QMNIST-ReLU-kernels.pdf}}
 	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
@@
 	\setlength\tabcolsep{4pt}
-	\input{artifacts/metrics.tex}
+	\input{python/artifacts/metrics.tex}
 \end{table}

### 2022-05-16 python/main.py

@@ -1,5 +1,6 @@
 from matplotlib import pyplot as plt
 from matplotlib.ticker import MaxNLocator
+from os import environ
 from os.path import join
 from torch import nn, optim
 from torch.utils.data import DataLoader
@@ -9,7 +10,6 @@ from torchvision.models import mobilenet_v2
 from torchvision.transforms import Compose, Lambda, Normalize, ToTensor
 from torchvision.utils import save_image
 import numpy as np
-import os
 import pandas as pd
 import torch
 
@@ -23,8 +23,8 @@ def change_module(model, module_old, module_new):
 
 
 def main():
-    artifacts_dir = os.getenv('ARTIFACTSDIR')
-    full = os.getenv('FULL')
+    artifacts_dir = environ['ARTIFACTSDIR']
+    full = environ['FULL']
     plt.rcParams['font.size'] = 18
     plt.rcParams['savefig.format'] = 'pdf'
     dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]

### 2022-05-17 python/main.py
apply source_normalizer

@@ -14,12 +14,12 @@ import pandas as pd
 import torch
 
 
-def change_module(model, module_old, module_new):
+def change_module(model, module_new, module_old):
     for (child_name, child) in model.named_children():
         if isinstance(child, module_old):
             setattr(model, child_name, module_new())
         else:
-            change_module(child, module_old, module_new)
+            change_module(child, module_new, module_old)
 
 
 def main():
@@ -62,9 +62,9 @@ def main():
         for (activation_function_index, activation_function) in enumerate(activation_function_list):
             model = mobilenet_v2().to(device)
             if activation_function == 'SiLU':
-                change_module(model, nn.ReLU6, nn.SiLU)
+                change_module(model, nn.SiLU, nn.ReLU6)
             elif activation_function == 'ReLU':
-                change_module(model, nn.ReLU6, nn.ReLU)
+                change_module(model, nn.ReLU, nn.ReLU6)
             optimizer = optim.SGD(model.parameters(), lr=lr)
             validation_loss_best = float('inf')
             model_file_name = f'{dataset.__name__}-{activation_function}'
@@ -104,9 +104,9 @@ def main():
                     torch.save(model.state_dict(), model_file_path)
             model = mobilenet_v2().to(device)
             if activation_function == 'SiLU':
-                change_module(model, nn.ReLU6, nn.SiLU)
+                change_module(model, nn.SiLU, nn.ReLU6)
             elif activation_function == 'ReLU':
-                change_module(model, nn.ReLU6, nn.ReLU)
+                change_module(model, nn.ReLU, nn.ReLU6)
             model.load_state_dict(torch.load(model_file_path))
             model.eval()
             kernels = model.features[0][0].weight.detach().clone()

### 2022-10-06 ms.tex
fix

--- 2022-04-21 ms.tex
@@
 \begin{document}
-\DTLloaddb{keys-values}{artifacts/keys-values.csv}
+\DTLloaddb{keys-values}{python/bin/keys-values.csv}
 
@@
 			\end{scope}
-			\node[draw, right=1.5cm of code, fill=green!20] (results) {artifacts/results};
+			\node[draw, right=1.5cm of code, fill=green!20] (results) {python/bin/results};
 			\path[draw, ->] (code) -- (results);
-			\node[draw, right=4cm of document, fill=green!20] (pdf) {artifacts/ms.pdf};
+			\node[draw, right=4cm of document, fill=green!20] (pdf) {python/bin/ms.pdf};
 			\path[draw, ->] (results) |- (pdf);
@@
 \begin{lstlisting}[language=bash, style=lststyle, caption={Pseudoalgorithm of the Makefile.}]
-artifacts/$(document_pdf): $(latex_code) artifacts/$(results)
+bin/$(document_pdf): $(latex_code) bin/$(results)
 	run container latex
 
-artifacts/$(results): $(results_code)
+bin/$(results): $(results_code)
 	build image $(results_image)
@@
 clean:
-	rm -rf artifacts/
+	rm -rf bin/
 \end{lstlisting}
@@
 \begin{lstlisting}[language=bash, style=lststyle, caption={Basic Makefile commands.}]
-make                # Generate draft artifacts (fast).\ 
-make FULL=1         # Generate full artifacts (slow).\ 
-make clean          # Remove artifacts/ directory.
+make                # Generate draft bin (fast).\ 
+make FULL=1         # Generate full bin (slow).\ 
+make clean          # Remove bin/ directory.
 \end{lstlisting}
@@
 
-The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{artifacts/} respectively.
+The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{bin/} respectively.
 An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
@@
 A useful \LaTeX\ package for automatically presenting variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (artifacts/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
-\DTLloaddb{keys-values}{artifacts/keys-values.csv}
+\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (bin/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
+\DTLloaddb{keys-values}{bin/keys-values.csv}
 \DTLfetch{keys-values}{key}{lr}{value}
@@
 When using Python, a useful function for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table:
-\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (artifacts/metrics.tex) in \textit{results code}.}]
+\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (bin/metrics.tex) in \textit{results code}.}]
 df = pd.DataFrame(table)
-df.to_latex("artifacts/metrics.tex", float_format="%.2f")
+df.to_latex("bin/metrics.tex", float_format="%.2f")
 \end{lstlisting}
@@
 # Backup the first resulting pdf.\ 
-cp artifacts/ms.pdf artifacts/ms-previous.pdf
+cp bin/ms.pdf bin/ms-previous.pdf
 # Update the modification timestamp of main.py.\ 
@@
 # Compare draft document versions byte by byte.\ 
-cmp artifacts/ms.pdf artifacts/ms-previous.pdf
+cmp bin/ms.pdf bin/ms-previous.pdf
 # Compare draft document versions
 # in a human readable form.\ 
-diffoscope artifacts/ms.pdf artifacts/ms-previous.pdf
+diffoscope bin/ms.pdf bin/ms-previous.pdf
 \end{lstlisting}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-loss.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-loss.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-loss.pdf}}
 	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
@@
 \begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/MNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/FashionMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-ReLU-kernels.pdf}}
 	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/KMNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{artifacts/QMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-ReLU-kernels.pdf}}
+	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-ReLU-kernels.pdf}}
 	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
@@
 	\setlength\tabcolsep{4pt}
-	\input{artifacts/metrics.tex}
+	\input{python/bin/metrics.tex}
 \end{table}

### 2022-10-06 makefile-tests.sh

@@ -3,23 +3,21 @@ set -o errexit
 
 # Requirements: ash, bash, dash, ksh, posh, yash, zsh, bmake and make
 
-artifacts_dir=artifacts/artifacts-test
 make_array=( bmake make )
 shell_array=( ash bash dash ksh posh yash zsh )
 for make_element in "${make_array[@]}"
 do
 	for shell_element in "${shell_array[@]}"
 	do
-		mkdir -p ${artifacts_dir}/python/
-		cp python/Makefile ${artifacts_dir}/python/Makefile
-		"$make_element" -C ${artifacts_dir}/python/ SHELL="$shell_element" || rm -rf ${artifacts_dir}
-		"$make_element" -C ${artifacts_dir}/python/ SHELL="$shell_element" clean || rm -rf ${artifacts_dir}
-		cp Makefile ${artifacts_dir}/Makefile
-		"$make_element" -C ${artifacts_dir}/ SHELL="$shell_element" || rm -rf ${artifacts_dir}
-		"$make_element" -C ${artifacts_dir}/ SHELL="$shell_element" artifacts/tex.tar || rm -rf ${artifacts_dir}
-		"$make_element" -C ${artifacts_dir}/ SHELL="$shell_element" artifacts/tex-lint || rm -rf ${artifacts_dir}
-		"$make_element" -C ${artifacts_dir}/ SHELL="$shell_element" artifacts/ms-server.pdf SERVER_URL=https://arxiv.org/e-print/2005.12660 || rm -rf ${artifacts_dir}
-		"$make_element" -C ${artifacts_dir}/ SHELL="$shell_element" clean || rm -rf ${artifacts_dir}
-		rm -rf ${artifacts_dir}/
+		mkdir -p bin/bin-test/python/
+		cp python/Makefile bin/bin-test/python/Makefile
+		"$make_element" -C bin/bin-test/python/ SHELL="$shell_element" all || rm -rf bin/bin-test
+		"$make_element" -C bin/bin-test/python/ SHELL="$shell_element" check || rm -rf bin/bin-test
+		"$make_element" -C bin/bin-test/python/ SHELL="$shell_element" clean || rm -rf bin/bin-test
+		cp Makefile bin/bin-test/Makefile
+		"$make_element" -C bin/bin-test/ SHELL="$shell_element" all || rm -rf bin/bin-test
[…]

### 2022-10-06 python/main.py

@@ -23,7 +23,6 @@ def change_module(model, module_new, module_old):
 
 
 def main():
-    artifacts_dir = environ['ARTIFACTS_DIR']
     full = environ['FULL']
     plt.rcParams['font.size'] = 18
     plt.rcParams['savefig.format'] = 'pdf'
@@ -54,8 +53,8 @@ def main():
     cross_entropy_loss = nn.CrossEntropyLoss()
     for (dataset_index, (dataset, dataset_name, range_training, range_validation, test_range, std_mean)) in enumerate(zip(dataset_list, dataset_name_list, range_training_list, range_validation_list, test_range_list, std_mean_list)):
         transform = Compose([ToTensor(), Lambda(lambda tensor: torch.cat([tensor, tensor, tensor], 0)), Normalize(std_mean[0], std_mean[1])])
-        dataset_training = dataset(artifacts_dir, transform=transform, download=True)
-        dataset_test = dataset(artifacts_dir, train=False, transform=transform, download=True)
+        dataset_training = dataset('bin', transform=transform, download=True)
+        dataset_test = dataset('bin', train=False, transform=transform, download=True)
         dataloader_training = DataLoader(dataset_training, batch_size=batch_size, sampler=SubsetRandomSampler(range_training))
         dataloader_validation = DataLoader(dataset_training, batch_size=batch_size, sampler=SubsetRandomSampler(range_validation))
         dataloader_test = DataLoader(dataset_test, batch_size=batch_size_test, sampler=SubsetRandomSampler(test_range))
@@ -68,7 +67,7 @@ def main():
             optimizer = optim.SGD(model.parameters(), lr=lr)
             loss_validation_best = float('inf')
             model_file_name = f'{dataset.__name__}-{activation_function_name}'
-            model_file_path = join(artifacts_dir, f'{model_file_name}.pt')
+            model_file_path = join('bin', f'{model_file_name}.pt')
             for epoch in range(epochs_num):
                 loss_training_sum = 0
                 predictions_num = 0
@@ -107,7 +106,7 @@ def main():
                 change_module(model, nn.ReLU, nn.ReLU6)
             model.load_state_dict(torch.load(model_file_path))
             kernels = model.features[0][0].weight.detach().clone()
-            save_image(kernels[:25], join(artifacts_dir, f'{model_file_name}-kernels.pdf'), padding=1, nrow=5, normalize=True)
[…]

### 2022-10-31 python/main.py
fix

@@ -33,7 +33,7 @@ def main():
     range_training_list = [range(50000), range(50000), range(50000), range(50000)]
     range_validation_list = [range(50000, 60000), range(50000, 60000), range(50000, 60000), range(50000, 60000)]
     test_range_list = [range(10000), range(10000), range(10000), range(10000)]
-    if environ['debug'] == '1':
+    if environ['DEBUG'] == '1':
         epochs_num = 2
         range_training_list = [range_training[:10] for range_training in range_training_list]
         range_validation_list = [range_validation[:10] for range_validation in range_validation_list]

### 2022-11-03 ms.tex
fix

@@
 
-\lstdefinestyle{lststyle}{basicstyle=\tt\footnotesize, captionpos=b, frame=single}
-
 \begin{document}
@@
 
-\title{A Makefile for Developing Containerized \LaTeX\ Technical Documents}
+\title{Principle of least action as a software development method}
 
@@
 \begin{abstract}
-	We propose a Makefile for developing containerized \LaTeX\ technical documents.
-	The Makefile allows the author to execute the code that generates variables, tables and figures (results), which are then used during the \LaTeX\ compilation, to produce either the draft (fast) or full (slow) version of the document.
-	We also present various utilities that aid in automating the results generation and improve the reproducibility of the document.
-	We lastly release an open source repository of this paper that uses the Makefile.
+	We propose principle of least action as a software development method.
+	We release open source repositories of the examples use cases of this method.
 \end{abstract}
@@
 \section{Introduction}
-Developing technical documents that present both computationally generated results (variables, tables and figures) and natural text, is a central aspect of computational research.
-One programming paradigm that was proposed as a solution is \textit{literate programming}~\cite{knuth1984literate}, in which the author inserts snippets of code and the output of its execution, alongside natural text.
-Applications of \textit{literate programming} include Jupyter~\cite{kluyver2016jupyter} which allows publishing code, results and explanations in a executable format, PythonTeX~\cite{poore2015pythontex} which allows Python to be executed in \LaTeX\ and ActivePapers~\cite{hinsen2014activepapers} in which code can be executed using the Java Virtual Machine.
+Action is ...
+Principle of least action is ...
 
-Although \textit{literate programming} provides many advantages for demonstrative projects and immediate visual feedback during experimentation, its `dual nature' constrains authors in using specifically designed text editors and/or source code formats thus leading to `app/vendor lock-in' situations.
-Moreover, the overlap between natural text and results code makes \textit{literate programming} difficult to debug and version control.
+\section{Action and software development}
+a. characteristics of the user (e.g. technical capabilities)
+b. characteristics of the user environment (e.g. Operating system)
+c. characteristics of the developer (e.g. technical capabilities)
+choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future)
+d. characteristics of the developer environment (e.g. Operating system)
+different stakeholders calculate different actions. the developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
+if the benefit is greater than the cost then it is implemented
+moreover the cost and benefits are relative to the user and developer respectively
+software development should take in consideration stability both for the user and the developer across two axis: space (other machines) and time
+stability not only applies the same program use but also to other programs
+the benefit of achieving a target is balanced with the cost of the time required to achieve it
+the minimal action principle results in the unix philosophy: Programs should do one thing and one thing only.
+From that sense a window manager should only be responsible for managing windows and not workspaces, tags etc
+the central concept of the paper is translating the idea of action and the principle of minimal action to software development as a specification and then show the implementation that uses Makefile+containers
+present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
+creating a program (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
+it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
+the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
+the target is the the final program which can be reached with make. The target should fulfill the needs of the users and can change
+both users and developers want to reduce their relative action. Balance is achieved at a point
+The principle of least action can be used throughout all decision of a software project.
 
-We propose a Makefile for developing containerized \LaTeX\ technical documents.
-By using portable technologies that withstood the test of time, we ensure the stability and portability of the proposed Makefile.
-We write this paper using a repository that consists of the Makefile and choose Docker as the container technology and the Python programming language for generating the results.
+\section{Development environment/tools}
+Mention install-archlinux.
+Mention vim etc.
 
-For the rest of the paper we will refer to:
+\section{The Makefile}
+The principle of least action has been applied in the following aspects of the Makefile:
 \begin{itemize}
-	\item \textit{results code} as the scientific-oriented programming language code (\textit{main.py}) that produces the variables, tables and figures,
-	\item \textit{results} as the variables, tables and figures that are generated by the \textit{results code},
-	\item \textit{\LaTeX\ code} as the natural text (\textit{ms.tex}) and bibliography (\textit{ms.bib}),
-	\item \textit{code} as both the \textit{results code} and \textit{\LaTeX\ code},
-	\item \textit{document} as the technical document that contains the rendered \textit{results} and natural text and
-	\item \textit{author} as the author of the \textit{document} that develops the \textit{code}.
+	\item this
+	\item that
 \end{itemize}
 
-\section{The Makefile}
+although we could have a target regarding downloading external data this makes the Makefile non-portable for other projects thus this action needs to be done within the code
+consistency across time from the developer perspective means that the technology used to program it will be available in the future
+consistency across time from the user perspective practically means that the program should be finished from the point of view of features and only bug fixes might be developed
+makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
+the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard with the exception of docker or npm where needed
+there is an inverse relationship between consistency and configurability
+think about that I have used subsets of standards
+time includes user interation to reach the target and total development time (including maintainance)
+users care about the program, developers care about the code
+we define a target of reducing the time required to create and navigate windows in a computing environment
+we use Makefile to create the isolated environment (container) by bootstraping all required files if not already present and to make sure that subsequent changes to the requirements update the environment.
+The DAG should be as project agnostic as possible thus sentinel files are used
+we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel
 
-\begin{figure}[!t]
-	\centering
-	\begin{tikzpicture}[%
-			grow via three points={one child at (0.5,-0.7) and two children at (0.5,-0.7) and (0.5,-1.4)},
-			edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
-			\node[draw](document){document/}
-			child{node[draw, anchor=west](makefile){Makefile}}
-			child{node[draw, anchor=west, fill=red!20](tex){ms.tex}}
-			child{node[draw, anchor=west, fill=red!20](bib){ms.bib}}
-			child{node[draw, anchor=west, fill=blue!20](py){main.py}}
-			child{node[draw, anchor=west, fill=blue!20](containerfile){Containerfile}}
-			child{node[draw, anchor=west, fill=blue!20](requirements){requirements.txt}};
-			\begin{scope}[on background layer]
-				\node[draw, rounded corners, dashed, fill=gray!20, inner sep=4pt, fit=(document) (requirements)]{};
-				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(py) (requirements)](code){};
-				\node[draw, rounded corners, dashed, fill=gray!80, inner sep=2pt, fit=(tex) (bib)](document){};
-			\end{scope}
-			\node[draw, right=1.5cm of code, fill=green!20] (results) {python/bin/results};
-			\path[draw, ->] (code) -- (results);
-			\node[draw, right=4cm of document, fill=green!20] (pdf) {python/bin/ms.pdf};
-			\path[draw, ->] (results) |- (pdf);
-			\path[draw, ->] (document) -- (pdf);
-	\end{tikzpicture}
-	\caption{The files of a repository that uses the Makefile is depicted in the light gray background and the arrows denote the containerized data flow towards generating the \textit{document}.
-	Green indicates temporary cache or generated files, red \textit{\LaTeX\ code} files, blue \textit{results code} files and within the dark gray background, files that are developed by the \textit{author}.}\label{fig:repositoryfiles}
-\end{figure}
+\section{Variable naming}
+think prime-modifier-class naming scheme and how it relates to the action-as-information
 
-The proposed Makefile can be used for developing \textit{documents} that consist of \textit{results} generated from \textit{results code} executed within a container.
-The three tools that are used by the Makefile are the Make program which is a build automation tool, \LaTeX\ which is a typesetting system for publishing high quality research documents, and the container technology (such as Docker) which allows portable execution of \textit{code} between different hardware, operating systems and environments.
+\section{Example use case: window manager}
+an extreme example of configurable window managers is `ricing' where the window manager is configured mostly for form and not function
+fswm targets users with high technical capabilities (therefore no visual indication is needed regarding which window they are in every time etc.)
+if keyboard portability is not so important then keycodes are hardcoded for the specific user environment
+moreover a window manager should open windows only in full screen
+the concept of tiling window managers is oriented towards multitasking
+the key shortcuts of a window manager should be predictable by resembling as close as possible most other window managers and development environemnts
+the need to be portable across different keyboards demands the use of an additional requirement (xcb-util-keysyms)
+the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
+the windows could be easily represented as a cyclic doubly linked list
+thus C89 was chosen for optimal portability and xcb as the main library
+an additional advantage of non-configurability is that the program is ready to be used when installed
 
-The pseudoalgorithm of the Makefile is as follows:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Pseudoalgorithm of the Makefile.}]
-bin/$(document_pdf): $(latex_code) bin/$(results)
-	run container latex
-
-bin/$(results): $(results_code)
-	build image $(results_image)
-	run container $(results_image)
-
-clean:
-	rm -rf bin/
-\end{lstlisting}
-
-The default target runs the container for the \LaTeX\ compilation while the \textit{results} target builds the image and runs the container that generates the \textit{results}.
-When the \textit{author} edits a file from \textit{results code} or \textit{\LaTeX\ code}, only the required compilation is automatically triggered with Make.
-Forced compilations without change could be done using the \textit{touch} utility that updates the modification time of a file.
-
-The basic commands of the Makefile are the following:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Basic Makefile commands.}]
-make                # Generate draft bin (fast).\ 
-make FULL=1         # Generate full bin (slow).\ 
-make clean          # Remove bin/ directory.
-\end{lstlisting}
-
-The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
-\begin{enumerate}
-	\item clones/downloads the repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:repositoryfiles},
-	\item creates and develops the \textit{results code}.
-	\item creates and develops the \textit{\LaTeX\ code}.
-	\item executes \textit{make} for fast development iterations and experimentation,
-	\item executes \textit{make FULL=1} for distribution or publication and
-	\item executes \textit{make clean} to restore to a clean state.
-\end{enumerate}
-
-The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{bin/} respectively.
-An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.
-
-\section{The Makefile utilities}
-In this section we present useful utilities that can be combined with the Makefile to automate \textit{results} generation and improve the reproducibility of the \textit{document}.
-
-A useful \LaTeX\ package for automatically presenting variables from \textit{results} in \textit{\LaTeX\ code} is \textit{datatool} with the following example use:
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ datatool example of loading a file that contains pairs of keys and values (bin/keys-values.csv) generated by a \textit{results code} and getting the value of a key named lr.}]
-\DTLloaddb{keys-values}{bin/keys-values.csv}
-\DTLfetch{keys-values}{key}{lr}{value}
-\end{lstlisting}
-
-When using Python, a useful function for \textit{results code} is \textit{pandas.DataFrame.to\_latex} which automatically converts a dataframe table to a \LaTeX\ table:
-\begin{lstlisting}[language=python, style=lststyle, caption={Convert Pandas DataFrame (df) to \LaTeX\ table (bin/metrics.tex) in \textit{results code}.}]
-df = pd.DataFrame(table)
-df.to_latex("bin/metrics.tex", float_format="%.2f")
-\end{lstlisting}
-
-There are some considerations need to be taken into account when reproducibility is needed.
-Regarding \LaTeX\, a culprit against reproducibility is the time-date metadata embedded in the pdf output.
-These can be disabled using the following commands into the \textit{\LaTeX\ code} or as extra arguments during \LaTeX\ compilation (as done by default in the Makefile):
-\begin{lstlisting}[language=TeX, style=lststyle, caption={\LaTeX\ pdf reproducibility commands.}]
-\pdfinfoomitdate=1
-\pdfsuppressptexinfo=-1
-\pdftrailerid{}
-\end{lstlisting}
-
-Regarding the \textit{results code} for Python, we can achieve deterministic stochasticity by setting the random seeds to a specific value such as:
-\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for popular libraries.}]
-# build-in random module
-random.seed(0)
-# numpy
-np.random.seed(0)
-# tensorflow
-tf.random.set_seed(0)
-# pytorch
-torch.backends.cudnn.benchmark = False
-torch.backends.cudnn.deterministic = True
-torch.cuda.manual_seed_all(0)
-torch.manual_seed(0)
-\end{lstlisting}
-
-Additionally, an \textit{author} can use the \textit{cmp} utility to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope for identifying sources of non-determinism as follows:
-\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
-# Generate the first draft document version.\ 
-make
-# Backup the first resulting pdf.\ 
-cp bin/ms.pdf bin/ms-previous.pdf
-# Update the modification timestamp of main.py.\ 
-touch main.py
-# Generate the second draft document version.\ 
-make
-# Compare draft document versions byte by byte.\ 
-cmp bin/ms.pdf bin/ms-previous.pdf
-# Compare draft document versions
-# in a human readable form.\ 
-diffoscope bin/ms.pdf bin/ms-previous.pdf
-\end{lstlisting}
-
-\section{Example use case of the Makefile}
-This section provides a use case of the Makefile and also serves as a manual for developing \LaTeX\ \textit{documents} with Python as the \textit{results code} programming language.
+\section{Example use case: technical document}
+This section provides a use case of the Makefile and also serves as a manual for developing using this method.
 We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
@@
 
-\section{Discussion}
+\section{About the use of Make}
 The proposed Makefile is based on plain text file editing and can be used with any operating system that supports containers and Make.
@@
 \section*{Conclusion}
-Creation, usage and publication of technical documents are one of the top challenges for reproducible technical documents~\cite{barba2019praxis}.
-The proposed Makefile aids to this purpose by providing a way to write reproducible technical documents using the standard tools that many of the academics already use (\LaTeX, Docker, Make) in a portable, efficient and future-proof way.
 

### 2022-11-03 python/main.py
fix

@@ -15,7 +15,7 @@ import torch
 
 
 def change_module(model, module_new, module_old):
-    for (child_name, child) in model.named_children():
+    for child_name, child in model.named_children():
         if isinstance(child, module_old):
             setattr(model, child_name, module_new())
         else:
@@ -50,14 +50,14 @@ def main():
     accuracy_test_array = np.zeros((len(dataset_list), len(activation_function_name_list)))
     batch_size_test = 1000
     cross_entropy_loss = nn.CrossEntropyLoss()
-    for (dataset_index, (dataset, dataset_name, range_training, range_validation, test_range, std_mean)) in enumerate(zip(dataset_list, dataset_name_list, range_training_list, range_validation_list, test_range_list, std_mean_list)):
+    for dataset_index, (dataset, dataset_name, range_training, range_validation, test_range, std_mean) in enumerate(zip(dataset_list, dataset_name_list, range_training_list, range_validation_list, test_range_list, std_mean_list)):
         transform = Compose([ToTensor(), Lambda(lambda tensor: torch.cat([tensor, tensor, tensor], 0)), Normalize(std_mean[0], std_mean[1])])
         dataset_training = dataset('bin', transform=transform, download=True)
         dataset_test = dataset('bin', train=False, transform=transform, download=True)
         dataloader_training = DataLoader(dataset_training, batch_size=batch_size, sampler=SubsetRandomSampler(range_training))
         dataloader_validation = DataLoader(dataset_training, batch_size=batch_size, sampler=SubsetRandomSampler(range_validation))
         dataloader_test = DataLoader(dataset_test, batch_size=batch_size_test, sampler=SubsetRandomSampler(test_range))
-        for (activation_function_name_index, activation_function_name) in enumerate(activation_function_name_list):
+        for activation_function_name_index, activation_function_name in enumerate(activation_function_name_list):
             model = mobilenet_v2().to(device)
             if activation_function_name == 'SiLU':
                 change_module(model, nn.SiLU, nn.ReLU6)
@@ -71,7 +71,7 @@ def main():
                 loss_training_sum = 0
                 predictions_num = 0
                 model.train()
-                for (data, target) in dataloader_training:
+                for data, target in dataloader_training:
                     data = data.to(device)
                     target = target.to(device)
                     output = model(data)
@@ -87,7 +87,7 @@ def main():
                 predictions_num = 0
                 model.eval()
                 with torch.no_grad():
[…]

### 2022-11-11 ms.tex
fix

@@
 \section{Action and software development}
+The principle of least action can be used throughout all decision of a software project.
+
 a. characteristics of the user (e.g. technical capabilities)
@@
 both users and developers want to reduce their relative action. Balance is achieved at a point
-The principle of least action can be used throughout all decision of a software project.
 
@@
 we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel
+
+\section{Various}
+semantic html is a standard. And standards should be used if no personal opinion is required in the subject.
 

### 2022-11-14 makefile-tests.sh
fix

@@ -1,4 +1,4 @@
-#!/bin/bash
+#!/bin/sh
 set -o errexit
 
 # Requirements: ash, bash, dash, ksh, posh, yash, zsh, bmake and make

### 2022-12-08 ms.tex
fix

@@
 \section{Introduction}
-Action is ...
-Principle of least action is ...
+Action is this.
+Principle of least action is that.
+So this is a sentence.
 
@@
 the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
-the target is the the final program which can be reached with make. The target should fulfill the needs of the users and can change
+the target is the final program which can be reached with make. The target should fulfill the needs of the users and can change
 both users and developers want to reduce their relative action. Balance is achieved at a point
@@
 makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
-the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard with the exception of docker or npm where needed
+the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard except for docker where needed
 there is an inverse relationship between consistency and configurability
-think about that I have used subsets of standards
+think about that subsets of standards have been used
 time includes user interation to reach the target and total development time (including maintainance)
@@
 the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
-the windows could be easily represented as a cyclic doubly linked list
+the windows could be represented as a cyclic doubly linked list
 thus C89 was chosen for optimal portability and xcb as the main library
@@
 Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.
-We also use the \textit{pandas.DataFrame.to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):
+We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):
 
@@
 	\item common development environment across multiple \textit{authors},
-	\item coauthors, reviewers, journal editors or other researchers can easily reproduce the \textit{document} with few requirements.
+	\item coauthors, reviewers, journal editors or other researchers can reproduce the \textit{document} with few requirements.
 \end{itemize}

### 2022-12-15 ms.tex
fix

@@
 \documentclass[journal]{IEEEtran}
-\usepackage[caption=false,font=footnotesize]{subfig}
 \usepackage[nopdftrailerid=true]{pdfprivacy}
-\usepackage{booktabs}
-\usepackage{datatool}
-\usepackage{listings}
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\usetikzlibrary{trees}
-\usetikzlibrary{fit}
-\usetikzlibrary{backgrounds}
-\usepackage{hyperref}
 
 \begin{document}
-\DTLloaddb{keys-values}{python/bin/keys-values.csv}
 
@@
 So this is a sentence.
+Software development practices like agile~\cite{abrahamsson2017agile}.
 
@@
 we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel
+The Makefile is only responsible for install the requirements inside the container.
+The specific command arguments that e.g. check applications take should be done outside of the container to prevent the cache invalidation of the container.
 
@@
 This section provides a use case of the Makefile and also serves as a manual for developing using this method.
-We train, validate and test MobilenetV2 neural networks~\cite{sandler2018mobilenetv2} in PyTorch, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.
-We use the default train, validation and test datasets and compare the use of ReLU, ReLU6\cite{dahl2013improving} and SiLU\cite{elfwing2018sigmoid} activation functions in the MobilenetV2 model.
-
-Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}: the number of epochs is $\DTLfetch{keys-values}{key}{epochs-num}{value}$, the batch size is $\DTLfetch{keys-values}{key}{batch-size}{value}$ and the learning rate for SGD is $\DTLfetch{keys-values}{key}{lr}{value}$.
-Additionally, making use of random seed setting we consistenly get the same figures as shown in Fig.\ref{fig:loss} and Fig.\ref{fig:kernels}.
-We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table (as shown in Table~\ref{table:table}):
-
-\begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-loss.pdf}}
-	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-loss.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-loss.pdf}}
-	\caption{Comparison of the train and validation loss of MobilenetV2 with ReLU, ReLU6 and SiLU for all datasets.}\label{fig:loss}
-\end{figure}
-
-\begin{figure}[!t]
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/MNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/FashionMNIST-ReLU-kernels.pdf}}
-	\\
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/KMNIST-ReLU-kernels.pdf}}
-	\subfloat{\includegraphics[width=0.5\columnwidth]{python/bin/QMNIST-ReLU-kernels.pdf}}
-	\caption{The first 25 kernels of the first convolutional layer of MobilenetV2 with ReLU for MNIST (upper-left), FashionMNIST (upper-right), KMNIST (lower-left) and QMNIST (lower-right).}\label{fig:kernels}
-\end{figure}
-
-\begin{table}[ht]
-	\centering
-	\caption{MobilenetV2 test dataset accuracies.}\label{table:table}
-	\setlength\tabcolsep{4pt}
-	\input{python/bin/metrics.tex}
-\end{table}
+Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}.
+Additionally, making use of random seed setting we consistenly get the same figures.
+We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table.
 

### 2022-12-15 python/main.py

@@ -1,148 +1,0 @@
-from matplotlib import pyplot as plt
-from matplotlib.ticker import MaxNLocator
-from os import environ
-from os.path import join
-from torch import nn, optim
-from torch.utils.data import DataLoader
-from torch.utils.data.sampler import SubsetRandomSampler
-from torchvision.datasets import FashionMNIST, KMNIST, MNIST, QMNIST
-from torchvision.models import mobilenet_v2
-from torchvision.transforms import Compose, Lambda, Normalize, ToTensor
-from torchvision.utils import save_image
-import numpy as np
-import pandas as pd
-import torch
-
-
-def change_module(model, module_new, module_old):
-    for child_name, child in model.named_children():
-        if isinstance(child, module_old):
-            setattr(model, child_name, module_new())
-        else:
-            change_module(child, module_new, module_old)
-
-
-def main():
-    plt.rcParams['font.size'] = 18
-    plt.rcParams['savefig.format'] = 'pdf'
-    dataset_list = [MNIST, FashionMNIST, KMNIST, QMNIST]
-    dataset_name_list = [dataset.__name__ for dataset in dataset_list]
-    activation_function_name_list = ['ReLU', 'ReLU6', 'SiLU']
-    std_mean_list = [((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,)), ((0.1307,), (0.3081,))]
-    epochs_num = 20
-    range_training_list = [range(50000), range(50000), range(50000), range(50000)]
-    range_validation_list = [range(50000, 60000), range(50000, 60000), range(50000, 60000), range(50000, 60000)]
-    test_range_list = [range(10000), range(10000), range(10000), range(10000)]
-    if environ['DEBUG'] == '1':
-        epochs_num = 2
-        range_training_list = [range_training[:10] for range_training in range_training_list]
-        range_validation_list = [range_validation[:10] for range_validation in range_validation_list]
-        test_range_list = [test_range[:10] for test_range in test_range_list]
-    np.random.seed(0)
-    torch.backends.cudnn.benchmark = False
-    torch.backends.cudnn.deterministic = True
-    torch.manual_seed(0)
-    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-    lr = 0.01
-    batch_size = 64
-    loss_training_array = np.zeros((len(dataset_list), len(activation_function_name_list), epochs_num))
[…]

### 2022-12-30 ms.tex
fix

@@
 \begin{abstract}
-	We propose principle of least action as a software development method.
+	This paper proposes the principle of least action as a software development method.
 	We release open source repositories of the examples use cases of this method.
@@
 Action is this.
-Principle of least action is that.
-So this is a sentence.
+Principle of least action (PLA) is that.
 Software development practices like agile~\cite{abrahamsson2017agile}.
 
-\section{Action and software development}
-The principle of least action can be used throughout all decision of a software project.
+PLA can be used throughout all software-related decisions:
+\begin{enumerate}
+	\item whether to use dependencies (e.g. libraries, frameworks) or implement a build-in solution
+	\item whether to use standards or extend/restrict/ignore them
+	\item whether to implement/drop a feature
+	\item whether to use a tool (e.g. text editor, IDE)
+\end{enumerate}
 
+PLA can be used for both the user and the developer across two axis: space (other machines) and time
 a. characteristics of the user (e.g. technical capabilities)
@@
 d. characteristics of the developer environment (e.g. Operating system)
-different stakeholders calculate different actions. the developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
+
+Action is relative to the observer.
+The developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
+both developers and users want to reduce their relative action. A minimum is achieved at a point
+moreover the cost and benefits are relative to the user and developer respectively
 if the benefit is greater than the cost then it is implemented
-moreover the cost and benefits are relative to the user and developer respectively
-software development should take in consideration stability both for the user and the developer across two axis: space (other machines) and time
-stability not only applies the same program use but also to other programs
 the benefit of achieving a target is balanced with the cost of the time required to achieve it
-the minimal action principle results in the unix philosophy: Programs should do one thing and one thing only.
-From that sense a window manager should only be responsible for managing windows and not workspaces, tags etc
-the central concept of the paper is translating the idea of action and the principle of minimal action to software development as a specification and then show the implementation that uses Makefile+containers
-present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
-creating a program (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
+
+The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
+present the Makefile for python and tex for document generation and then the Makefile for website creation
+creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
 it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
 the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
-the target is the final program which can be reached with make. The target should fulfill the needs of the users and can change
-both users and developers want to reduce their relative action. Balance is achieved at a point
+the target is the application which can be reached with make. The target should fulfill the needs of the users and can change
 
@@
 \section{The Makefile}
-The principle of least action has been applied in the following aspects of the Makefile:
+PLA has been applied in the following aspects of the Makefile:
 \begin{itemize}
@@
 
-although we could have a target regarding downloading external data this makes the Makefile non-portable for other projects thus this action needs to be done within the code
 consistency across time from the developer perspective means that the technology used to program it will be available in the future
-consistency across time from the user perspective practically means that the program should be finished from the point of view of features and only bug fixes might be developed
+consistency across time from the user perspective practically means that the application should be finished from the point of view of features and only bug fixes might be developed
 makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
@@
 time includes user interation to reach the target and total development time (including maintainance)
-users care about the program, developers care about the code
+users care about the application, developers care about the code
 we define a target of reducing the time required to create and navigate windows in a computing environment
@@
 think prime-modifier-class naming scheme and how it relates to the action-as-information
-
-\section{Example use case: window manager}
-an extreme example of configurable window managers is `ricing' where the window manager is configured mostly for form and not function
-fswm targets users with high technical capabilities (therefore no visual indication is needed regarding which window they are in every time etc.)
-if keyboard portability is not so important then keycodes are hardcoded for the specific user environment
-moreover a window manager should open windows only in full screen
-the concept of tiling window managers is oriented towards multitasking
-the key shortcuts of a window manager should be predictable by resembling as close as possible most other window managers and development environemnts
-the need to be portable across different keyboards demands the use of an additional requirement (xcb-util-keysyms)
-the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
-the windows could be represented as a cyclic doubly linked list
-thus C89 was chosen for optimal portability and xcb as the main library
-an additional advantage of non-configurability is that the program is ready to be used when installed
 

### 2022-12-30 ms.tex
fix

@@
 The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
-present the Makefile for python and tex for document generation and then the Makefile for website creation
+present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
 creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
@@
 
+\section{Example use case: window manager}
+an extreme example of configurable window managers is `ricing' where the window manager is configured mostly for form and not function
+fswm targets users with high technical capabilities (therefore no visual indication is needed regarding which window they are in every time etc.)
+if keyboard portability is not so important then keycodes are hardcoded for the specific user environment
+moreover a window manager should open windows only in full screen
+the concept of tiling window managers is oriented towards multitasking
+the key shortcuts of a window manager should be predictable by resembling as close as possible most other window managers and development environemnts
+the need to be portable across different keyboards demands the use of an additional requirement (xcb-util-keysyms)
+the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
+the windows could be represented as a cyclic doubly linked list
+thus C89 was chosen for optimal portability and xcb as the main library
+an additional advantage of non-configurability is that the application is ready to be used when installed
+
 \section{Example use case: technical document}

### 2023-01-02 ms.tex
fix

@@
 there is an inverse relationship between consistency and configurability
-think about that subsets of standards have been used
 time includes user interation to reach the target and total development time (including maintainance)
@@
 The specific command arguments that e.g. check applications take should be done outside of the container to prevent the cache invalidation of the container.
-
-\section{Various}
-semantic html is a standard. And standards should be used if no personal opinion is required in the subject.
 

### 2023-04-11 latex/ms.tex
.

--- 2023-01-02 ms.tex
@@
 \begin{enumerate}
-	\item whether to use dependencies (e.g. libraries, frameworks) or implement a build-in solution
+	\item whether to use dependencies (e.g.\ libraries, frameworks) or implement a build-in solution
 	\item whether to use standards or extend/restrict/ignore them
 	\item whether to implement/drop a feature
-	\item whether to use a tool (e.g. text editor, IDE)
+	\item whether to use a tool (e.g.\ text editor, IDE)
 \end{enumerate}
@@
 PLA can be used for both the user and the developer across two axis: space (other machines) and time
-a. characteristics of the user (e.g. technical capabilities)
-b. characteristics of the user environment (e.g. Operating system)
-c. characteristics of the developer (e.g. technical capabilities)
-choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future)
-d. characteristics of the developer environment (e.g. Operating system)
+\begin{enumerate}
+	\item characteristics of the user (e.g.\ technical capabilities)
+	\item characteristics of the user environment (e.g.\ Operating system)
+	\item characteristics of the developer (e.g.\ technical capabilities)
+	\item characteristics of the developer environment (e.g.\ Operating system)
+\end{enumerate}
+Choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future).
 
@@
 
-The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
-present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
+The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile and containers.
+Present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
 creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
@@
 The Makefile is only responsible for install the requirements inside the container.
-The specific command arguments that e.g. check applications take should be done outside of the container to prevent the cache invalidation of the container.
+The specific command arguments that e.g.\ check applications take should be done outside of the container to prevent the cache invalidation of the container.
 

### 2023-11-30 latex/ms.tex
.

@@
 \author{Paschalis~Bizopoulos
-\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com}}
+\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizop@gmail.com}}
 
@@
 
-PLA can be used throughout all software-related decisions:
+PLA can be used throughout all software-related decisions. For example:
 \begin{enumerate}
@@
 	\item whether to implement/drop a feature
-	\item whether to use a tool (e.g.\ text editor, IDE)
+	\item whether to use a development tool (e.g.\ text editor, IDE)
 \end{enumerate}
@@
 the target is the application which can be reached with make. The target should fulfill the needs of the users and can change
+
+It starts with a user requirement.
+Is it important?
+If yes then, should it be solved with software?
+If yes, then does it already exist?
+If no, then can it programmed as a feature to an existing repo?
+If no then create new repo.
+If yes, then is it a new directory in the existing repo?
+If yes then does it use an artifact of another repo?
+If yes, then make it a parent directory of the another repo.
+If no, then program the user requirement into the main.py.
 
@@
 think prime-modifier-class naming scheme and how it relates to the action-as-information
+\begin{itemize}
+	\item Single-function repositories to a verb-noun naming convention.
+	\item Multi-function repositories are appended with -tool.
+	\item Research papers are a whole sentence.
+	\item Repositories with URL are named as the URL\@.
+\end{itemize}
 
@@
 
+\section{Folder structure}
+\begin{itemize}
+	\item prm/: permanent data
+	\item tmp/: temporary data
+	\item main.py: code
+	\item Dockerfile: code for the environment
+	\item pyproject.toml: data for the environment
+\end{itemize}
+
 \section*{Conclusion}

### 2024-02-05 latex/ms.tex
.

--- 2023-01-02 ms.tex
@@
 \documentclass[journal]{IEEEtran}
+\usepackage{dirtree}
+\usepackage[boxed]{algorithm2e}
 \usepackage[nopdftrailerid=true]{pdfprivacy}
@@
 
-\title{Principle of least action as a software development method}
+\title{Portable Development Methodology}
 
 \author{Paschalis~Bizopoulos
-\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com}}
+\thanks{P. Bizopoulos is an Independent Researcher, Thessaloniki, Greece e-mail: pbizop@gmail.com}}
 
@@
 \begin{abstract}
-	This paper proposes the principle of least action as a software development method.
-	We release open source repositories of the examples use cases of this method.
+	This paper proposes a portable development methodology.
+	We release open source repositories of the examples use cases of this.
 \end{abstract}
@@
 \section{Introduction}
-Action is this.
-Principle of least action (PLA) is that.
-Software development practices like agile~\cite{abrahamsson2017agile}.
+Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of it exist in software development.
+This non-portability of software development practices is a lost potential in reducing software development time.
 
-PLA can be used throughout all software-related decisions:
-\begin{enumerate}
-	\item whether to use dependencies (e.g. libraries, frameworks) or implement a build-in solution
-	\item whether to use standards or extend/restrict/ignore them
-	\item whether to implement/drop a feature
-	\item whether to use a tool (e.g. text editor, IDE)
-\end{enumerate}
+In this paper we present the design and implementation of the Makefile for python and tex for document generation and then the Makefile for website creation.
 
-PLA can be used for both the user and the developer across two axis: space (other machines) and time
-a. characteristics of the user (e.g. technical capabilities)
-b. characteristics of the user environment (e.g. Operating system)
-c. characteristics of the developer (e.g. technical capabilities)
-choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future)
-d. characteristics of the developer environment (e.g. Operating system)
-
-Action is relative to the observer.
-The developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
-both developers and users want to reduce their relative action. A minimum is achieved at a point
-moreover the cost and benefits are relative to the user and developer respectively
-if the benefit is greater than the cost then it is implemented
-the benefit of achieving a target is balanced with the cost of the time required to achieve it
-
-The aim of this paper is translating the idea of action and PLA to software development and then show the implementation that uses Makefile+containers.
-present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
-creating an application (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
-it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
-the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
-the target is the application which can be reached with make. The target should fulfill the needs of the users and can change
-
-\section{Development environment/tools}
-Mention install-archlinux.
-Mention vim etc.
-
-\section{The Makefile}
-PLA has been applied in the following aspects of the Makefile:
-\begin{itemize}
-	\item this
-	\item that
-\end{itemize}
-
-consistency across time from the developer perspective means that the technology used to program it will be available in the future
-consistency across time from the user perspective practically means that the application should be finished from the point of view of features and only bug fixes might be developed
-makes use of pre-existing standards: GNU standard for Makefile conventions and POSIX for the use of UNIX tools
-the portability of the Makefile is achieved by using the mandatory UNIX utilities also mentioned by the GNU standard except for docker where needed
-there is an inverse relationship between consistency and configurability
-time includes user interation to reach the target and total development time (including maintainance)
-users care about the application, developers care about the code
-we define a target of reducing the time required to create and navigate windows in a computing environment
-we use Makefile to create the isolated environment (container) by bootstraping all required files if not already present and to make sure that subsequent changes to the requirements update the environment.
-The DAG should be as project agnostic as possible thus sentinel files are used
-we use these specific targets for the Makefile (all, check, clean, help) because the first three are standard targets recommended by GNU standard targets and the fourth one is used in the linux kernel
-The Makefile is only responsible for install the requirements inside the container.
-The specific command arguments that e.g. check applications take should be done outside of the container to prevent the cache invalidation of the container.
-
-\section{Variable naming}
-think prime-modifier-class naming scheme and how it relates to the action-as-information
-
-\section{Example use case: window manager}
-an extreme example of configurable window managers is `ricing' where the window manager is configured mostly for form and not function
-fswm targets users with high technical capabilities (therefore no visual indication is needed regarding which window they are in every time etc.)
-if keyboard portability is not so important then keycodes are hardcoded for the specific user environment
-moreover a window manager should open windows only in full screen
-the concept of tiling window managers is oriented towards multitasking
-the key shortcuts of a window manager should be predictable by resembling as close as possible most other window managers and development environemnts
-the need to be portable across different keyboards demands the use of an additional requirement (xcb-util-keysyms)
-the set of functionalities that should be integrated to a window manager are: Enter next/previous window and open program in new window
-the windows could be represented as a cyclic doubly linked list
-thus C89 was chosen for optimal portability and xcb as the main library
-an additional advantage of non-configurability is that the application is ready to be used when installed
-
-\section{Example use case: technical document}
-This section provides a use case of the Makefile and also serves as a manual for developing using this method.
-Making use of the \textit{datatool} package the values of the following variables are not directly referred in the main \textit{.tex} file but they are instead read by an intermediate \textit{.tex} file created by the \textit{results code}.
-Additionally, making use of random seed setting we consistenly get the same figures.
-We also use the \textit{to\_latex} command which automatically converts a dataframe table to a \LaTeX\ table.
-
-\section{About the use of Make}
-The proposed Makefile is based on plain text file editing and can be used with any operating system that supports containers and Make.
+\section{Make}
 Make has existed for decades and has passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
@@
 \begin{itemize}
-	\item regression testing and debugging, to ensure that changes to \textit{code} do not alter \textit{results},
-	\item common development environment across multiple \textit{authors},
-	\item coauthors, reviewers, journal editors or other researchers can reproduce the \textit{document} with few requirements.
+	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the \texttt{artifacts},
+	\item portable development environment across multiple \texttt{developers},
+	\item portable development environment across time.
 \end{itemize}
 
-\section*{Conclusion}
+Makes use of pre-existing standards:
+\begin{itemize}
+	\item GNU standard targets for Makefile~\cite{stallman1992gnu}
+	\item POSIX Utilities and Shell~\cite{lewine1991posix}
+\end{itemize}
+
+We use Makefile to create the isolated environment (container) by creating all required files if not already present and to make sure that subsequent changes to the requirements update the environment.
+
+The interface of the Makefile is a subset of the GNU standard targets:
+\begin{verbatim}
+make           # execute code 
+make STAGING=1 # execute staging code 
+make check     # check code
+make clean     # remove tmp/
+\end{verbatim}
+
+With the \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
+
+\section{Folder structure}
+\dirtree{%
+.0 python.
+.1 \texttt{.dockerignore}.
+.1 \texttt{.gitignore}.
+.1 Dockerfile.
+.1 Makefile.
+.1 main.py.
+.1 prm/.
+.1 pyproject.toml.
+.1 tmp/.
+}
+
+\section{Workflow}
+
+\begin{algorithm}
+	\KwData{User requirement}
+	\If{user requirement is unimportant}{
+		\Return{}
+	}
+	\If{it can be solved without software}{
+		\Return{}
+	}
+	\If{a package already exists}{
+		Introduce the package as a dependency in the relevant main.py\;
+		\Return{}
+	}
+	\If{a relevant repository exists}{
+		Make repository compatible with stack/method\;
+		\Return{}
+	}
+	\If{it can be programmed within a relevant main.py}{
+		Program it in a relevant main.py\;
+		\Return{}
+	}
+	\If{it can be programmed as a dependency/dependent of another directory}{
+		Create a new dependent directory\;
+		\Return{}
+	}
+	Create a new repository\;
+	\Return{}
+	\caption{Workflow}
+\end{algorithm}
 

### 2024-02-05 latex/ms.tex
.

@@
 \documentclass[journal]{IEEEtran}
-\usepackage{dirtree}
 \usepackage[boxed]{algorithm2e}
@@
 \begin{itemize}
-	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the \texttt{artifacts},
+	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the generated data,
 	\item portable development environment across multiple \texttt{developers},
@@
 
-Makes use of pre-existing standards:
+\section{Directory structure}
+The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
+The interface of the Makefile is a subset of the GNU standard targets:
 \begin{itemize}
-	\item GNU standard targets for Makefile~\cite{stallman1992gnu}
-	\item POSIX Utilities and Shell~\cite{lewine1991posix}
+	\item \texttt{.dockerignore}: Consists of:
+		\begin{itemize}
+			\item * (every file/directory)
+			\item except files needed for environment creation (e.g.\ \texttt{pyproject.toml})
 		\end{itemize}
-
-We use Makefile to create the isolated environment (container) by creating all required files if not already present and to make sure that subsequent changes to the requirements update the environment.
-
-The interface of the Makefile is a subset of the GNU standard targets:
-\begin{verbatim}
-make           # execute code 
-make STAGING=1 # execute staging code 
-make check     # check code
-make clean     # remove tmp/
-\end{verbatim}
-
-With the \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
-
-\section{Folder structure}
-\dirtree{%
-.0 python.
-.1 \texttt{.dockerignore}.
-.1 \texttt{.gitignore}.
-.1 Dockerfile.
-.1 Makefile.
-.1 main.py.
-.1 prm/.
-.1 pyproject.toml.
-.1 tmp/.
-}
+	\item \texttt{.gitignore}: Consists of:
+		\begin{itemize}
+			\item the temporary directory \texttt{tmp/} and
+			\item the environmental variable file \texttt{.env}.
+		\end{itemize}
+	\item \texttt{Dockerfile}: Rarely editable. The developer edits:
+		\begin{itemize}
+			\item the FROM image and
+			\item whether other apt-get installations are done.
+		\end{itemize}
+	\item \texttt{Makefile}: Non-editable. Properties~\cite{stallman1992gnu}:
+		\begin{itemize}
+			\item It should be POSIX-compliant and use POSIX utilities~\cite{lewine1991posix}.
+			\item The \texttt{all} target should generate data saved in \texttt{tmp/}.
+			\item The \texttt{check} target should check all \texttt{code}. It should also check and disallow any additional files or directories besides the ones defined here.
+			\item The \texttt{clean} target should delete \texttt{tmp/}.
+			\item It should support a \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
+			\item It should create all files and directories from the structure if they do not already exist.
+		\end{itemize}
+	\item \texttt{main.py}: Frequently editable. The developer writes \texttt{code} in here that generates data saved in \texttt{tmp/}.
+	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible. This should be as small as possible.
+	\item \texttt{pyproject.toml}: Rarely editable. The developer edits:
+		\begin{itemize}
+			\item the dependencies and
+			\item the version of the dependencies
+		\end{itemize}
+	\item \texttt{tmp/}: Data generated by \texttt{main.py} are saved here.
+\end{itemize}
 

### 2024-02-05 latex/ms.tex
.

@@
 \usepackage[nopdftrailerid=true]{pdfprivacy}
+\usepackage{hyperref}
 
@@
 	This paper proposes a portable development methodology.
-	We release open source repositories of the examples use cases of this.
+	Repository example use cases are also presented.
 \end{abstract}
@@
 \section{Introduction}
-Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of it exist in software development.
-This non-portability of software development practices is a lost potential in reducing software development time.
+Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of each of them exist in software development.
+Loosely defined practices introduce non-portability issues through time and space, increasing development costs.
 
-In this paper we present the design and implementation of the Makefile for python and tex for document generation and then the Makefile for website creation.
+In this paper we present a portable development methodology which is concrete enough to be portable and abstract enough to be of general use.
+We also present example use cases for python and tex document generation and website creation.
 
 \section{Make}
-Make has existed for decades and has passed the test of time, while the container technology was standardized with the Open Container Initiative and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
+Make~\cite{fowler1990case} has been used since 1970s and some of its basic features were standardized by POSIX\@.
 Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.
@@
 \end{itemize}
+
+\section{Containers}
+Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
 
@@
 
-\section{Workflow}
+\section{Workflows}
 
 \begin{algorithm}
-	\KwData{User requirement}
+	\KwData{New user requirement}
 	\If{user requirement is unimportant}{
@@
 	\Return{}
-	\caption{Workflow}
+	\caption{Workflow for new user requirement}
 \end{algorithm}

### 2024-02-05 latex/ms.tex
.

@@
 \section{Introduction}
-Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough thus multiple versions of each of them exist in software development.
+Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple versions of each of them exist in software development.
 Loosely defined practices introduce non-portability issues through time and space, increasing development costs.
@@
 
-\section{Make}
-Make~\cite{fowler1990case} has been used since 1970s and some of its basic features were standardized by POSIX\@.
-Moreover the Makefile can be combined with any version control system, container registry provider and text editor thus preventing `app/vendor lock-in' situations.
+\section{Requirements}
+POSIX utilities and shell are the base of any Unix system today.
+However, by itself is not enough to cover most of the modern needs of software development, namely: machine learning and web applications.
 
-Use cases of the Makefile include:
-\begin{itemize}
-	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the generated data,
-	\item portable development environment across multiple \texttt{developers},
-	\item portable development environment across time.
-\end{itemize}
-
-\section{Containers}
+Containers combined with POSIX utilities and shell can be used to create isolated environments.
 Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.

### 2024-02-06 latex/ms.tex
.

@@
 \documentclass[journal]{IEEEtran}
+\usepackage{dirtree}
 \usepackage[boxed]{algorithm2e}
@@
 
-\title{Portable Development Methodology}
+\title{Development Methodology}
 
@@
 \begin{abstract}
-	This paper proposes a portable development methodology.
-	Repository example use cases are also presented.
+	This paper proposes a development methodology and also presents example use cases.
 \end{abstract}
@@
 \section{Introduction}
-Widespread software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple versions of each of them exist in software development.
-Loosely defined practices introduce non-portability issues through time and space, increasing development costs.
+Software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple subversions of each of them exist in software development.
+Loosely defined practices introduce non-portability issues between developers and through time, increasing development costs.
 
-In this paper we present a portable development methodology which is concrete enough to be portable and abstract enough to be of general use.
+In this paper we present a development methodology which is concrete enough to be portable and abstract enough to be of general use.
 We also present example use cases for python and tex document generation and website creation.
@@
 POSIX utilities and shell are the base of any Unix system today.
-However, by itself is not enough to cover most of the modern needs of software development, namely: machine learning and web applications.
+However, they are not enough to cover modern user/developer requirements, such as machine learning and web applications.
 
-Containers combined with POSIX utilities and shell can be used to create isolated environments.
+Containers such as Docker, can be used to create isolated environments.
 Containers were standardized with the Open Container Initiative\footnote{\url{https://opencontainers.org/}} and there exist alternatives such as Podman that could be used as drop-in replacements for Docker.
@@
 \section{Directory structure}
+\dirtree{.0 python/|docs/|latex/.
+.1 \texttt{.dockerignore}.
+.1 \texttt{.gitignore}.
+.1 Dockerfile.
+.1 Makefile.
+.1 main.py|index.html|ms.tex.
+.1 prm/.
+.1 pyproject.toml|package.json.
+.1 tmp/.
+}
+
 The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
-The interface of the Makefile is a subset of the GNU standard targets:
+The interface of the Makefile is a subset of the GNU standard targets.
+File and directory name whitelisting is enforced with the target of having one file per `technology'.
 \begin{itemize}
@@
 	\item \texttt{main.py}: Frequently editable. The developer writes \texttt{code} in here that generates data saved in \texttt{tmp/}.
-	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible. This should be as small as possible.
+	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible.
+It is a practical `backdoor' out of the file/directory name whitelisting of the Makefile.
+The contents of this directory should be as few as possible.
 	\item \texttt{pyproject.toml}: Rarely editable. The developer edits:
@@
 \begin{algorithm}
-	\KwData{New user requirement}
-	\If{user requirement is unimportant}{
+	\KwData{New user/developer requirement}
+	\If{requirement is unimportant}{
 		\Return{}
@@
 	\Return{}
-	\caption{Workflow for new user requirement}
+	\caption{Workflow for new user/developer requirement}
 \end{algorithm}

### 2024-02-13 latex/ms.tex
.

@@
 
-\title{Development Methodology}
+\title{Software Development Methodology}
 
@@
 \begin{abstract}
-	This paper proposes a development methodology and also presents example use cases.
+	We propose a portable and consistent software development methodology and also refer to example use cases.
 \end{abstract}
@@
 \section{Introduction}
-Software development practices like agile~\cite{abrahamsson2017agile} are not concrete enough, thus multiple subversions of each of them exist in software development.
-Loosely defined practices introduce non-portability issues between developers and through time, increasing development costs.
-
-In this paper we present a development methodology which is concrete enough to be portable and abstract enough to be of general use.
-We also present example use cases for python and tex document generation and website creation.
+Code is usually targeted to be executed by multiple machines and developed by multiple humans.
+Therefore, it is vital to have a portable way for machines to execute code and a consistent way for humans to develop code.
+In this paper we present a simple software development methodology which satisfies these conditions.
+We also refer example use cases for python machine learning applications, \LaTeX{} documents generation and web applications.
 
 \section{Requirements}
-POSIX utilities and shell are the base of any Unix system today.
+Portable code execution is handled by:
+\begin{itemize}
+	\item POSIX Shell and Utilities
+	\item Containers
+\end{itemize}
+
+POSIX is the base of all Unix-based systems today.
+POSIX is maintained by the Austin Group.
 However, they are not enough to cover modern user/developer requirements, such as machine learning and web applications.
@@
 
+Code consistency is handled by:
+\begin{itemize}
+	\item applying a subset of the GNU standard targets for the interface of the Makefile.
+	\item enforcing a directory structure.
+\end{itemize}
+
 \section{Directory structure}
+The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
+File and directory name whitelisting is enforced with the target of having one file per `technology'.
 \dirtree{.0 python/|docs/|latex/.
@@
 
-The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
-The interface of the Makefile is a subset of the GNU standard targets.
-File and directory name whitelisting is enforced with the target of having one file per `technology'.
+More specifically:
 \begin{itemize}

### 2024-02-14 latex/ms.tex
.

@@
 In this paper we present a simple software development methodology which satisfies these conditions.
+We propose using POSIX XCU and Containers for code portability and a directory structure enforcement for code consistency.
 We also refer example use cases for python machine learning applications, \LaTeX{} documents generation and web applications.
 
-\section{Requirements}
-Portable code execution is handled by:
-\begin{itemize}
-	\item POSIX Shell and Utilities
-	\item Containers
-\end{itemize}
-
-POSIX is the base of all Unix-based systems today.
-POSIX is maintained by the Austin Group.
-However, they are not enough to cover modern user/developer requirements, such as machine learning and web applications.
+\section{Code portability}
+POSIX (Portable Operating System Interface) is a set of standards developed by the Austin Group with the target of maintaining compatibility between operating systems.
+More specifically the XCU (Shell and Utilities) volume of POSIX focuses on defining specifications for common utility applications.
+However, POSIX XCU is not enough to cover modern user/developer requirements, such as machine learning and web applications.
 
@@
 
-Code consistency is handled by:
-\begin{itemize}
-	\item applying a subset of the GNU standard targets for the interface of the Makefile.
-	\item enforcing a directory structure.
-\end{itemize}
-
-\section{Directory structure}
+\section{Code Consistency}
 The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
@@
 		\end{itemize}
-	\item \texttt{Makefile}: Non-editable. Properties~\cite{stallman1992gnu}:
+	\item \texttt{Makefile}: Non-editable. Uses a subset of the GNU standard targets. Properties~\cite{stallman1992gnu}:
 		\begin{itemize}
@@
 
-\section{Workflows}
+\section{Workflow}
 
@@
 	\If{a relevant repository exists}{
-		Make repository compatible with stack/method\;
+		Make repository compatible with methodology\;
 		\Return{}
@@
 	}
-	\If{it can be programmed as a dependency/dependent of another directory}{
-		Create a new dependent directory\;
+	\If{it can be put as a parent/child of another directory}{
+		Create a new parent/child directory of another directory\;
 		\Return{}

### 2024-02-14 latex/ms.tex
.

@@
 
+On a higher level the directory should look like this:
+\begin{verbatim}
+$HOME/$PLATFORM_DOMAIN_NAME/$REPOSITORY_OWNER/$REPOSITORY_NAME/
+\end{verbatim}
+
+For example the directory structure that corresponds to the repository that hosts the source code of this paper is:
+\begin{verbatim}
+$HOME/github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents/
+\end{verbatim}
+
+In that way version control related commands could work between different machines.
+For example the following incorporates changes from all \texttt{github.com} remote repositories into the current branches using \texttt{git}:
+\begin{verbatim}
+find $HOME/github.com -name .git | xargs dirname | xargs -I{} -P0 git -C {} pull
+\end{verbatim}
+
 \section{Workflow}

### 2024-02-14 latex/ms.tex
.

--- 2024-02-14 latex/ms.tex
@@
 \section{Code Consistency}
+On a higher level the directory should look like this:
+\dirtree{%
+.1 \texttt{\$HOME/}.
+.2 \texttt{\$PLATFORM\_DOMAIN\_NAME/}.
+.3 \texttt{\$REPOSITORY\_OWNER/}.
+.4 \texttt{\$REPOSITORY\_NAME/}.
+}
+
+For example the directory structure that corresponds to the repository that hosts the source code of this paper is:
+\dirtree{%
+.1 \texttt{\$HOME/}.
+.2 \texttt{github.com/}.
+.3 \texttt{pbizopoulos/}.
+.4 \texttt{software-development-methodology/}.
+}
+
 The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
 File and directory name whitelisting is enforced with the target of having one file per `technology'.
-\dirtree{.0 python/|docs/|latex/.
-.1 \texttt{.dockerignore}.
-.1 \texttt{.gitignore}.
-.1 Dockerfile.
-.1 Makefile.
-.1 main.py|index.html|ms.tex.
-.1 prm/.
-.1 pyproject.toml|package.json.
-.1 tmp/.
+\dirtree{%
+.1 python/|docs/|latex/.
+.2 \texttt{.dockerignore}.
+.2 \texttt{.gitignore}.
+.2 Dockerfile.
+.2 Makefile.
+.2 main.py|index.html|ms.tex.
+.2 prm/.
+.2 pyproject.toml|package.json.
+.2 tmp/.
 }
@@
 
+Code consistency on the directory structure level also brings code portability and also easier execution of commands on multiple repositories.
+Using POSIX Utilities we can use the following:
+\begin{verbatim}
+find $HOME/$DIRECTORY -name $DIRECTORY_OR_FILE |\
+xargs dirname |\
+xargs -I{} -P0 $COMMAND
+\end{verbatim}
+
+For example the following incorporates changes from all \texttt{github.com} remote repositories into the current branches using \texttt{git}:
+\begin{verbatim}
+find $HOME/github.com -name .git |\
+xargs dirname |\
+xargs -I{} -P0 git -C {} pull
+\end{verbatim}
+
+Another example is to \texttt{make check} all \texttt{github.com} repositories from user \texttt{pbizopoulos}:
+\begin{verbatim}
+find $HOME/github.com/pbizopoulos/ -name Makefile |\
+xargs dirname |\
+xargs -I{} -P0 make check -C {}
+\end{verbatim}
+
 \section{Workflow}

### 2024-02-22 latex/ms.tex
.

@@
 
-\title{Software Development Methodology}
+\title{Abstraction-averse programming}
 
@@
 \begin{abstract}
-	We propose a portable and consistent software development methodology and also refer to example use cases.
+	We propose a software development methodology for portable and consistent code and also refer to example use cases.
 \end{abstract}
@@
 \section{Introduction}
+The most important problem today with software is its increasing complexity which can be attributed to the use of unnessesary abstractions.
+Abstractions can be variables, functions, classes, modules, files, directories, third-party dependencies.
+Most of the times using already existing abstractions is better than creating/introducing new ones.
+
 Code is usually targeted to be executed by multiple machines and developed by multiple humans.
@@
 We propose using POSIX XCU and Containers for code portability and a directory structure enforcement for code consistency.
-We also refer example use cases for python machine learning applications, \LaTeX{} documents generation and web applications.
+We also refer example use cases for python machine learning applications, \LaTeX{} documents generation, web applications and python packages.
+
+\section{Abstraction-averse programming}
+The phrase "Abstraction-averse" is in contrast to "Abstraction-free" where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
+However "Abstraction-averse" recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.
 

### 2024-03-01 latex/ms.tex
update dependencies

@@
 \section{Abstraction-averse programming}
-The phrase "Abstraction-averse" is in contrast to "Abstraction-free" where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
-However "Abstraction-averse" recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.
+Abstraction-averse is in contrast to Abstraction-free where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
+However Abstraction-averse recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.
 
